### 2023-05-19 Manuscript.Rmd
updates

---
title: "Manuscript"
author: "Jesper Fischer Ehmsen"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(tidyverse, osfr, lmerTest, MuMIn, DHARMa, here, cmdstanr, tidybayes, bayesplot, posterior,future,furrr, patchwork, R.utils, brms)

scripts = c("agent.R","parameter_recovery.R","stan_functions.R")
q = lapply(here("scripts", scripts), source)
```

## R Markdown

```{r parameter recovery for RW}
mu_alpha = seq(0.1,0.5,by = 0.1)
kappa_alpha = seq(10,300,length.out = 3)

mu_w1 = seq(0.1,0.5,by = 0.1)
kappa_w1 = seq(10,300,length.out = 3)

sd_precision_percept = seq(0.1,2, length.out = 3)

sd_beta = seq(0.1,2, length.out = 3)

nsubs = 50

parameters = expand.grid(mu_alpha = mu_alpha,
                         kappa_alpha = kappa_alpha,
                         mu_w1 = mu_w1,
                         kappa_w1 = kappa_w1,
                         sd_precision_percept = sd_precision_percept,
                         sd_beta = sd_beta,
                         nsubs = nsubs)

parameters$id = 1:nrow(parameters)

data_list <- split(parameters, parameters$id)

plan(multisession, workers = availableCores()-1)

data_list = data_list[1:100]

rw_pp = furrr::future_map(data_list, ~parameter_recovery_rw(.x), .progress = TRUE, .options = furrr_options(seed = 123))
```

```{r parameter recovery for WB}

mu_alpha = seq(0.1,0.5,by = 0.1)
kappa_alpha = seq(10,300, length.out = 3)

mu_w1 = seq(0.1,0.5,by = 0.1)
kappa_w1 = seq(10,300, length.out = 3)

mu_w2 = seq(0.3,0.3,by = 0.1)
kappa_w2 = seq(10,300, length.out = 3)

sd_percept_precision = seq(0.1,2, length.out = 3)

sd_beta = seq(0.1,2, length.out = 3)

nsubs = 50

parameters = expand.grid(nsubs = nsubs, 
                         mu_alpha = mu_alpha, 
                         kappa_alpha = kappa_alpha, 
                         mu_w1 =  mu_w1, kappa_w1 = kappa_w1,
                         mu_w2 = mu_w2, kappa_w2 = kappa_w2, 
                         sd_percept_precision = sd_percept_precision, 
                         sd_beta = sd_beta)

parameters$id = 1:nrow(parameters)

data_list <- split(parameters, parameters$id)

plan(multisession, workers = availableCores()-1)

data_list = data_list[1:100]

wb_pp = furrr::future_map(data_list, ~parameter_recovery_wb(.x), .progress = TRUE, .options = furrr_options(seed = 123))

```

```{r parameter recovery for Kalman}

mu_sigmaEta = seq(1,100,length.out = 3)
mu_sigmaPsi = seq(1,100,length.out = 3)
mu_sigmaEpsilon = seq(1,100,length.out = 3)

sd_sigmaEta = seq(0.1,10,length.out = 3)
sd_sigmaPsi = seq(0.1,10,length.out = 3)
sd_sigmaEpsilon = seq(0.1,10,length.out = 3)

nsubs = 5

parameters = expand.grid(mu_sigmaEta = mu_sigmaEta,
                         mu_sigmaPsi = mu_sigmaPsi,
                         mu_sigmaEpsilon = mu_sigmaEpsilon,
                         sd_sigmaEta = sd_sigmaEta,
                         sd_sigmaPsi = sd_sigmaPsi,
                         sd_sigmaEpsilon = sd_sigmaEpsilon,
                         nsubs = nsubs)

parameters$id = 1:nrow(parameters)

data_list <- split(parameters, parameters$id)

plan(multisession, workers = availableCores()-1)

data_list = data_list[1:100]

kalman_pp = furrr::future_map(data_list, ~parameter_recovery_kalman(.x), .progress = TRUE, .options = furrr_options(seed = 123))

```

```{r}
#plot parameterrecovery
hier_pp <- do.call(rbind, lapply(rw_dd, "[[", 1))
hier_pp %>% mutate(divergences = ifelse(div > 0,1,0)) %>% 
  ggplot(aes(x = mean, y = reals.reals))+
  geom_point(aes(col = as.factor(divergences)))+
  facet_wrap(~variable, scales = "free")+
  theme_classic()+
  geom_abline(slope = 1, intercept = 0)+
  scale_color_manual("divergence?",values = c("black","red"))

sub_pp <- do.call(rbind, lapply(rw_dd, "[[", 2))
sub_pp %>% mutate(divergences = ifelse(div > 0,1,0)) %>% 
  ggplot(aes(x = mean, y = reals.reals))+
  geom_point(aes(col = as.factor(divergences)))+
  facet_wrap(~variable, scales = "free")+
  theme_classic()+
  geom_abline(slope = 1, intercept = 0)+
  scale_color_manual("divergence?",values = c("black","red"))

```

### 2023-05-19 scripts/agent.R

@@ -186,9 +186,6 @@ our_hier_rw_agent = function(parameters){
 
 
 
-
-
-
 our_kalman_agent = function(parameters){
   
   dd = get_experiment()
@@ -436,7 +433,7 @@ weighted_Bayes_f = function(parameters) {
   }
   
   df = data.frame(u = u[1:ntrials], cue = cue[1:ntrials], stim = stim[1:ntrials], expect = expect[1:ntrials], pred = pred[1:ntrials], perceptmu = perceptmu[1:ntrials], percept_bin = percept_bin[1:ntrials], percept = percept[1:ntrials], association = association[1:ntrials],
-                  pe = pe[1:ntrials], alpha = alpha, w1 = w1, w2 = w2, percept_precision = percept_precision, beta = beta, x = 1:ntrials, desired = rep(bias,1))
+                  pe = pe[1:ntrials], alpha = alpha, w1 = w1, w2 = w2, percept_precision = percept_precision, beta = beta, trial = 1:ntrials, desired = rep(bias,1))
   
   return(df)
   
@@ -490,7 +487,7 @@ weighted_Bayes_f_v2 = function(alpha, w1, w2, percept_precision, beta) {
   }
   
   df = data.frame(u = u[1:ntrials], cue = cue[1:ntrials], stim = stim[1:ntrials], expect = expect[1:ntrials], pred = pred[1:ntrials], perceptmu = perceptmu[1:ntrials], percept_bin = percept_bin[1:ntrials], percept = percept[1:ntrials], association = association[1:ntrials],
-                  pe = pe[1:ntrials], alpha = alpha, w1 = w1, w2 = w2, percept_precision = percept_precision, beta = beta, x = 1:ntrials, desired = rep(bias,1), id = rnorm(1,0,1))
+                  pe = pe[1:ntrials], alpha = alpha, w1 = w1, w2 = w2, percept_precision = percept_precision, beta = beta, trial = 1:ntrials, desired = rep(bias,1), id = rnorm(1,0,1))
   
   return(df)
   

### 2023-05-19 scripts/parameter_recovery.R

@@ -1,13 +1,11 @@
 #parameter_recovery
 
 
-parameter_recovery = function(parameters){
+parameter_recovery_rw = function(parameters){
   
   df = our_hier_rw_agent(parameters)[[1]]
   hier = our_hier_rw_agent(parameters)[[2]]
   
-  
-  source(here::here("stan_functions.R"))
   #fitting hierachically
   data = df %>% filter(id %in% unique(id)[1:nsubs])
   
@@ -27,29 +25,187 @@ parameter_recovery = function(parameters){
                stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
                cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)))
   
-  mod = cmdstan_model(here::here("myRW_real.stan"))
   
-  fit <- mod$sample(
-    data = data1,
-    chains = 4, 
-    parallel_chains = 4,
-    refresh = 100,
-    adapt_delta = 0.80,
-    max_treedepth = 10
-  )
+  mod = cmdstan_model(here::here("Stan","no generated quantities","myRW_real_nogen.stan"))
   
-  index = rnorm(1,0,1)
   
-  hier_parameters = c("kappa_w1","mu_w1","kappa_alpha","mu_alpha","sd_beta","sd_precision_percept")
   
-  sub_parameters = c("w1","alpha","beta","precision_percept")
-  return(list(hier = data.frame(fit$summary(hier_parameters),
-                    reals = hier %>% dplyr::select(all_of(hier_parameters)) %>% pivot_longer(everything()) %>% rename(reals = value),
-                    div = sum(fit$diagnostic_summary()$num_divergent),index = index),
-              sub = data.frame(fit$summary(sub_parameters) %>% arrange(variable),
-                               reals = df %>% filter(trial == 1) %>% mutate(ids = 1:nrow(.)) %>% dplyr::select(all_of(sub_parameters),ids) %>% pivot_longer(cols = -ids) %>% rename(reals =value) %>% mutate(names = paste0(name,"[",ids,"]")) %>% arrange(names) %>% select(names,reals),
-                               div = sum(fit$diagnostic_summary()$num_divergent),index = index)))
+  fitter = function(){
+    fit <- mod$sample(
+      data = data1,
+      chains = 4, 
+      parallel_chains = 4,
+      refresh = 100,
[…]

### 2023-05-19 Manuscript.Rmd
updates

@@
 
-scripts = c("agent.R","parameter_recovery.R","stan_functions.R")
+scripts = c("agent.R","parameter_recovery.R","stan_functions.R","utility functions.R")
 q = lapply(here("scripts", scripts), source)
@@
 ## R Markdown
+
+```{r parameters visualization}
+
+```
 
@@
 
-nsubs = 5
+nsubs = 50
 
@@
 ```
+
+```{r model recovery}
+
+```
+
+```{r model comparison}
+
+```
+
+```{r hierachical session correlation}
+
+df= read.csv(here::here("data_TPL_AC.csv")) %>% 
+  rename_all(tolower) %>% 
+  filter(trial != 0) %>% 
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% 
+  mutate_all(replace_na, 0) %>% mutate(id = as.factor(id), trial = as.factor(trial), session = as.factor(session))
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
+
+#ratings
+df %>% filter(session == 2) %>% ggplot(aes(x = percept, fill = as.factor(stim))) + geom_histogram()
+#cue-contingency
+df %>% filter(session == 1, id == 1) %>% ggplot(aes(x = trial, y = u)) + geom_point()+theme_classic()
+
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data1 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(session == 1) %>% filter(id %in% unique(id)[1])),
+            sesions = length(unique(data$session)),
+            percept = get_3darray(data,variable = "percept"),
+            expectPain = get_3darray(data,variable = "pred"),
+            percept_bin = get_3darray(data,variable = "percept_bin"),
+            stim = get_3darray(data,variable = "stim"),
+            cues = get_3darray(data,variable = "cue"),
+            u = get_3darray(data,variable = "u")
+            )
+
+mod = cmdstan_model(here::here("Stan","fitting both sessions","myRW_correlation.stan"))
+
+fit <- mod$sample(
+  data = data1,
+  chains = 4, 
+  parallel_chains = 4,
+  refresh = 100,
+  adapt_delta = 0.90,
+  max_treedepth = 12
+)
+
+```
+
+```{r fitting to real data tester hierachical RW}
+
+df= read.csv(here::here("data_TPL_AC.csv")) %>% 
+  rename_all(tolower) %>% 
+  filter(trial != 0) %>% 
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% 
+  mutate_all(replace_na, 0)
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
+
+#ratings
+df %>% filter(session == 2) %>% ggplot(aes(x = percept, fill = as.factor(stim))) + geom_histogram()
+#cue-contingency
+df %>% filter(session == 1, id == 1) %>% ggplot(aes(x = trial, y = u)) + geom_point()+theme_classic()
+
+df = df %>% filter(session == 1)
+
+source(here::here("stan_functions.R"))
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data1 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
+            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
+            expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
+            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
+            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)),
+            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL))
+            )
+
+data1 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
+            pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL))
+            )
+
+mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier.stan"))
+
+fit <- mod$sample(
+      data = data1,
+      chains = 4, 
+      parallel_chains = 4,
+      refresh = 100,
+      adapt_delta = 0.90,
+      max_treedepth = 12
+    )
+
+alphas = fit$summary(variables = c("alpha_1","alpha_1_mu"))
+
+```

### 2023-05-19 scripts/agent.R

@@ -23,10 +23,7 @@ get_experiment = function(){
 
 
 
-our_rw_agent = function(parameters){
-  
-
-  dd = get_experiment()
+our_rw_agent = function(parameters,dd){
   
   cue = dd$cue
   stim = dd$stim
@@ -186,9 +183,7 @@ our_hier_rw_agent = function(parameters){
 
 
 
-our_kalman_agent = function(parameters){
-  
-  dd = get_experiment()
+our_kalman_agent = function(parameters,dd){
   
   cue = dd$cue
   stim = dd$stim
@@ -259,7 +254,7 @@ our_kalman_agent = function(parameters){
   
   return(data.frame(exp_mu = exp_mu[1:ntrials], perceptmu = perceptmu, pred = pred, percept = percept,
                     percept_bin = percept_bin, trial = 1:ntrials, stim = stim, u = u, association = association[1:ntrials], cue = cue,
-                    sigmaPsi = sigmaPsi, sigmaEta = sigmaEta, sigmaEpsilon = sigmaEpsilon))
+                    sigmaPsi = sigmaPsi, sigmaEta = sigmaEta, sigmaEpsilon = sigmaEpsilon, desired = rep(bias,1)))
   
   
   
@@ -372,21 +367,15 @@ our_hier_kalman_agent = function(parameters){
 
 
 
-weighted_Bayes_f = function(parameters) {
+weighted_Bayes_f = function(parameters,dd) {
   
-  trials = c(40,40,40,40)
-  bias = rep(c(0.1,0.9,0.1,0.9),trials)
-  ntrials = sum(trials)
+  cue = dd$cue
+  stim = dd$stim
+  u = dd$u
+  bias = dd$bias
   
-  cue = rbinom(sum(trials),1,0.5)
+  ntrials = nrow(dd)
   
-  stim = array(sum(trials, NA))
-  for(i in 1:ntrials){
-    stim[i] = ifelse(cue[i] == 1, rbinom(1,1,bias[i]), rbinom(1,1,(1-bias[i])))
-    
-  }
-  
-  u = ifelse(cue == stim, 1,0)
   dd = data.frame(stim = stim, cue = cue, u = u)
   
   dd %>% ggplot(aes(x = 1:nrow(.), y = u, col = as.factor(stim)))+geom_point()+theme_classic()

### 2023-05-19 scripts/utility functions.R

@@ -1,0 +1,42 @@
+#utility functions
+
+
+
+get_3darray = function(data,variable){
+  if(variable == "percept"){
+    qq  = as.matrix(data %>% filter(session == 1) %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL))
+    qq1  = as.matrix(data %>% filter(session == 2) %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL))
+    qq2 = simplify2array(list(qq,qq1))
+    
+    return(qq2)
+  }else if(variable == "percept_bin"){
+    qq  = as.matrix(data %>% filter(session == 1) %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL))
+    qq1  = as.matrix(data %>% filter(session == 2) %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL))
+    qq2 = simplify2array(list(qq,qq1))
+    return(qq2)
+  }else if(variable == "pred"){
+    qq  = as.matrix(data %>% filter(session == 1) %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL))
+    qq1  = as.matrix(data %>% filter(session == 2) %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL))
+    qq2 = simplify2array(list(qq,qq1))
+    return(qq2)
+  }else if(variable == "stim"){
+    qq  = as.matrix(data %>% filter(session == 1) %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL))
+    qq1  = as.matrix(data %>% filter(session == 2) %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL))
+    qq2 = simplify2array(list(qq,qq1))
+    return(qq2)
+    
+  }else if(variable == "cue"){
+    qq  = as.matrix(data %>% filter(session == 1) %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL))
[…]

### 2023-05-20 Manuscript.Rmd
updates

@@
 knitr::opts_chunk$set(echo = TRUE)
-pacman::p_load(tidyverse, osfr, lmerTest, MuMIn, DHARMa, here, cmdstanr, tidybayes, bayesplot, posterior,future,furrr, patchwork, R.utils, brms)
+pacman::p_load(tidyverse, osfr, lmerTest, MuMIn, DHARMa, here, cmdstanr, tidybayes, bayesplot, posterior,future,furrr, patchwork, R.utils, brms, extraDistr)
 
-scripts = c("agent.R","parameter_recovery.R","stan_functions.R","utility functions.R")
+scripts = c("agent.R","parameter_recovery.R","stan_functions.R","utility functions.R", "model recovery.R")
 q = lapply(here("scripts", scripts), source)
@@
 ```{r model recovery}
+########################################### Resorla wagner parameters:
+mu_alpha = seq(0.1,0.3,length.out = 10)
+kappa_alpha = 50
+mu_w1 = seq(0.1,0.3,length.out = 10)
+kappa_w1 = 50
+sd_precision_percept = 0.5
+sd_beta = 0.5
+nsubs = 10
+parameters = expand.grid(mu_alpha = mu_alpha,
+                         kappa_alpha = kappa_alpha,
+                         mu_w1 = mu_w1,
+                         kappa_w1 = kappa_w1,
+                         sd_precision_percept = sd_precision_percept,
+                         sd_beta = sd_beta,
+                         nsubs = nsubs)
+
+parameters$id = 1:nrow(parameters)
+data_list_rw <- split(parameters, parameters$id)
+
+######################################## Weighted bayes
+
+mu_alpha = rep(0.2,100)
+kappa_alpha = 50
+mu_w1 = 0.2
+kappa_w1 = 50
+mu_w2 = 0.2
+kappa_w2 = 50
+sd_percept_precision = 0.5
+sd_beta = 0.5
+nsubs = 50
+parameters = expand.grid(nsubs = nsubs, 
+                         mu_alpha = mu_alpha, 
+                         kappa_alpha = kappa_alpha, 
+                         mu_w1 =  mu_w1, kappa_w1 = kappa_w1,
+                         mu_w2 = mu_w2, kappa_w2 = kappa_w2, 
+                         sd_percept_precision = sd_percept_precision, 
+                         sd_beta = sd_beta)
+parameters$id = 1:nrow(parameters)
+data_list_wb <- split(parameters, parameters$id)
+
+######################################### Kalman
+
+mu_sigmaEta = rep(50,100)
+mu_sigmaPsi = 10
+mu_sigmaEpsilon = 0.1
+sd_sigmaEta = 0.1
+sd_sigmaPsi = 0.1
+sd_sigmaEpsilon = 0.1
+nsubs = 50
+parameters = expand.grid(mu_sigmaEta = mu_sigmaEta,
+                         mu_sigmaPsi = mu_sigmaPsi,
+                         mu_sigmaEpsilon = mu_sigmaEpsilon,
+                         sd_sigmaEta = sd_sigmaEta,
+                         sd_sigmaPsi = sd_sigmaPsi,
+                         sd_sigmaEpsilon = sd_sigmaEpsilon,
+                         nsubs = nsubs)
+parameters$id = 1:nrow(parameters)
+data_list_kalman <- split(parameters, parameters$id)
+
+######################################### fit data_rw:
+#loos = model_fitter_rwdata(data_list_rw[[1]])
+
+data_list = data_list_rw[1:3]
+
+plan(multisession, workers = 5)
+
+rw_loo = furrr::future_map(data_list, ~model_fitter_rwdata(.x), .progress = TRUE, .options = furrr_options(seed = 123))
 
@@
 
+sum = fit$summary(variables = c("mu_alpha","mu_w1","sd_beta","sd_precision_percept", "kappa_alpha","kappa_w1","alpha","w1","beta","precision_percept"))
+
+variabless = c("mu_alpha[1]","mu_w1[1]","sd_beta[1]","sd_precision_percept[1]","mu_alpha[2]","mu_w1[2]","sd_beta[2]","sd_precision_percept[2]")
+
+pairs = mcmc_pairs(fit$draws(variables = variabless), np = nuts_params(fit), pars = variabless,
+                   off_diag_args = list(size = 0.75))
 ```

### 2023-05-20 scripts/model recovery.R

@@ -1,0 +1,190 @@
+#model recovery
+
+
+
+model_fitter_rwdata = function(parameters_rw){
+  
+  
+  df_rw = our_hier_rw_agent(parameters_rw)[[1]]
+  
+  #fitting hierachically
+  data_rw = df_rw %>% filter(id %in% unique(id)[1:nsubs])
+  
+  data_rw = data_rw %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+  
+  
+  data1_rw = list(nsubs = length(unique(data_rw$id)),
+               ntrials = nrow(data_rw %>% filter(id %in% unique(id)[1])),
+               percept = as.matrix(data_rw %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
+               expectPain = as.matrix(data_rw %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+               percept_bin = as.matrix(data_rw %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
+               stim = as.matrix(data_rw %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
+               cues = as.matrix(data_rw %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)))
+  
+
+  
+  
+  
+  rw_model = here::here("Stan","myRW_real.stan")
+  wb_model = here::here("Stan","hier_weighted_bayes.stan")
+  kalman_model = here::here("Stan","myKalmanfilter.stan")
+  
+  
+  data1_rw_wb = data1_rw
+  
+  names(data1_rw_wb) = c("nsubs","ntrials","percept","pred","percept_bin","stim","cue")
+  data1_rw_wb$stim = ifelse(data1_rw_wb$stim == 1, 0.999, 0.001)
+  
+  data1_rw_kalman$u = as.matrix(data_rw %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL))
+  
+  
+  loo_rw_rw = get_loo(rw_model, data1_rw)
+  loo_rw_wb = get_loo(wb_model, data1_rw_wb)
+  loo_rw_kalman = get_loo(kalman_model, data1_rw_kalman)
+  
[…]

### 2023-05-20 scripts/parameter_recovery.R

@@ -94,6 +94,10 @@ parameter_recovery_wb = function(parameters){
                stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
                cue = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)))
   
+  
+  
+  
+
   mod = cmdstan_model(here::here("Stan","no generated quantities","hier_weighted_bayes_nogen.stan"))
   
   

### 2023-05-20 Manuscript.Rmd
updates

@@
 sd_beta = 0.5
-nsubs = 50
+nsubs = 10
 parameters = expand.grid(nsubs = nsubs, 
@@
 
-mu_sigmaEta = rep(50,100)
-mu_sigmaPsi = 10
-mu_sigmaEpsilon = 0.1
+mu_sigmaEta = rep(0.1,100)
+mu_sigmaPsi = 0.1
+mu_sigmaEpsilon = 2
 sd_sigmaEta = 0.1
@@
 sd_sigmaEpsilon = 0.1
-nsubs = 50
+nsubs = 10
 parameters = expand.grid(mu_sigmaEta = mu_sigmaEta,
@@
 
-data_list = data_list_rw[1:3]
+data_list = data_list_rw[1:5]
 
@@
 
-```
+elpld_loo <- map_dfr(rw_loo, ~ .x[[1]])
 
-```{r model comparison}
+full_loo <- map_dfr(rw_loo, ~ .x[[2]])
+
+########################################## fit data_wb
+
+data_list = data_list_wb[1]
+
+plan(multisession, workers = 5)
+
+wb_loo = furrr::future_map(data_list, ~model_fitter_wbdata(.x), .progress = TRUE, .options = furrr_options(seed = 123))
+
+elpld_loo <- map_dfr(wb_loo, ~ .x[[1]])
+
+full_loo <- map_dfr(wb_loo, ~ .x[[2]])
+
+########################################### fit kalman data
+
+data_list = data_list_kalman[1]
+
+plan(multisession, workers = 5)
+
+kalman_loo = furrr::future_map(data_list, ~model_fitter_kalmandata(.x), .progress = TRUE, .options = furrr_options(seed = 123))
+
+elpld_loo <- map_dfr(kalman_loo, ~ .x[[1]])
+
+full_loo <- map_dfr(kalman_loo, ~ .x[[2]])
 
@@
 
-```{r hierachical session correlation}
-
+```{r fitting RW model to session 1}
 df= read.csv(here::here("data_TPL_AC.csv")) %>% 
@@
   rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% 
-  mutate_all(replace_na, 0) %>% mutate(id = as.factor(id), trial = as.factor(trial), session = as.factor(session))
+  mutate_all(replace_na, 0)
 
 df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
-df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
 
@@
 df %>% filter(session == 1, id == 1) %>% ggplot(aes(x = trial, y = u)) + geom_point()+theme_classic()
+
+df = df %>% filter(session == 1)
 
@@
 data1 = list(nsubs = length(unique(data$id)),
-            ntrials = nrow(data %>% filter(session == 1) %>% filter(id %in% unique(id)[1])),
-            sesions = length(unique(data$session)),
-            percept = get_3darray(data,variable = "percept"),
-            expectPain = get_3darray(data,variable = "pred"),
-            percept_bin = get_3darray(data,variable = "percept_bin"),
-            stim = get_3darray(data,variable = "stim"),
-            cues = get_3darray(data,variable = "cue"),
-            u = get_3darray(data,variable = "u")
-            )
+            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
+            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
+            expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
+            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
+            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)))
 
-mod = cmdstan_model(here::here("Stan","fitting both sessions","myRW_correlation.stan"))
+mod = cmdstan_model(here::here("Stan","myRW_real.stan"))
 
-fit <- mod$sample(
+rw_fit_sess1 <- mod$sample(
       data = data1,
@@
     )
-
-sum = fit$summary(variables = c("mu_alpha","mu_w1","sd_beta","sd_precision_percept", "kappa_alpha","kappa_w1","alpha","w1","beta","precision_percept"))
-
-variabless = c("mu_alpha[1]","mu_w1[1]","sd_beta[1]","sd_precision_percept[1]","mu_alpha[2]","mu_w1[2]","sd_beta[2]","sd_precision_percept[2]")
-
-pairs = mcmc_pairs(fit$draws(variables = variabless), np = nuts_params(fit), pars = variabless,
-                   off_diag_args = list(size = 0.75))
 ```
 
-```{r fitting to real data tester hierachical RW}
-
+```{r fitting RW model to session 2}
 df= read.csv(here::here("data_TPL_AC.csv")) %>% 
@@
 df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
-df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
 
@@
 
+df = df %>% filter(session == 2)
+
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data1 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
+            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
+            expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
+            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
+            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)))
+
+mod = cmdstan_model(here::here("Stan","myRW_real.stan"))
+
+rw_fit_sess2 <- mod$sample(
+      data = data1,
+      chains = 4, 
+      parallel_chains = 4,
+      refresh = 100,
+      adapt_delta = 0.90,
+      max_treedepth = 12
+    )
+```
+
+```{r fitting Kalman model to session 1}
+df= read.csv(here::here("data_TPL_AC.csv")) %>% 
+  rename_all(tolower) %>% 
+  filter(trial != 0) %>% 
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% 
+  mutate_all(replace_na, 0)
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+
 df = df %>% filter(session == 1)
 
-source(here::here("stan_functions.R"))
 #fitting hierachically
@@
 
+mod = cmdstan_model(here::here("Stan","myKalmanfilter.stan"))
+
+kalman_fit_sess1 <- mod$sample(
+      data = data1,
+      chains = 4, 
+      parallel_chains = 4,
+      refresh = 100,
+      adapt_delta = 0.90,
+      max_treedepth = 12
+    )
+```
+
+```{r fitting Kalman model to session 2}
+df= read.csv(here::here("data_TPL_AC.csv")) %>% 
+  rename_all(tolower) %>% 
+  filter(trial != 0) %>% 
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% 
+  mutate_all(replace_na, 0)
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+
+df = df %>% filter(session == 2)
+
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
 data1 = list(nsubs = length(unique(data$id)),
             ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
-            pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
+            expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
+            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
+            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)),
             u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL))
@@
 
-mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier.stan"))
+mod = cmdstan_model(here::here("Stan","myKalmanfilter.stan"))
+
+kalman_fit_sess1 <- mod$sample(
+      data = data1,
+      chains = 4, 
+      parallel_chains = 4,
+      refresh = 100,
+      adapt_delta = 0.90,
+      max_treedepth = 12
+    )
+```
+
+```{r fitting WB model to session 1}
+df= read.csv(here::here("data_TPL_AC.csv")) %>% 
+  rename_all(tolower) %>% 
+  filter(trial != 0) %>% 
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% 
+  mutate_all(replace_na, 0)
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+
+df = df %>% filter(session == 1)
+
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(c(percept,stim), ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data1 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
+            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
+            pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
+            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
+            cue = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL))
+            )
+
+mod = cmdstan_model(here::here("Stan","hier_weighted_bayes.stan"))
+
+fit <- mod$sample(
+      data = data1,
+      chains = 4, 
+      parallel_chains = 4,
+      refresh = 100,
+      adapt_delta = 0.90,
+      max_treedepth = 12
+    )
+```
+
+```{r fitting WB model to session 2}
+
+df= read.csv(here::here("data_TPL_AC.csv")) %>% 
+  rename_all(tolower) %>% 
+  filter(trial != 0) %>% 
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% 
+  mutate_all(replace_na, 0)
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+
+df = df %>% filter(session == 2)
+
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(c(percept,stim), ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data1 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
+            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
+            pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
+            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
+            cue = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL))
+            )
+
+mod = cmdstan_model(here::here("Stan","hier_weighted_bayes.stan"))
 
@@
 
-alphas = fit$summary(variables = c("alpha_1","alpha_1_mu"))
+```
 
-```
+<!-- ```{r hierachical session correlation} -->
+
+<!-- df= read.csv(here::here("data_TPL_AC.csv")) %>% -->
+<!--   rename_all(tolower) %>% -->
+<!--   filter(trial != 0) %>% -->
+<!--   rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% -->
+<!--   mutate_all(replace_na, 0) %>% mutate(id = as.factor(id), trial = as.factor(trial), session = as.factor(session)) -->
+
+<!-- df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0)) -->
+<!-- df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0)) -->
+
+<!-- #ratings -->
+<!-- df %>% filter(session == 2) %>% ggplot(aes(x = percept, fill = as.factor(stim))) + geom_histogram() -->
+<!-- #cue-contingency -->
+<!-- df %>% filter(session == 1, id == 1) %>% ggplot(aes(x = trial, y = u)) + geom_point()+theme_classic() -->
+
+<!-- #fitting hierachically -->
+<!-- data = df %>% mutate(percept = percept/100) -->
+
+<!-- data = data %>% mutate(across(percept, ~case_when( -->
+<!--     . < 0.001 ~ 0.001, -->
+<!--     . > 0.999 ~ 0.999, -->
+<!--     TRUE ~ . -->
+<!--   ))) -->
+
+<!-- data1 = list(nsubs = length(unique(data$id)), -->
+<!--             ntrials = nrow(data %>% filter(session == 1) %>% filter(id %in% unique(id)[1])), -->
+<!--             sesions = length(unique(data$session)), -->
+<!--             percept = get_3darray(data,variable = "percept"), -->
+<!--             expectPain = get_3darray(data,variable = "pred"), -->
+<!--             percept_bin = get_3darray(data,variable = "percept_bin"), -->
+<!--             stim = get_3darray(data,variable = "stim"), -->
+<!--             cues = get_3darray(data,variable = "cue"), -->
+<!--             u = get_3darray(data,variable = "u") -->
+<!--             ) -->
+
+<!-- mod = cmdstan_model(here::here("Stan","fitting both sessions","myRW_correlation.stan")) -->
+
+<!-- fit <- mod$sample( -->
+<!--   data = data1, -->
+<!--   chains = 4, -->
+<!--   parallel_chains = 4, -->
+<!--   refresh = 100, -->
+<!--   adapt_delta = 0.90, -->
+<!--   max_treedepth = 12 -->
+<!-- ) -->
+
+<!-- sum = fit$summary(variables = c("mu_alpha","mu_w1","sd_beta","sd_precision_percept", "kappa_alpha","kappa_w1","alpha","w1","beta","precision_percept")) -->
+
+<!-- variabless = c("mu_alpha[1]","mu_w1[1]","sd_beta[1]","sd_precision_percept[1]","mu_alpha[2]","mu_w1[2]","sd_beta[2]","sd_precision_percept[2]") -->
+
+<!-- pairs = mcmc_pairs(fit$draws(variables = variabless), np = nuts_params(fit), pars = variabless, -->
+<!--                    off_diag_args = list(size = 0.75)) -->
+<!-- ``` -->
+
+<!-- ```{r fitting to real data tester hierachical RW session 1} -->
+
+<!-- df= read.csv(here::here("data_TPL_AC.csv")) %>%  -->
+<!--   rename_all(tolower) %>%  -->
+<!--   filter(trial != 0) %>%  -->
+<!--   rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%  -->
+<!--   mutate_all(replace_na, 0) -->
+
+<!-- df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0)) -->
+<!-- df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0)) -->
+
+<!-- #ratings -->
+<!-- df %>% filter(session == 2) %>% ggplot(aes(x = percept, fill = as.factor(stim))) + geom_histogram() -->
+<!-- #cue-contingency -->
+<!-- df %>% filter(session == 1, id == 1) %>% ggplot(aes(x = trial, y = u)) + geom_point()+theme_classic() -->
+
+<!-- df = df %>% filter(session == 1) -->
+
+<!-- source(here::here("stan_functions.R")) -->
+<!-- #fitting hierachically -->
+<!-- data = df %>% mutate(percept = percept/100) -->
+
+<!-- data = data %>% mutate(across(percept, ~case_when( -->
+<!--     . < 0.001 ~ 0.001, -->
+<!--     . > 0.999 ~ 0.999, -->
+<!--     TRUE ~ . -->
+<!--   ))) -->
+
+<!-- data1 = list(nsubs = length(unique(data$id)), -->
+<!--             ntrials = nrow(data %>% filter(id %in% unique(id)[1])), -->
+<!--             percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)), -->
+<!--             expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)), -->
+<!--             percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)), -->
+<!--             stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)), -->
+<!--             cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)), -->
+<!--             u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL)) -->
+<!--             ) -->
+
+<!-- data1 = list(nsubs = length(unique(data$id)), -->
+<!--             ntrials = nrow(data %>% filter(id %in% unique(id)[1])), -->
+<!--             pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)), -->
+<!--             u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL)) -->
+<!--             ) -->
+
+<!-- mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier.stan")) -->
+
+<!-- rw_fit_ses1 <- mod$sample( -->
+<!--       data = data1, -->
+<!--       chains = 4,  -->
+<!--       parallel_chains = 4, -->
+<!--       refresh = 100, -->
+<!--       adapt_delta = 0.90, -->
+<!--       max_treedepth = 12 -->
+<!--     ) -->
+<!-- ``` -->
+
+<!-- ```{r fitting to real data tester hierachical RW seesion2} -->
+
+<!-- df= read.csv(here::here("data_TPL_AC.csv")) %>%  -->
+<!--   rename_all(tolower) %>%  -->
+<!--   filter(trial != 0) %>%  -->
+<!--   rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%  -->
+<!--   mutate_all(replace_na, 0) -->
+
+<!-- df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0)) -->
+<!-- df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0)) -->
+
+<!-- #ratings -->
+<!-- df %>% filter(session == 2) %>% ggplot(aes(x = percept, fill = as.factor(stim))) + geom_histogram() -->
+<!-- #cue-contingency -->
+<!-- df %>% filter(session == 1, id == 1) %>% ggplot(aes(x = trial, y = u)) + geom_point()+theme_classic() -->
+
+<!-- df = df %>% filter(session == 2) -->
+
+<!-- source(here::here("stan_functions.R")) -->
+<!-- #fitting hierachically -->
+<!-- data = df %>% mutate(percept = percept/100) -->
+
+<!-- data = data %>% mutate(across(percept, ~case_when( -->
+<!--     . < 0.001 ~ 0.001, -->
+<!--     . > 0.999 ~ 0.999, -->
+<!--     TRUE ~ . -->
+<!--   ))) -->
+
+<!-- data1 = list(nsubs = length(unique(data$id)), -->
+<!--             ntrials = nrow(data %>% filter(id %in% unique(id)[1])), -->
+<!--             percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)), -->
+<!--             expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)), -->
+<!--             percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)), -->
+<!--             stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)), -->
+<!--             cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)), -->
+<!--             u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL)) -->
+<!--             ) -->
+
+<!-- data1 = list(nsubs = length(unique(data$id)), -->
+<!--             ntrials = nrow(data %>% filter(id %in% unique(id)[1])), -->
+<!--             pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)), -->
+<!--             u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL)) -->
+<!--             ) -->
+
+<!-- mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier.stan")) -->
+
+<!-- rw_fit_ses2 <- mod$sample( -->
+<!--       data = data1, -->
+<!--       chains = 4,  -->
+<!--       parallel_chains = 4, -->
+<!--       refresh = 100, -->
+<!--       adapt_delta = 0.90, -->
+<!--       max_treedepth = 12 -->
+<!--     ) -->
+<!-- ``` -->

### 2023-05-20 scripts/agent.R

@@ -190,8 +190,6 @@ our_kalman_agent = function(parameters,dd){
   u = dd$u
   bias = dd$bias
   
-  
-  
   ntrials = nrow(dd)
   
   percept = array(NA, ntrials)
@@ -213,11 +211,13 @@ our_kalman_agent = function(parameters,dd){
   association = array(NA,ntrials)
   
   association[1] = 0.5
-  exp_var[1] = 2
+  
   
   sigmaEta = parameters$sigmaEta
   sigmaEpsilon = parameters$sigmaEpsilon
   sigmaPsi = parameters$sigmaPsi
+  
+  exp_var[1] = sigmaEta
   
   for(t in 1:ntrials){
     
@@ -231,7 +231,7 @@ our_kalman_agent = function(parameters,dd){
     
     
     perceptmu[t] =  (sigmaEpsilon * exp_mu[t] + (sigmaPsi + exp_var[t]) * stim[t] ) / 
-      (sigmaEpsilon + sigmaPsi + exp_var[t]);
+      (sigmaEpsilon + sigmaPsi + exp_var[t])
     
     perceptvar[t] = ( sigmaEpsilon * (sigmaPsi + exp_var[t]) ) / (sigmaEpsilon + sigmaPsi + exp_var[t])
     
@@ -254,12 +254,97 @@ our_kalman_agent = function(parameters,dd){
   
   return(data.frame(exp_mu = exp_mu[1:ntrials], perceptmu = perceptmu, pred = pred, percept = percept,
                     percept_bin = percept_bin, trial = 1:ntrials, stim = stim, u = u, association = association[1:ntrials], cue = cue,
-                    sigmaPsi = sigmaPsi, sigmaEta = sigmaEta, sigmaEpsilon = sigmaEpsilon, desired = rep(bias,1)))
+                    sigmaPsi = sigmaPsi, sigmaEta = sigmaEta, sigmaEpsilon = sigmaEpsilon, desired = rep(bias,1),exp_var = exp_var[1:ntrials], perceptvar = perceptvar[1:ntrials]))
   
   
   
   
 }
+
+
+our_kalman_agent22 = function(parameters,dd){
+  
+  cue = dd$cue
+  stim = dd$stim
+  u = dd$u
+  bias = dd$bias
+  
+  ntrials = nrow(dd)
+  
+  percept = array(NA, ntrials)
[…]

### 2023-05-20 scripts/model recovery.R

@@ -1,7 +1,6 @@
 #model recovery
 
 
-
 model_fitter_rwdata = function(parameters_rw){
   
   
@@ -25,7 +24,7 @@ model_fitter_rwdata = function(parameters_rw){
                stim = as.matrix(data_rw %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
                cues = as.matrix(data_rw %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)))
   
-
+  id = rnorm(1,0,1)
   
   
   
@@ -35,6 +34,7 @@ model_fitter_rwdata = function(parameters_rw){
   
   
   data1_rw_wb = data1_rw
+  data1_rw_kalman = data1_rw
   
   names(data1_rw_wb) = c("nsubs","ntrials","percept","pred","percept_bin","stim","cue")
   data1_rw_wb$stim = ifelse(data1_rw_wb$stim == 1, 0.999, 0.001)
@@ -47,14 +47,15 @@ model_fitter_rwdata = function(parameters_rw){
   loo_rw_kalman = get_loo(kalman_model, data1_rw_kalman)
   
   
-  comparison = loo_compare(list(loo_rw_rw[[3]],loo_rw_wb[[3]],loo_rw_kalman[[3]]))
-  
+  comparison = data.frame(loo_compare(list(loo_rw_rw[[3]],loo_rw_wb[[3]],loo_rw_kalman[[3]])))
+  comparison$id = id
 
   return(list(data.frame(names = c("rw",
                                    "wb",
                                    "kalman"),
                          means = c(loo_rw_rw[[1]],loo_rw_wb[[1]],loo_rw_kalman[[1]]),
-                         sds = c(loo_rw_rw[[2]],loo_rw_wb[[2]],loo_rw_kalman[[2]])),
+                         sds = c(loo_rw_rw[[2]],loo_rw_wb[[2]],loo_rw_kalman[[2]]),
+                         id = id),
               comparison))
 }
 
@@ -73,6 +74,7 @@ model_fitter_wbdata = function(parameters_wb){
     TRUE ~ .
   )))
   
+  data_wb$stim = ifelse(data_wb$stim > 0.5, 1, 0)
   
   data1_wb = list(nsubs = length(unique(data_wb$id)),
[…]

### 2023-05-20 visualize_parameters.R

@@ -1,0 +1,183 @@
+#visualize parameters
+
+
+RW = function(){
+  
+  
+  scripts = c("agent.R","parameter_recovery.R","stan_functions.R")
+  q = lapply(here("scripts", scripts), source)
+  alpha = seq(0.1,0.5,by = 0.1)
+  w1 = seq(0.1,0.5,by = 0.1)
+  #precision_percept = seq(10,100,50)
+  #beta = seq(1,50,20)
+  
+  beta = 1
+  precision_percept = seq(10,300,length.out = 3)
+  
+  parameters = expand.grid(alpha = alpha,w1 =  w1, precision_percept = precision_percept, beta = beta)
+  
+  
+  
+  parameters$id = 1:nrow(parameters)
+  
+  data_list <- split(parameters, parameters$id)
+  
+  plan(multisession, workers = 12)
+  
+  
+  dd = get_experiment()
+  
+  
+  dd = furrr::future_map_dfr(data_list, ~our_rw_agent(.x, dd), .progress = TRUE, .options = furrr_options(seed = 123))
+  
+  dd$stim = as.factor(dd$stim)
+  dd$precision_percept = as.factor(dd$precision_percept)
+  
+  
+  plot1 = dd %>% 
+    ggplot()+
+    geom_line(aes(x = trial, y = association))+
+    geom_point(aes(x = trial, y = u), col = "blue")+
+    geom_line(aes(x = trial, y = desired))+
+    facet_grid(alpha~w1, labeller = label_both)+
+    theme_classic()+
+    scale_y_continuous("Cue-stimulus association", breaks = scales::pretty_breaks(n = 5))+
+    scale_x_continuous("Trial", breaks = scales::pretty_breaks(n = 5))
+  
+  
+  plot2 = dd %>% ggplot(aes(exp, y = percept,col = precision_percept, group = interaction(stim, precision_percept)))+
+    geom_point()+
+    facet_grid(alpha~w1, labeller = label_both)+
+    geom_smooth(method = "lm")+
+    theme_classic()+
+    scale_y_continuous("Mean of percept", breaks = scales::pretty_breaks(n = 5))+
+    scale_x_continuous("% belief of Stimulus being Hot", breaks = scales::pretty_breaks(n = 5))
+  
+ 
+  plot1+plot2+plot_layout(guides = 'collect')
+   
+}
+
+
[…]

### 2023-05-21 Manuscript.Rmd
updates

@@
 
-scripts = c("agent.R","parameter_recovery.R","stan_functions.R","utility functions.R", "model recovery.R")
+scripts = c("agent.R","parameter_recovery.R","stan_functions.R","utility functions.R", "model recovery.R","visualize_parameters.R")
 q = lapply(here("scripts", scripts), source)
@@
 ```{r parameters visualization}
+RW()
 
@@
 
-nsubs = 50
+nsubs = 10
 
@@
 
-plan(multisession, workers = availableCores()-1)
+plan(multisession, workers = 3)
 
-data_list = data_list[1:100]
+data_list1 = data_list[501:600]
 
@@
     )
+
+rw_fit_sess1$diagnostic_summary()
 ```
@@
     )
+
+rw_fit_sess2$diagnostic_summary()
+
 ```
 
-```{r fitting Kalman model to session 1}
-df= read.csv(here::here("data_TPL_AC.csv")) %>% 
-  rename_all(tolower) %>% 
-  filter(trial != 0) %>% 
-  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% 
-  mutate_all(replace_na, 0)
+<!-- ```{r fitting Kalman model to session 1} -->
+<!-- df= read.csv(here::here("data_TPL_AC.csv")) %>%  -->
+<!--   rename_all(tolower) %>%  -->
+<!--   filter(trial != 0) %>%  -->
+<!--   rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%  -->
+<!--   mutate_all(replace_na, 0) -->
 
-df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+<!-- df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0)) -->
 
-df = df %>% filter(session == 1)
+<!-- df = df %>% filter(session == 1) -->
 
-#fitting hierachically
-data = df %>% mutate(percept = percept/100)
+<!-- #fitting hierachically -->
+<!-- data = df %>% mutate(percept = percept/100) -->
 
-data = data %>% mutate(across(percept, ~case_when(
-    . < 0.001 ~ 0.001,
-    . > 0.999 ~ 0.999,
-    TRUE ~ .
-  )))
+<!-- data = data %>% mutate(across(percept, ~case_when( -->
+<!--     . < 0.001 ~ 0.001, -->
+<!--     . > 0.999 ~ 0.999, -->
+<!--     TRUE ~ . -->
+<!--   ))) -->
 
-data1 = list(nsubs = length(unique(data$id)),
-            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
-            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
-            expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
-            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
-            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
-            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)),
-            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL))
-            )
+<!-- data1 = list(nsubs = length(unique(data$id)), -->
+<!--             ntrials = nrow(data %>% filter(id %in% unique(id)[1])), -->
+<!--             percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)), -->
+<!--             expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)), -->
+<!--             percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)), -->
+<!--             stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)), -->
+<!--             cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)), -->
+<!--             u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL)) -->
+<!--             ) -->
 
-mod = cmdstan_model(here::here("Stan","myKalmanfilter.stan"))
+<!-- mod = cmdstan_model(here::here("Stan","myKalmanfilter.stan")) -->
 
-kalman_fit_sess1 <- mod$sample(
-      data = data1,
-      chains = 4, 
-      parallel_chains = 4,
-      refresh = 100,
-      adapt_delta = 0.90,
-      max_treedepth = 12
-    )
-```
+<!-- kalman_fit_sess1 <- mod$sample( -->
+<!--       data = data1, -->
+<!--       chains = 4,  -->
+<!--       parallel_chains = 4, -->
+<!--       refresh = 100, -->
+<!--       adapt_delta = 0.90, -->
+<!--       max_treedepth = 12 -->
+<!--     ) -->
+<!-- ``` -->
 
-```{r fitting Kalman model to session 2}
-df= read.csv(here::here("data_TPL_AC.csv")) %>% 
-  rename_all(tolower) %>% 
-  filter(trial != 0) %>% 
-  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% 
-  mutate_all(replace_na, 0)
+<!-- ```{r fitting Kalman model to session 2} -->
+<!-- df= read.csv(here::here("data_TPL_AC.csv")) %>%  -->
+<!--   rename_all(tolower) %>%  -->
+<!--   filter(trial != 0) %>%  -->
+<!--   rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%  -->
+<!--   mutate_all(replace_na, 0) -->
 
-df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+<!-- df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0)) -->
 
-df = df %>% filter(session == 2)
+<!-- df = df %>% filter(session == 2) -->
 
-#fitting hierachically
-data = df %>% mutate(percept = percept/100)
+<!-- #fitting hierachically -->
+<!-- data = df %>% mutate(percept = percept/100) -->
 
-data = data %>% mutate(across(percept, ~case_when(
-    . < 0.001 ~ 0.001,
-    . > 0.999 ~ 0.999,
-    TRUE ~ .
-  )))
+<!-- data = data %>% mutate(across(percept, ~case_when( -->
+<!--     . < 0.001 ~ 0.001, -->
+<!--     . > 0.999 ~ 0.999, -->
+<!--     TRUE ~ . -->
+<!--   ))) -->
 
-data1 = list(nsubs = length(unique(data$id)),
-            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
-            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
-            expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
-            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
-            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
-            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)),
-            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL))
-            )
+<!-- data1 = list(nsubs = length(unique(data$id)), -->
+<!--             ntrials = nrow(data %>% filter(id %in% unique(id)[1])), -->
+<!--             percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)), -->
+<!--             expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)), -->
+<!--             percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)), -->
+<!--             stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)), -->
+<!--             cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)), -->
+<!--             u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL)) -->
+<!--             ) -->
 
-mod = cmdstan_model(here::here("Stan","myKalmanfilter.stan"))
+<!-- mod = cmdstan_model(here::here("Stan","myKalmanfilter.stan")) -->
 
-kalman_fit_sess1 <- mod$sample(
-      data = data1,
-      chains = 4, 
-      parallel_chains = 4,
-      refresh = 100,
-      adapt_delta = 0.90,
-      max_treedepth = 12
-    )
-```
+<!-- kalman_fit_sess1 <- mod$sample( -->
+<!--       data = data1, -->
+<!--       chains = 4,  -->
+<!--       parallel_chains = 4, -->
+<!--       refresh = 100, -->
+<!--       adapt_delta = 0.90, -->
+<!--       max_treedepth = 12 -->
+<!--     ) -->
+<!-- ``` -->
 
@@
 
-fit <- mod$sample(
+wb_fit_sess1  <- mod$sample(
       data = data1,
@@
 
+w7b_fit_sess2 <- mod$sample(
+      data = data1,
+      chains = 4, 
+      parallel_chains = 4,
+      refresh = 100,
+      adapt_delta = 0.90,
+      max_treedepth = 12
+    )
+
+```
+
+```{r hierachical session correlation (RW)}
+
+df= read.csv(here::here("data_TPL_AC.csv")) %>%
+  rename_all(tolower) %>%
+  filter(trial != 0) %>%
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
+  mutate_all(replace_na, 0) %>% mutate(id = as.factor(id), trial = as.factor(trial), session = as.factor(session))
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
+
+#ratings
+df %>% filter(session == 2) %>% ggplot(aes(x = percept, fill = as.factor(stim))) + geom_histogram()
+#cue-contingency
+df %>% filter(session == 1, id == 1) %>% ggplot(aes(x = trial, y = u)) + geom_point()+theme_classic()
+
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data1 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(session == 1) %>% filter(id %in% unique(id)[1])),
+            sesions = length(unique(data$session)),
+            percept = get_3darray(data,variable = "percept"),
+            expectPain = get_3darray(data,variable = "pred"),
+            percept_bin = get_3darray(data,variable = "percept_bin"),
+            stim = get_3darray(data,variable = "stim"),
+            cues = get_3darray(data,variable = "cue"),
+            u = get_3darray(data,variable = "u")
+            )
+
+mod = cmdstan_model(here::here("Stan","fitting both sessions","myRW_correlation.stan"))
+
+fit <- mod$sample(
+  data = data1,
+  chains = 4,
+  parallel_chains = 4,
+  refresh = 100,
+  adapt_delta = 0.90,
+  max_treedepth = 12
+)
+
+sum = fit$summary(variables = c("mu_alpha","mu_w1","sd_beta","sd_precision_percept", "kappa_alpha","kappa_w1","alpha","w1","beta","precision_percept"))
+
+variabless = c("mu_alpha[1]","mu_w1[1]","sd_beta[1]","sd_precision_percept[1]","mu_alpha[2]","mu_w1[2]","sd_beta[2]","sd_precision_percept[2]")
+
+pairs = mcmc_pairs(fit$draws(variables = variabless), np = nuts_params(fit), pars = variabless,
+                   off_diag_args = list(size = 0.75))
+```
+
+```{r hierachical session correlation (WB)}
+
+df= read.csv(here::here("data_TPL_AC.csv")) %>%
+  rename_all(tolower) %>%
+  filter(trial != 0) %>%
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
+  mutate_all(replace_na, 0) %>% mutate(id = as.factor(id), trial = as.factor(trial), session = as.factor(session))
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
+
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(c(percept,stim), ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data1 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(session == 1) %>% filter(id %in% unique(id)[1])),
+            sesions = length(unique(data$session)),
+            percept = get_3darray(data,variable = "percept"),
+            pred = get_3darray(data,variable = "pred"),
+            percept_bin = get_3darray(data,variable = "percept_bin"),
+            stim = get_3darray(data,variable = "stim"),
+            cue = get_3darray(data,variable = "cue")
+            )
+
+mod = cmdstan_model(here::here("Stan","fitting both sessions","hier_weighted_bayes_correlation.stan"))
+
 fit <- mod$sample(
@@
 ```
-
-<!-- ```{r hierachical session correlation} -->
-
-<!-- df= read.csv(here::here("data_TPL_AC.csv")) %>% -->
-<!--   rename_all(tolower) %>% -->
-<!--   filter(trial != 0) %>% -->
-<!--   rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% -->
-<!--   mutate_all(replace_na, 0) %>% mutate(id = as.factor(id), trial = as.factor(trial), session = as.factor(session)) -->
-
-<!-- df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0)) -->
-<!-- df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0)) -->
-
-<!-- #ratings -->
-<!-- df %>% filter(session == 2) %>% ggplot(aes(x = percept, fill = as.factor(stim))) + geom_histogram() -->
-<!-- #cue-contingency -->
-<!-- df %>% filter(session == 1, id == 1) %>% ggplot(aes(x = trial, y = u)) + geom_point()+theme_classic() -->
-
-<!-- #fitting hierachically -->
-<!-- data = df %>% mutate(percept = percept/100) -->
-
-<!-- data = data %>% mutate(across(percept, ~case_when( -->
-<!--     . < 0.001 ~ 0.001, -->
-<!--     . > 0.999 ~ 0.999, -->
-<!--     TRUE ~ . -->
-<!--   ))) -->
-
-<!-- data1 = list(nsubs = length(unique(data$id)), -->
-<!--             ntrials = nrow(data %>% filter(session == 1) %>% filter(id %in% unique(id)[1])), -->
-<!--             sesions = length(unique(data$session)), -->
-<!--             percept = get_3darray(data,variable = "percept"), -->
-<!--             expectPain = get_3darray(data,variable = "pred"), -->
-<!--             percept_bin = get_3darray(data,variable = "percept_bin"), -->
-<!--             stim = get_3darray(data,variable = "stim"), -->
-<!--             cues = get_3darray(data,variable = "cue"), -->
-<!--             u = get_3darray(data,variable = "u") -->
-<!--             ) -->
-
-<!-- mod = cmdstan_model(here::here("Stan","fitting both sessions","myRW_correlation.stan")) -->
-
-<!-- fit <- mod$sample( -->
-<!--   data = data1, -->
-<!--   chains = 4, -->
-<!--   parallel_chains = 4, -->
-<!--   refresh = 100, -->
-<!--   adapt_delta = 0.90, -->
-<!--   max_treedepth = 12 -->
-<!-- ) -->
-
-<!-- sum = fit$summary(variables = c("mu_alpha","mu_w1","sd_beta","sd_precision_percept", "kappa_alpha","kappa_w1","alpha","w1","beta","precision_percept")) -->
-
-<!-- variabless = c("mu_alpha[1]","mu_w1[1]","sd_beta[1]","sd_precision_percept[1]","mu_alpha[2]","mu_w1[2]","sd_beta[2]","sd_precision_percept[2]") -->
-
-<!-- pairs = mcmc_pairs(fit$draws(variables = variabless), np = nuts_params(fit), pars = variabless, -->
-<!--                    off_diag_args = list(size = 0.75)) -->
-<!-- ``` -->
 

### 2023-05-21 equations.Rmd
updates

---
title: "equations"
author: "Jesper Fischer Ehmsen"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

The Rescorla wagner model is a mathematical model of how classical conditions are thought to occur. The basic idea is that an agent updates his belief based on a weighted prediction error which is the difference between the last cue-stimulus association (association) and the last belief. The weighing of the prediction error is generally called the learning rate as this parameter determines the degree to which an agent utilises the new information to update his belief. This learning rate $\alpha$ is for the Rescorla Wagner agent assumed to be constant.

$$
\begin{equation}
\tag{1}
E_t = E_{t-1}+\alpha*\underbrace{(A_{t-1}-E_{t-1})}_{\text{Prediction Error (PE)}}
\end{equation}
$$
In the current experiment we modify this update equation to encapsulate the interaction between precept and expectations. We do this by modifying how the prediction error is calculated as now the prediction error is going to be calculated from the precept  $\psi_t$ that the expectation and the stimulus elicits. We assume for the RW agent that the weighting of stimulus and expectation is governed by a single parameter $\gamma$, like the learning rate $\alpha$ it determines the weight that is put on the stimulus vs expectation in determining what the participant felt on the current trial $\psi_t$

$$
\begin{equation}
\tag{2}
\psi_t = \gamma*S_t+(1-\gamma)*E_t
\end{equation}
$$

$$
\begin{equation}
\tag{3}
PE_t = \psi_t-E_{t-1}
\end{equation}
$$

#### weighted bayes

The weighted bayes model is inspired by bayes theorem where two sources of information a prior and a likelihood  are combined to a posterior belief. The difference between this and the Resorla wagner model is that the percept which is used to update the belief on each trial is calculated using a simplified bayes theorem, where the logit of the posterior is being set equal to the sum of the weighted logits of the sources of information. This entails that the two sources of information are weighted independently, resembling a normal linear regression.

$$
\begin{equation}
\tag{4}
\psi_t = S(w_1*S^{-1}(S_t)+w_2*S^{-1}(E_1))
\end{equation}
$$
where $S(x) = \frac{1}{1+e^{-x}}$. The rest of the update equations remain similar to the Resorla Wagner, essentially also utilizing the RW model to update the expectation on each trial with the prediction error being (3)

##### Kalman filter

The Kalman filter can be thought of as a generalization of the RW model, where the assumption of the learning rate being constant is not met. From a normative perspective it makes sense that agents should update the rate at which they learn depending on the context of the experiment. In the Kalman filter model it is assumed that the learning rate is trial specific and dependent on the uncertainty of the prediction made, where higher uncertainty means a higher learning rate and lower uncertainty a lower learning rate. It is assumed in the Kalman filter that the agent keeps track of both belief as in the RW model, but also the uncertainty of that belief in order to update his belief based on both.

To arrive at the update equations for the kalman filter we start off by assuming that each agent observes the Stimulus with Gaussian noise:

$$
\begin{equation}
\tag{5}
S_t \sim \mathcal{N}{(\mu_{p_t}, \sigma_s^2)}
\end{equation}
$$

Next we assume that the mean of this normal distribution is sampled from another normal distribution with the expectation at trial t as its mean

$$
\begin{equation}
\tag{6}
\psi_t \sim \mathcal{N}{(E_t, \sigma_{\psi}^2)}
\end{equation}
$$
Where this mean is updated based on the stimulus given the cue on previous trials

$$
\begin{equation}
\tag{7}
E_t \sim \mathcal{N}{(E_{t-1}, \sigma_\eta^2)}
\end{equation}
$$
Lastly this prior expectation, i.e. the expectation of the last trial is given by all the previous inputs which the agent keeps track off.

$$
\begin{equation}
\tag{8}
E_t | S_{{t-1}} \sim \mathcal{N}{(E_{t-1}, \sigma_E^2)}
\end{equation}
$$
Now combining (8) and (6) we get a prior for the precept at a given trial, which is before getting the stimulus but after getting the cue

$$
\begin{equation}
\tag{9}
\psi_t | S_{{t-1}} \sim \mathcal{N}{(E_{t-1}, \sigma_E^2+ \sigma_{\psi}^2))}
\end{equation}
$$

After the stimulus is the observed (the likelihood) (5) we can combine this with the prior (9) using bayes rule to get a posterior for percept.

$$
\begin{equation}
\tag{9}
\psi_t | S_{{t-1}} \sim \mathcal{N}{(\frac{\sigma_{s}^2*E_t+(\sigma_{\psi}^2+\sigma_E^2)*S_t}{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_E^2}, \frac{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_E^2}{\sigma_{s}^2*(\sigma_{\psi}^2+\sigma_E^2)}})
\end{equation}
$$
The mean rating of the agent on trial t is therefore given by the mean, which can also be writting as:

$$
\begin{equation}
\tag{9}
\mu_{\psi_t} = \frac{\sigma_{s}^2}{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_E^2}*E_t+\frac{(\sigma_{\psi}^2+\sigma_E^2)}{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_E^2}*S_t
\end{equation}
$$

where it becomes evident that the mean rating at trial t is a weighting between the expectation and the stimulus on the current trial.

After the posterior for the percept is calculated the belief is then updated which can then be used as priors for the next trial.

$$
\begin{equation}
\tag{7}
E_{t+1}|S_t \sim \mathcal{N}{(\frac{(\sigma_{s}^2+\sigma_{\psi}^2)*E_{t-1}+\sigma_E^2*S_t}{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_E^2}, \frac{(\sigma_{s}^2+\sigma_{\psi}^2)*\sigma_E^2}{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_E^2}+\sigma_\eta^2})
\end{equation}
$$

see equation (1)

$$
\begin{equation}
\tag{*}
beinf(y;p_0,p_1,\mu,\phi) = \begin{cases}
      p_0 & x = 0 \\
      f(y;\mu,\phi) & x \in (0,1) \\
      p_1 & x = 1 
   \end{cases}
\end{equation}
$$

where the probability density function of the beta distribution $f(y;\mu,\phi)$ is given by

$$
f(y;\mu,\phi) = \frac{\Gamma(\alpha+\beta)}{\Gamma(\alpha)\Gamma(\beta)}y^{\alpha-1}(1-y)^{\beta-1},y\in (0,1)
$$

In the current study using the GAMLSS packages the parameters are reparameterized as follows:

$$ 
\mu = \frac{\alpha}{\alpha+\beta}
$$

$$
\sigma = \frac{1}{\alpha+\beta+1}
$$

$$
\tau = \frac{p_0}{p_2}
$$

$$
\nu = \frac{p_1}{p_2}
$$
where $p_2 = 1-p_0-p_1$

### 2023-05-21 scripts/parameter_recovery.R

@@ -44,7 +44,7 @@ parameter_recovery_rw = function(parameters){
   
   
   fit <- tryCatch({
-    fit = withTimeout(fitter(), timeout = 1500)
+    fit = withTimeout(fitter(), timeout = 1000, cpu = 1000)
   }, error = function(e) {
     print("An error occurred!")
     return(NA)

### 2023-05-21 visualize_parameters.R

@@ -1,183 +1,0 @@
-#visualize parameters
-
-
-RW = function(){
-  
-  
-  scripts = c("agent.R","parameter_recovery.R","stan_functions.R")
-  q = lapply(here("scripts", scripts), source)
-  alpha = seq(0.1,0.5,by = 0.1)
-  w1 = seq(0.1,0.5,by = 0.1)
-  #precision_percept = seq(10,100,50)
-  #beta = seq(1,50,20)
-  
-  beta = 1
-  precision_percept = seq(10,300,length.out = 3)
-  
-  parameters = expand.grid(alpha = alpha,w1 =  w1, precision_percept = precision_percept, beta = beta)
-  
-  
-  
-  parameters$id = 1:nrow(parameters)
-  
-  data_list <- split(parameters, parameters$id)
-  
-  plan(multisession, workers = 12)
-  
-  
-  dd = get_experiment()
-  
-  
-  dd = furrr::future_map_dfr(data_list, ~our_rw_agent(.x, dd), .progress = TRUE, .options = furrr_options(seed = 123))
-  
-  dd$stim = as.factor(dd$stim)
-  dd$precision_percept = as.factor(dd$precision_percept)
-  
-  
-  plot1 = dd %>% 
-    ggplot()+
-    geom_line(aes(x = trial, y = association))+
-    geom_point(aes(x = trial, y = u), col = "blue")+
-    geom_line(aes(x = trial, y = desired))+
-    facet_grid(alpha~w1, labeller = label_both)+
-    theme_classic()+
-    scale_y_continuous("Cue-stimulus association", breaks = scales::pretty_breaks(n = 5))+
-    scale_x_continuous("Trial", breaks = scales::pretty_breaks(n = 5))
-  
-  
-  plot2 = dd %>% ggplot(aes(exp, y = percept,col = precision_percept, group = interaction(stim, precision_percept)))+
-    geom_point()+
-    facet_grid(alpha~w1, labeller = label_both)+
-    geom_smooth(method = "lm")+
-    theme_classic()+
-    scale_y_continuous("Mean of percept", breaks = scales::pretty_breaks(n = 5))+
-    scale_x_continuous("% belief of Stimulus being Hot", breaks = scales::pretty_breaks(n = 5))
-  
- 
-  plot1+plot2+plot_layout(guides = 'collect')
-   
-}
-
-
[…]

### 2023-05-22 equations.Rmd
updates

@@
 date: "`r Sys.Date()`"
-output: html_document
+output:
+  word_document: default
+  html_document: default
 ---
@@
 \tag{5}
-S_t \sim \mathcal{N}{(\mu_{p_t}, \sigma_s^2)}
+S_t \sim \mathcal{N}{(\psi{_t}, \sigma_s^2)}
 \end{equation}
@@
 \tag{8}
-E_t | S_{{t-1}} \sim \mathcal{N}{(E_{t-1}, \sigma_E^2)}
+E_t | S_{{t-1}} \sim \mathcal{N}{(\mu_{E_{t-1}}, \sigma_{E_t}^2)}
 \end{equation}
@@
 \tag{9}
-\psi_t | S_{{t-1}} \sim \mathcal{N}{(E_{t-1}, \sigma_E^2+ \sigma_{\psi}^2))}
+\psi_t | S_{{t-1}} \sim \mathcal{N}{(\mu_{E_{t-1}}, \sigma_{E_t}^2+ \sigma_{\psi}^2))}
 \end{equation}
@@
 \begin{equation}
-\tag{9}
-\psi_t | S_{{t-1}} \sim \mathcal{N}{(\frac{\sigma_{s}^2*E_t+(\sigma_{\psi}^2+\sigma_E^2)*S_t}{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_E^2}, \frac{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_E^2}{\sigma_{s}^2*(\sigma_{\psi}^2+\sigma_E^2)}})
+\tag{10}
+\psi_t | S_{{t}} \sim \mathcal{N}{(\frac{\sigma_{s}^2*\mu_{E_{t-1}}+(\sigma_{\psi}^2+\sigma_{E_t}^2)*S_t}{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_{E_t}^2}, \frac{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_{E_t}^2}{\sigma_{s}^2*(\sigma_{\psi}^2+\sigma_{E_t}^2)}})
 \end{equation}
@@
 \begin{equation}
-\tag{9}
-\mu_{\psi_t} = \frac{\sigma_{s}^2}{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_E^2}*E_t+\frac{(\sigma_{\psi}^2+\sigma_E^2)}{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_E^2}*S_t
+\tag{11}
+\mu_{\psi_t} = \frac{\sigma_{s}^2}{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_{E_t}^2}*\mu_{E_{t-1}}+\frac{\sigma_{\psi}^2+\sigma_{E_t}^2}{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_{E_t}^2}*S_t
 \end{equation}
@@
 \begin{equation}
-\tag{7}
-E_{t+1}|S_t \sim \mathcal{N}{(\frac{(\sigma_{s}^2+\sigma_{\psi}^2)*E_{t-1}+\sigma_E^2*S_t}{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_E^2}, \frac{(\sigma_{s}^2+\sigma_{\psi}^2)*\sigma_E^2}{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_E^2}+\sigma_\eta^2})
+\tag{12}
+E_{t}|S_t \sim \mathcal{N}{(\frac{(\sigma_{s}^2+\sigma_{\psi}^2)*\mu_{E_{t-1}}+\sigma_{E_t}^2*S_t}{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_{E_t}^2}, \frac{(\sigma_{s}^2+\sigma_{\psi}^2)*\sigma_{E_t}^2}{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_{E_t}^2}+\sigma_\eta^2})
 \end{equation}
@@
 
-see equation (1)
+It can be shown that these update equations for the expectation and the mean percept are a generalization of the above mentioned RW model if we define two trial by trial parameters $\gamma_{t}$ and $\alpha_{t}$
 
@@
 \begin{equation}
-\tag{*}
-beinf(y;p_0,p_1,\mu,\phi) = \begin{cases}
-      p_0 & x = 0 \\
-      f(y;\mu,\phi) & x \in (0,1) \\
-      p_1 & x = 1 
-   \end{cases}
+\tag{13}
+\gamma_{t} = \frac{\sigma_{s}^2}{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_{E_t}^2}
+\end{equation}
+$$
+$$
+\begin{equation}
+\tag{14}
+\alpha_{t} = \frac{\sigma_{E_t}^2}{\sigma_{\psi}^2+\sigma_{E_t}^2}
 \end{equation}
@@
 
-where the probability density function of the beta distribution $f(y;\mu,\phi)$ is given by
+one can arrive at the following update equations for the percept and the expectation
 
 $$
-f(y;\mu,\phi) = \frac{\Gamma(\alpha+\beta)}{\Gamma(\alpha)\Gamma(\beta)}y^{\alpha-1}(1-y)^{\beta-1},y\in (0,1)
-$$
-
-In the current study using the GAMLSS packages the parameters are reparameterized as follows:
-
-$$ 
-\mu = \frac{\alpha}{\alpha+\beta}
+\begin{equation}
+\tag{15}
+\psi_{t} = (1-\gamma_{t})*S_{t}+\gamma_{t}*E_{t}
+\end{equation}
 $$
@@
 $$
-\sigma = \frac{1}{\alpha+\beta+1}
+\begin{equation}
+\tag{16}
+E_{t} = \alpha_{t}*\psi_{t}+(1-\alpha_{t})*E_{t}
+\end{equation}
 $$
-
-$$
-\tau = \frac{p_0}{p_2}
-$$
-
-$$
-\nu = \frac{p_1}{p_2}
-$$
-where $p_2 = 1-p_0-p_1$
+For the derivation of equation 15 and 16 readers are refereed to the supplementary material.

### 2023-05-22 scripts/agent.R

@@ -308,7 +308,7 @@ our_kalman_agent22 = function(parameters,dd){
     
     exp_mu[t] = ifelse(exp_mu[t] > 0.999, 0.999, ifelse(exp_mu[t] < 0.001, 0.001, exp_mu[t]))
     
-    pred[t] = rbinom(1,1,(exp_mu[t]^beta[t])/((exp_mu[t]^beta[t])+(1-exp_mu[t])^(beta[t])))
+    pred[t] = rbinom(1,1,(exp_mu[t]^beta)/((exp_mu[t]^beta)+(1-exp_mu[t])^(beta)))
     
     
     perceptmu[t] =  (sigmaEpsilon * exp_mu[t] + (sigmaPsi + exp_var[t]) * stim[t] ) / 
@@ -323,7 +323,7 @@ our_kalman_agent22 = function(parameters,dd){
     percept[t] = extraDistr::rprop(1,precision_percept,perceptmu[t])
     
     
-    percept_bin[t] = rbinom(1,1,(perceptmu[t]^beta[t])/((perceptmu[t]^beta[t])+(1-perceptmu[t])^(beta[t])))
+    percept_bin[t] = rbinom(1,1,(perceptmu[t]^beta)/((perceptmu[t]^beta)+(1-perceptmu[t])^(beta)))
     
     association[t+1] <- ((sigmaEpsilon + sigmaPsi) * association[t] + (exp_var[t] * u[t])) / 
       (sigmaEpsilon + sigmaPsi + exp_var[t])

### 2023-05-22 scripts/visualize_parameters.R

@@ -124,8 +124,8 @@ KALMAN_v2 = function(){
   sigmaEta = seq(0.01,0.1,length.out = 5)
   sigmaPsi = seq(0.01,2,length.out = 5)
   sigmaEpsilon = seq(0.1,1,length.out = 5)
-  beta = 200
-  precision_percept = 200
+  beta = 100
+  precision_percept = 100
   
   
   parameters = expand.grid(sigmaEta = sigmaEta,sigmaPsi =  sigmaPsi, sigmaEpsilon = sigmaEpsilon, beta = beta, precision_percept = precision_percept)

### 2023-05-22 Manuscript.Rmd
updates

@@
 ```{r parameters visualization}
-RW()
+dd = get_experiment()
+
+rwplot = RW(dd)
+
+kalmanplot = KALMAN_v2(dd)
+
+wbplot = WB(dd)
+
+layout = (c(
+  area(1, 1),
+  area(1, 2),
+  area(2, 1),
+  area(2, 2)
+
+))
+
+plot_spacer()+kalmanplot+rwplot+wbplot+plot_layout(design = layout)
 
@@
 rw_pp = furrr::future_map(data_list, ~parameter_recovery_rw(.x), .progress = TRUE, .options = furrr_options(seed = 123))
+
 ```
@@
 
-mu_sigmaEta = seq(1,100,length.out = 3)
-mu_sigmaPsi = seq(1,100,length.out = 3)
-mu_sigmaEpsilon = seq(1,100,length.out = 3)
+mu_sigmaEta = seq(0.1,1,length.out = 3)
+mu_sigmaPsi = seq(0.1,1,length.out = 3)
+mu_sigmaEpsilon = seq(0.1,1,length.out = 3)
 
-sd_sigmaEta = seq(0.1,10,length.out = 3)
-sd_sigmaPsi = seq(0.1,10,length.out = 3)
-sd_sigmaEpsilon = seq(0.1,10,length.out = 3)
+sd_sigmaEta = seq(0.1,1,length.out = 3)
+sd_sigmaPsi = seq(0.1,1,length.out = 3)
+sd_sigmaEpsilon = seq(0.1,1,length.out = 3)
 
-nsubs = 50
+sd_precision_percept = seq(0.1,2, length.out = 3)
+
+sd_beta = seq(0.1,2, length.out = 3)
+
+nsubs = 10
 
@@
                          sd_sigmaEpsilon = sd_sigmaEpsilon,
+                         sd_precision_percept = sd_precision_percept, 
+                         sd_beta = sd_beta,
                          nsubs = nsubs)
@@
 #plot parameterrecovery
-hier_pp <- do.call(rbind, lapply(rw_dd, "[[", 1))
+hier_pp <- do.call(rbind, lapply(rw_pp, "[[", 1))
 hier_pp %>% mutate(divergences = ifelse(div > 0,1,0)) %>% 
@@
 
-sub_pp <- do.call(rbind, lapply(rw_dd, "[[", 2))
+sub_pp <- do.call(rbind, lapply(rw_pp, "[[", 2))
 sub_pp %>% mutate(divergences = ifelse(div > 0,1,0)) %>% 
@@
 
-data_list = data_list_wb[1]
+data_list = data_list_wb[1:100]
 
-plan(multisession, workers = 5)
+plan(multisession, workers = 10)
 
@@
 
-<!-- ```{r fitting Kalman model to session 1} -->
-<!-- df= read.csv(here::here("data_TPL_AC.csv")) %>%  -->
-<!--   rename_all(tolower) %>%  -->
-<!--   filter(trial != 0) %>%  -->
-<!--   rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%  -->
-<!--   mutate_all(replace_na, 0) -->
+```{r fitting Kalman model to session 1}
+df= read.csv(here::here("data_TPL_AC.csv")) %>%
+  rename_all(tolower) %>%
+  filter(trial != 0) %>%
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
+  mutate_all(replace_na, 0)
 
-<!-- df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0)) -->
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
 
-<!-- df = df %>% filter(session == 1) -->
+df = df %>% filter(session == 1, id > 40)
 
-<!-- #fitting hierachically -->
-<!-- data = df %>% mutate(percept = percept/100) -->
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
 
-<!-- data = data %>% mutate(across(percept, ~case_when( -->
-<!--     . < 0.001 ~ 0.001, -->
-<!--     . > 0.999 ~ 0.999, -->
-<!--     TRUE ~ . -->
-<!--   ))) -->
+data = data %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
 
-<!-- data1 = list(nsubs = length(unique(data$id)), -->
-<!--             ntrials = nrow(data %>% filter(id %in% unique(id)[1])), -->
-<!--             percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)), -->
-<!--             expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)), -->
-<!--             percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)), -->
-<!--             stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)), -->
-<!--             cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)), -->
-<!--             u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL)) -->
-<!--             ) -->
+data1 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
+            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
+            expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
+            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
+            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)),
+            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL))
+            )
 
-<!-- mod = cmdstan_model(here::here("Stan","myKalmanfilter.stan")) -->
+mod = cmdstan_model(here::here("Stan","myKalmanfilter_v2.stan"))
 
-<!-- kalman_fit_sess1 <- mod$sample( -->
-<!--       data = data1, -->
-<!--       chains = 4,  -->
-<!--       parallel_chains = 4, -->
-<!--       refresh = 100, -->
-<!--       adapt_delta = 0.90, -->
-<!--       max_treedepth = 12 -->
-<!--     ) -->
-<!-- ``` -->
+kalman_fit_sess1 <- mod$sample(
+      data = data1,
+      chains = 4,
+      parallel_chains = 4,
+      refresh = 100,
+      adapt_delta = 0.90,
+      max_treedepth = 12
+    )
 
-<!-- ```{r fitting Kalman model to session 2} -->
-<!-- df= read.csv(here::here("data_TPL_AC.csv")) %>%  -->
-<!--   rename_all(tolower) %>%  -->
-<!--   filter(trial != 0) %>%  -->
-<!--   rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%  -->
-<!--   mutate_all(replace_na, 0) -->
+diag_sigmaEta = get_diag(fit = kalman_fit_sess1,
+         parameter = "sigmaEta")
 
-<!-- df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0)) -->
+diag_sigmaPsi = get_diag(fit = kalman_fit_sess1,
+         parameter = "sigmaPsi")
 
-<!-- df = df %>% filter(session == 2) -->
+diag_sigmaEpsilon = get_diag(fit = kalman_fit_sess1,
+         parameter = "sigmaEpsilon")
 
-<!-- #fitting hierachically -->
-<!-- data = df %>% mutate(percept = percept/100) -->
+diag_sigmabeta = get_diag(fit = kalman_fit_sess1,
+         parameter = "beta")
 
-<!-- data = data %>% mutate(across(percept, ~case_when( -->
-<!--     . < 0.001 ~ 0.001, -->
-<!--     . > 0.999 ~ 0.999, -->
-<!--     TRUE ~ . -->
-<!--   ))) -->
+diag_precision_percept = get_diag(fit = kalman_fit_sess1,
+         parameter = "precision_percept")
+```
 
-<!-- data1 = list(nsubs = length(unique(data$id)), -->
-<!--             ntrials = nrow(data %>% filter(id %in% unique(id)[1])), -->
-<!--             percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)), -->
-<!--             expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)), -->
-<!--             percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)), -->
-<!--             stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)), -->
-<!--             cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)), -->
-<!--             u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL)) -->
-<!--             ) -->
+```{r fitting Kalman model to session 2}
+df= read.csv(here::here("data_TPL_AC.csv")) %>%
+  rename_all(tolower) %>%
+  filter(trial != 0) %>%
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
+  mutate_all(replace_na, 0)
 
-<!-- mod = cmdstan_model(here::here("Stan","myKalmanfilter.stan")) -->
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
 
-<!-- kalman_fit_sess1 <- mod$sample( -->
-<!--       data = data1, -->
-<!--       chains = 4,  -->
-<!--       parallel_chains = 4, -->
-<!--       refresh = 100, -->
-<!--       adapt_delta = 0.90, -->
-<!--       max_treedepth = 12 -->
-<!--     ) -->
-<!-- ``` -->
+df = df %>% filter(session == 2)
+
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data1 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
+            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
+            expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
+            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
+            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)),
+            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL))
+            )
+
+mod = cmdstan_model(here::here("Stan","myKalmanfilter_v2.stan"))
+
+kalman_fit_sess1 <- mod$sample(
+      data = data1,
+      chains = 4,
+      parallel_chains = 4,
+      refresh = 100,
+      adapt_delta = 0.90,
+      max_treedepth = 12
+    )
+```
 
@@
 
-<!-- ```{r fitting to real data tester hierachical RW session 1} -->
+```{r fitting to real data tester hierachical RW session 1}
 
-<!-- df= read.csv(here::here("data_TPL_AC.csv")) %>%  -->
-<!--   rename_all(tolower) %>%  -->
-<!--   filter(trial != 0) %>%  -->
-<!--   rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%  -->
-<!--   mutate_all(replace_na, 0) -->
+df= read.csv(here::here("data_TPL_AC.csv")) %>%
+  rename_all(tolower) %>%
+  filter(trial != 0) %>%
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
+  mutate_all(replace_na, 0)
 
-<!-- df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0)) -->
-<!-- df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0)) -->
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
 
-<!-- #ratings -->
-<!-- df %>% filter(session == 2) %>% ggplot(aes(x = percept, fill = as.factor(stim))) + geom_histogram() -->
-<!-- #cue-contingency -->
-<!-- df %>% filter(session == 1, id == 1) %>% ggplot(aes(x = trial, y = u)) + geom_point()+theme_classic() -->
+df = df %>% filter(session == 1)
 
-<!-- df = df %>% filter(session == 1) -->
+#source(here::here("stan_functions.R"))
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
 
-<!-- source(here::here("stan_functions.R")) -->
-<!-- #fitting hierachically -->
-<!-- data = df %>% mutate(percept = percept/100) -->
+data = data %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
 
-<!-- data = data %>% mutate(across(percept, ~case_when( -->
-<!--     . < 0.001 ~ 0.001, -->
-<!--     . > 0.999 ~ 0.999, -->
-<!--     TRUE ~ . -->
-<!--   ))) -->
+data1 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
+            pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL))
+            )
 
-<!-- data1 = list(nsubs = length(unique(data$id)), -->
-<!--             ntrials = nrow(data %>% filter(id %in% unique(id)[1])), -->
-<!--             percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)), -->
-<!--             expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)), -->
-<!--             percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)), -->
-<!--             stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)), -->
-<!--             cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)), -->
-<!--             u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL)) -->
-<!--             ) -->
+mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier.stan"))
 
-<!-- data1 = list(nsubs = length(unique(data$id)), -->
-<!--             ntrials = nrow(data %>% filter(id %in% unique(id)[1])), -->
-<!--             pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)), -->
-<!--             u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL)) -->
-<!--             ) -->
+rw_fit_ses1 <- mod$sample(
+      data = data1,
+      chains = 4,
+      parallel_chains = 4,
+      refresh = 100,
+      adapt_delta = 0.90,
+      max_treedepth = 12
+    )
 
-<!-- mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier.stan")) -->
+sum = rw_fit_ses1$summary(variables = c("alpha_1"))
 
-<!-- rw_fit_ses1 <- mod$sample( -->
-<!--       data = data1, -->
-<!--       chains = 4,  -->
-<!--       parallel_chains = 4, -->
-<!--       refresh = 100, -->
-<!--       adapt_delta = 0.90, -->
-<!--       max_treedepth = 12 -->
-<!--     ) -->
-<!-- ``` -->
+```
 
-<!-- ```{r fitting to real data tester hierachical RW seesion2} -->
+```{r fitting to real data tester hierachical RW seesion2}
 
-<!-- df= read.csv(here::here("data_TPL_AC.csv")) %>%  -->
-<!--   rename_all(tolower) %>%  -->
-<!--   filter(trial != 0) %>%  -->
-<!--   rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%  -->
-<!--   mutate_all(replace_na, 0) -->
+df= read.csv(here::here("data_TPL_AC.csv")) %>%
+  rename_all(tolower) %>%
+  filter(trial != 0) %>%
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
+  mutate_all(replace_na, 0)
 
-<!-- df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0)) -->
-<!-- df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0)) -->
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
 
-<!-- #ratings -->
-<!-- df %>% filter(session == 2) %>% ggplot(aes(x = percept, fill = as.factor(stim))) + geom_histogram() -->
-<!-- #cue-contingency -->
-<!-- df %>% filter(session == 1, id == 1) %>% ggplot(aes(x = trial, y = u)) + geom_point()+theme_classic() -->
+df = df %>% filter(session == 2)
 
-<!-- df = df %>% filter(session == 2) -->
+#source(here::here("stan_functions.R"))
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
 
-<!-- source(here::here("stan_functions.R")) -->
-<!-- #fitting hierachically -->
-<!-- data = df %>% mutate(percept = percept/100) -->
+data = data %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
 
-<!-- data = data %>% mutate(across(percept, ~case_when( -->
-<!--     . < 0.001 ~ 0.001, -->
-<!--     . > 0.999 ~ 0.999, -->
-<!--     TRUE ~ . -->
-<!--   ))) -->
+data2 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
+            pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL))
+            )
 
-<!-- data1 = list(nsubs = length(unique(data$id)), -->
-<!--             ntrials = nrow(data %>% filter(id %in% unique(id)[1])), -->
-<!--             percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)), -->
-<!--             expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)), -->
-<!--             percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)), -->
-<!--             stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)), -->
-<!--             cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)), -->
-<!--             u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL)) -->
-<!--             ) -->
+mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier.stan"))
 
-<!-- data1 = list(nsubs = length(unique(data$id)), -->
-<!--             ntrials = nrow(data %>% filter(id %in% unique(id)[1])), -->
-<!--             pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)), -->
-<!--             u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL)) -->
-<!--             ) -->
+rw_fit_ses2 <- mod$sample(
+      data = data2,
+      chains = 4,
+      parallel_chains = 4,
+      refresh = 100,
+      adapt_delta = 0.90,
+      max_treedepth = 12
+    )
 
-<!-- mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier.stan")) -->
+sums2 = rw_fit_ses2$summary(variables = c("alpha_1"))
 
-<!-- rw_fit_ses2 <- mod$sample( -->
-<!--       data = data1, -->
-<!--       chains = 4,  -->
-<!--       parallel_chains = 4, -->
-<!--       refresh = 100, -->
-<!--       adapt_delta = 0.90, -->
-<!--       max_treedepth = 12 -->
-<!--     ) -->
-<!-- ``` -->
+```

### 2023-05-22 equations.tex
updates

--- 2023-05-22 equations.Rmd
@@
----
-title: "equations"
-author: "Jesper Fischer Ehmsen"
-date: "`r Sys.Date()`"
-output:
-  word_document: default
-  html_document: default
----
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+%
+\documentclass[
+]{article}
+\usepackage{amsmath,amssymb}
+\usepackage{lmodern}
+\usepackage{iftex}
+\ifPDFTeX
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\usepackage[margin=1in]{geometry}
+\usepackage{graphicx}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={equations},
+  pdfauthor={Jesper Fischer Ehmsen},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-```
+\title{equations}
+\author{Jesper Fischer Ehmsen}
+\date{2023-05-22}
 
-## R Markdown
+\begin{document}
+\maketitle
 
-The Rescorla wagner model is a mathematical model of how classical conditions are thought to occur.
-The basic idea is that an agent updates his belief based on a weighted prediction error which is the difference between the last cue-stimulus association (association) and the last belief.
-The weighing of the prediction error is generally called the learning rate as this parameter determines the degree to which an agent utilises the new information to update his belief.
-This learning rate $\alpha$ is for the Rescorla Wagner agent assumed to be constant.
+\hypertarget{r-markdown}{%
+\subsection{R Markdown}\label{r-markdown}}
 
-$$
+The Rescorla wagner model is a mathematical model of how classical
+conditions are thought to occur. The basic idea is that an agent updates
+his belief based on a weighted prediction error which is the difference
+between the last cue-stimulus association (association) and the last
+belief. The weighing of the prediction error is generally called the
+learning rate as this parameter determines the degree to which an agent
+utilises the new information to update his belief. This learning rate
+\(\alpha\) is for the Rescorla Wagner agent assumed to be constant.
+
+\[
 \begin{equation}
@@
 \end{equation}
-$$
-In the current experiment we modify this update equation to encapsulate the interaction between precept and expectations.
-We do this by modifying how the prediction error is calculated as now the prediction error is going to be calculated from the precept  $\psi_t$ that the expectation and the stimulus elicits.
-We assume for the RW agent that the weighting of stimulus and expectation is governed by a single parameter $\gamma$, like the learning rate $\alpha$ it determines the weight that is put on the stimulus vs expectation in determining what the participant felt on the current trial $\psi_t$
+\] In the current experiment we modify this update equation to
+encapsulate the interaction between precept and expectations. We do this
+by modifying how the prediction error is calculated as now the
+prediction error is going to be calculated from the precept \(\psi_t\)
+that the expectation and the stimulus elicits. We assume for the RW
+agent that the weighting of stimulus and expectation is governed by a
+single parameter \(\gamma\), like the learning rate \(\alpha\) it
+determines the weight that is put on the stimulus vs expectation in
+determining what the participant felt on the current trial \(\psi_t\)
 
-$$
+\[
 \begin{equation}
@@
 \end{equation}
-$$
+\]
 
-$$
+\[
 \begin{equation}
@@
 \end{equation}
-$$
+\]
 
-#### weighted bayes
+\hypertarget{weighted-bayes}{%
+\paragraph{weighted bayes}\label{weighted-bayes}}
 
-The weighted bayes model is inspired by bayes theorem where two sources of information a prior and a likelihood  are combined to a posterior belief.
-The difference between this and the Resorla wagner model is that the percept which is used to update the belief on each trial is calculated using a simplified bayes theorem, where the logit of the posterior is being set equal to the sum of the weighted logits of the sources of information.
-This entails that the two sources of information are weighted independently, resembling a normal linear regression.
+The weighted bayes model is inspired by bayes theorem where two sources
+of information a prior and a likelihood are combined to a posterior
+belief. The difference between this and the Resorla wagner model is that
+the percept which is used to update the belief on each trial is
+calculated using a simplified bayes theorem, where the logit of the
+posterior is being set equal to the sum of the weighted logits of the
+sources of information. This entails that the two sources of information
+are weighted independently, resembling a normal linear regression.
 
-$$
+\[
 \begin{equation}
@@
 \end{equation}
-$$
-where $S(x) = \frac{1}{1+e^{-x}}$.
-The rest of the update equations remain similar to the Resorla Wagner, essentially also utilizing the RW model to update the expectation on each trial with the prediction error being (3)
+\] where \(S(x) = \frac{1}{1+e^{-x}}\). The rest of the update equations
+remain similar to the Resorla Wagner, essentially also utilizing the RW
+model to update the expectation on each trial with the prediction error
+being (3)
 
-##### Kalman filter
+\hypertarget{kalman-filter}{%
+\subparagraph{Kalman filter}\label{kalman-filter}}
 
-The Kalman filter can be thought of as a generalization of the RW model, where the assumption of the learning rate being constant is not met.
-From a normative perspective it makes sense that agents should update the rate at which they learn depending on the context of the experiment.
-In the Kalman filter model it is assumed that the learning rate is trial specific and dependent on the uncertainty of the prediction made, where higher uncertainty means a higher learning rate and lower uncertainty a lower learning rate.
-It is assumed in the Kalman filter that the agent keeps track of both belief as in the RW model, but also the uncertainty of that belief in order to update his belief based on both.
+The Kalman filter can be thought of as a generalization of the RW model,
+where the assumption of the learning rate being constant is not met.
+From a normative perspective it makes sense that agents should update
+the rate at which they learn depending on the context of the experiment.
+In the Kalman filter model it is assumed that the learning rate is trial
+specific and dependent on the uncertainty of the prediction made, where
+higher uncertainty means a higher learning rate and lower uncertainty a
+lower learning rate. It is assumed in the Kalman filter that the agent
+keeps track of both belief as in the RW model, but also the uncertainty
+of that belief in order to update his belief based on both.
 
-To arrive at the update equations for the kalman filter we start off by assuming that each agent observes the Stimulus with Gaussian noise:
+To arrive at the update equations for the kalman filter we start off by
+assuming that each agent observes the Stimulus with Gaussian noise:
 
-$$
+\[
 \begin{equation}
@@
 \end{equation}
-$$
+\]
 
-Next we assume that the mean of this normal distribution is sampled from another normal distribution with the expectation at trial t as its mean
+Next we assume that the mean of this normal distribution is sampled from
+another normal distribution with the expectation at trial t as its mean
 
-$$
+\[
 \begin{equation}
@@
 \end{equation}
-$$
-Where this mean is updated based on the stimulus given the cue on previous trials
+\] Where this mean is updated based on the stimulus given the cue on
+previous trials
 
-$$
+\[
 \begin{equation}
@@
 \end{equation}
-$$
-Lastly this prior expectation, i.e. the expectation of the last trial is given by all the previous inputs which the agent keeps track off.
+\] Lastly this prior expectation, i.e.~the expectation of the last trial
+is given by all the previous inputs which the agent keeps track off.
 
-$$
+\[
 \begin{equation}
@@
 \end{equation}
-$$
-Now combining (8) and (6) we get a prior for the precept at a given trial, which is before getting the stimulus but after getting the cue
+\] Now combining (8) and (6) we get a prior for the precept at a given
+trial, which is before getting the stimulus but after getting the cue
 
-$$
+\[
 \begin{equation}
@@
 \end{equation}
-$$
+\]
 
-After the stimulus is the observed (the likelihood) (5) we can combine this with the prior (9) using bayes rule to get a posterior for percept.
+After the stimulus is the observed (the likelihood) (5) we can combine
+this with the prior (9) using bayes rule to get a posterior for percept.
 
-$$
+\[
 \begin{equation}
@@
 \end{equation}
-$$
-The mean rating of the agent on trial t is therefore given by the mean, which can also be writting as:
+\] The mean rating of the agent on trial t is therefore given by the
+mean, which can also be writting as:
 
-$$
+\[
 \begin{equation}
@@
 \end{equation}
-$$
+\]
 
-where it becomes evident that the mean rating at trial t is a weighting between the expectation and the stimulus on the current trial.
+where it becomes evident that the mean rating at trial t is a weighting
+between the expectation and the stimulus on the current trial.
 
-After the posterior for the percept is calculated the belief is then updated which can then be used as priors for the next trial.
+After the posterior for the percept is calculated the belief is then
+updated which can then be used as priors for the next trial.
 
-$$
+\[
 \begin{equation}
@@
 \end{equation}
-$$
+\]
 
-It can be shown that these update equations for the expectation and the mean percept are a generalization of the above mentioned RW model if we define two trial by trial parameters $\gamma_{t}$ and $\alpha_{t}$
+It can be shown that these update equations for the expectation and the
+mean percept are a generalization of the above mentioned RW model if we
+define two trial by trial parameters \(\gamma_{t}\) and \(\alpha_{t}\)
 
-$$
+\[
 \begin{equation}
@@
 \end{equation}
-$$
-$$
+\] \[
 \begin{equation}
@@
 \end{equation}
-$$
+\]
 
-one can arrive at the following update equations for the percept and the expectation
+one can arrive at the following update equations for the percept and the
+expectation
 
-$$
+\[
 \begin{equation}
@@
 \end{equation}
-$$
-For the derivation of equation 15 and 16 readers are refereed to the supplementary material.
+\] For the derivation of equation 15 and 16 readers are refereed to the
+supplementary material.
+
+\end{document}

### 2023-05-22 scripts/agent.R

@@ -336,7 +336,7 @@ our_kalman_agent22 = function(parameters,dd){
   return(data.frame(exp_mu = exp_mu[1:ntrials], perceptmu = perceptmu, pred = pred, percept = percept,
                     percept_bin = percept_bin, trial = 1:ntrials, stim = stim, u = u, association = association[1:ntrials], cue = cue,
                     sigmaPsi = sigmaPsi, sigmaEta = sigmaEta, sigmaEpsilon = sigmaEpsilon, desired = rep(bias,1),exp_var = exp_var[1:ntrials],
-                    perceptvar = perceptvar[1:ntrials], id = rnorm(1,0,1)))
+                    perceptvar = perceptvar[1:ntrials], beta = beta, precision_percept = precision_percept, id = rnorm(1,0,1)))
   
   
   
@@ -427,6 +427,86 @@ our_kalman_agent_v2 = function(sigmaEta, sigmaEpsilon, sigmaPsi){
 }
 
 
+our_kalman_agent_v22 = function(sigmaEta, sigmaEpsilon, sigmaPsi,precision_percept,beta){
+  
+  dd = get_experiment()
+  
+  cue = dd$cue
+  stim = dd$stim
+  u = dd$u
+  bias = dd$bias
+  
+  
+  
+  ntrials = nrow(dd)
+  
+  percept = array(NA, ntrials)
+  perceptmu = array(NA, ntrials)
+  perceptvar = array(NA, ntrials)
+  perceptprec = array(NA,ntrials)
+  
+  
+  
+  exp_mu = array(NA, ntrials)
+  exp_var = array(NA, ntrials)
+  exp_prec = array(NA, ntrials)  
+  
+  association = array(NA, ntrials)
+  pred = array(NA,ntrials)
+  pe = array(NA,ntrials)
+  percept_bin = array(NA,ntrials)
+  
+  association = array(NA,ntrials)
+  
+  association[1] = 0.5
+  exp_var[1] = sigmaEta
+  
+  for(t in 1:ntrials){
+    
+    exp_mu[t] = ifelse(cue[t] == 1, association[t], 1-association[t])
+    
+    exp_prec[t] = 1/exp_var[t]
+    
+    exp_mu[t] = ifelse(exp_mu[t] > 0.999, 0.999, ifelse(exp_mu[t] < 0.001, 0.001, exp_mu[t]))
+    
[…]

### 2023-05-22 scripts/model recovery.R

@@ -30,7 +30,7 @@ model_fitter_rwdata = function(parameters_rw){
   
   rw_model = here::here("Stan","myRW_real.stan")
   wb_model = here::here("Stan","hier_weighted_bayes.stan")
-  kalman_model = here::here("Stan","myKalmanfilter.stan")
+  kalman_model = here::here("Stan","myKalmanfilter_v2.stan")
   
   
   data1_rw_wb = data1_rw
@@ -101,7 +101,7 @@ model_fitter_wbdata = function(parameters_wb){
   
   rw_model = here::here("Stan","myRW_real.stan")
   wb_model = here::here("Stan","hier_weighted_bayes.stan")
-  kalman_model = here::here("Stan","myKalmanfilter.stan")
+  kalman_model = here::here("Stan","myKalmanfilter_v2.stan")
   
   id = rnorm(1,0,1)
   
@@ -109,7 +109,6 @@ model_fitter_wbdata = function(parameters_wb){
   loo_wb_wb = get_loo(wb_model, data1_wb)
   loo_wb_kalman = get_loo(kalman_model, data1_wb_kalman)
   
-   
   comparison = data.frame(loo_compare(list(loo_wb_rw[[3]],loo_wb_wb[[3]],loo_wb_kalman[[3]])))
   comparison$id = id
   

### 2023-05-22 scripts/stan_functions.R

@@ -112,14 +112,14 @@ ppu_hier = function(fit,parameters,reals){
       df = rbind(post,priors)
       
       if(!is.na(reals)[1]){
-        reals = hier %>% select(grep(parameter,names(hier), value = TRUE))
+        reals2 = reals %>% select(grep(parameter,names(reals), value = TRUE))
         
         plot1 = df %>% pivot_longer(cols = post_parameters)%>% 
           ggplot(aes(x = value, fill = posterior))+
           geom_histogram(alpha = 0.5, position="identity")+
           facet_wrap(~name, scales = "free")+
           theme_classic()+
-          geom_vline(data = reals %>% pivot_longer(cols = post_parameters), aes(xintercept = value))
+          geom_vline(data = reals2 %>% pivot_longer(cols = post_parameters), aes(xintercept = value))
       
         plots[[q]] = plot1
       }else{

### 2023-05-22 scripts/visualize_parameters.R

@@ -1,17 +1,17 @@
 #visualize parameters
 
 
-RW = function(){
+RW = function(dd){
   
   
   scripts = c("agent.R","parameter_recovery.R","stan_functions.R")
   q = lapply(here("scripts", scripts), source)
-  alpha = seq(0.1,0.5,by = 0.1)
-  w1 = seq(0.1,0.5,by = 0.1)
+  alpha = seq(0.1,0.5,length.out = 3)
+  w1 = seq(0.1,0.5,length.out = 3)
   #precision_percept = seq(10,100,50)
   #beta = seq(1,50,20)
   
-  beta = 1
+  beta = 50
   precision_percept = seq(10,300,length.out = 3)
   
   parameters = expand.grid(alpha = alpha,w1 =  w1, precision_percept = precision_percept, beta = beta)
@@ -25,19 +25,19 @@ RW = function(){
   plan(multisession, workers = 12)
   
   
-  dd = get_experiment()
-  
-  
   dd = furrr::future_map_dfr(data_list, ~our_rw_agent(.x, dd), .progress = TRUE, .options = furrr_options(seed = 123))
   
   dd$stim = as.factor(dd$stim)
   dd$precision_percept = as.factor(dd$precision_percept)
   
   
+  levels(dd$stim) = c("Warm","Hot")
+  
+  
   plot1 = dd %>% 
     ggplot()+
     geom_line(aes(x = trial, y = association))+
-    geom_point(aes(x = trial, y = u), col = "blue")+
+    geom_point(aes(x = trial, y = u), col = "orange")+
     geom_line(aes(x = trial, y = desired))+
     facet_grid(alpha~w1, labeller = label_both)+
     theme_classic()+
@@ -46,15 +46,15 @@ RW = function(){
   
   
   plot2 = dd %>% ggplot(aes(exp, y = percept,col = precision_percept, group = interaction(stim, precision_percept)))+
-    geom_point()+
+    geom_point(aes(shape = stim))+
     facet_grid(alpha~w1, labeller = label_both)+
     geom_smooth(method = "lm")+
     theme_classic()+
-    scale_y_continuous("Mean of percept", breaks = scales::pretty_breaks(n = 5))+
-    scale_x_continuous("% belief of Stimulus being Hot", breaks = scales::pretty_breaks(n = 5))
+    scale_y_continuous("Mean of percept", breaks = scales::pretty_breaks(n = 4))+
[…]

### 2023-05-23 Manuscript.Rmd
updates

@@
 mu_sigmaEta = seq(0.1,1,length.out = 3)
-mu_sigmaPsi = seq(0.1,1,length.out = 3)
-mu_sigmaEpsilon = seq(0.1,1,length.out = 3)
+mu_sigmaPsi = seq(0.1,5,length.out = 3)
+mu_sigmaEpsilon = seq(0.1,5,length.out = 3)
 
-sd_sigmaEta = seq(0.1,1,length.out = 3)
-sd_sigmaPsi = seq(0.1,1,length.out = 3)
-sd_sigmaEpsilon = seq(0.1,1,length.out = 3)
+sd_sigmaEta = seq(0.1,1,length.out = 2)
+sd_sigmaPsi = seq(0.1,1,length.out = 2)
+sd_sigmaEpsilon = seq(0.1,1,length.out = 2)
 
-sd_precision_percept = seq(0.1,2, length.out = 3)
+sd_precision_percept = seq(0.1,1, length.out = 2)
 
-sd_beta = seq(0.1,2, length.out = 3)
+sd_beta = seq(0.1,1, length.out = 2)
 
@@
 
-plan(multisession, workers = availableCores()-1)
+#plan(multisession, workers = availableCores()-1)
 
-data_list = data_list[1:100]
+data_list = data_list[1:2]
 
@@
 
-df = df %>% filter(session == 1, id > 40)
+df = df %>% filter(session == 1)
 
@@
 
-mod = cmdstan_model(here::here("Stan","myKalmanfilter_v2.stan"))
+mod = cmdstan_model(here::here("Stan","no generated quantities","myKalmanfilter_v2_nogen_nocent.stan"))
 
@@
 
-mod = cmdstan_model(here::here("Stan","myKalmanfilter_v2.stan"))
+mod = cmdstan_model(here::here("Stan","no generated quantities","myKalmanfilter_v2_nogen_nocent.stan"))
 
-kalman_fit_sess1 <- mod$sample(
+kalman_fit_sess2 <- mod$sample(
       data = data1,

### 2023-05-23 scripts/agent.R

@@ -343,10 +343,6 @@ our_kalman_agent22 = function(parameters,dd){
   
 }
 
-
-
-
-
 our_kalman_agent_v2 = function(sigmaEta, sigmaEpsilon, sigmaPsi){
   
   dd = get_experiment()

### 2023-05-23 scripts/parameter_recovery.R

@@ -170,7 +170,7 @@ parameter_recovery_kalman = function(parameters){
                u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL))
   )
   
-  mod = cmdstan_model(here::here("Stan","no generated quantities","myKalmanfilter_nogen.stan"))
+  mod = cmdstan_model(here::here("Stan","no generated quantities","myKalmanfilter_v2_nogen_nocent.stan"))
   
   
   fitter = function(){
@@ -182,12 +182,13 @@ parameter_recovery_kalman = function(parameters){
       adapt_delta = 0.90,
       max_treedepth = 12
     )
-    return(fit)
+    
+        return(fit)
   }
   
   
   fit <- tryCatch({
-    fit = withTimeout(fitter(), timeout = 1500)
+    fit = withTimeout(fitter(), timeout = 1500, cpu = 1500)
   }, error = function(e) {
     print("An error occurred!")
     return(NA)

### 2023-05-23 scripts/visualize_parameters.R

@@ -121,9 +121,9 @@ KALMAN_v2 = function(dd){
   #kalman filter:
   
   
-  sigmaEta = seq(0.01,0.1,length.out = 3)
-  sigmaPsi = seq(0.01,2,length.out = 3)
-  sigmaEpsilon = seq(0.1,1,length.out = 3)
+  sigmaEta = seq(0.01,1,length.out = 3)
+  sigmaPsi = seq(0.01,5,length.out = 3)
+  sigmaEpsilon = seq(0.1,5,length.out = 3)
   beta = 50
   precision_percept = 155
   

### 2023-05-23 Manuscript.Rmd
updates

@@
 
-```{r parameters visualization}
+```{r parameters visualization, fig.height=10, fig.width=10}
 dd = get_experiment()
@@
 #plot parameterrecovery
-hier_pp <- do.call(rbind, lapply(rw_pp, "[[", 1))
-hier_pp %>% mutate(divergences = ifelse(div > 0,1,0)) %>% 
-  ggplot(aes(x = mean, y = reals.reals))+
-  geom_point(aes(col = as.factor(divergences)))+
-  facet_wrap(~variable, scales = "free")+
-  theme_classic()+
-  geom_abline(slope = 1, intercept = 0)+
-  scale_color_manual("divergence?",values = c("black","red"))
+plot_parameterrecovery(rw_pp, div = F, subs = 5)
 
-sub_pp <- do.call(rbind, lapply(rw_pp, "[[", 2))
-sub_pp %>% mutate(divergences = ifelse(div > 0,1,0)) %>% 
-  ggplot(aes(x = mean, y = reals.reals))+
-  geom_point(aes(col = as.factor(divergences)))+
-  facet_wrap(~variable, scales = "free")+
-  theme_classic()+
-  geom_abline(slope = 1, intercept = 0)+
-  scale_color_manual("divergence?",values = c("black","red"))
+plot_parameterrecovery(wb_pp, div = F, subs = 5)
 
@@
 ########################################### Resorla wagner parameters:
-mu_alpha = seq(0.1,0.3,length.out = 10)
+mu_alpha = rep(0.3,100)
 kappa_alpha = 50
-mu_w1 = seq(0.1,0.3,length.out = 10)
+mu_w1 = rep(0.3,100)
 kappa_w1 = 50
@@
 
+```
+
+```{r model recovery table:}
+
+get_value = function(loo){
+  get_from_means <- do.call(rbind, lapply(loo, "[[", 1))
+
+  get_from_means$id = as.factor(get_from_means$id)
+# Group by ID and find the model with the minimum value
+  min_values <- get_from_means %>%
+  group_by(id) %>%
+  filter(means == min(means))
+
+# Count the occurrences of each model with the minimum value per run
+  model_counts <- min_values %>%
+    group_by(names) %>%
+    summarize(Count = n())
+
+  get_from_loo <- do.call(rbind, lapply(loo, "[[", 2))
+
+  get_from_loo = get_from_loo %>% filter(elpd_diff == 0) %>% mutate(model = row.names(.)) %>% mutate(realmodel = sub("^[0-9]+\\.(.*)", "\\1", model)) %>% group_by(realmodel) %>% summarize(Count = n())
+
+  return(list(fromloo = get_from_loo, frommean = model_counts))
+}
+
+get_value(rw_loo)
 ```
@@
 
-```{r hierachical session correlation (RW)}
+<!-- ```{r hierachical session correlation (RW)} -->
 
-df= read.csv(here::here("data_TPL_AC.csv")) %>%
-  rename_all(tolower) %>%
-  filter(trial != 0) %>%
-  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
-  mutate_all(replace_na, 0) %>% mutate(id = as.factor(id), trial = as.factor(trial), session = as.factor(session))
+<!-- df= read.csv(here::here("data_TPL_AC.csv")) %>% -->
+<!--   rename_all(tolower) %>% -->
+<!--   filter(trial != 0) %>% -->
+<!--   rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% -->
+<!--   mutate_all(replace_na, 0) %>% mutate(id = as.factor(id), trial = as.factor(trial), session = as.factor(session)) -->
 
-df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
-df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
+<!-- df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0)) -->
+<!-- df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0)) -->
 
-#ratings
-df %>% filter(session == 2) %>% ggplot(aes(x = percept, fill = as.factor(stim))) + geom_histogram()
-#cue-contingency
-df %>% filter(session == 1, id == 1) %>% ggplot(aes(x = trial, y = u)) + geom_point()+theme_classic()
+<!-- #ratings -->
+<!-- df %>% filter(session == 2) %>% ggplot(aes(x = percept, fill = as.factor(stim))) + geom_histogram() -->
+<!-- #cue-contingency -->
+<!-- df %>% filter(session == 1, id == 1) %>% ggplot(aes(x = trial, y = u)) + geom_point()+theme_classic() -->
 
-#fitting hierachically
-data = df %>% mutate(percept = percept/100)
+<!-- #fitting hierachically -->
+<!-- data = df %>% mutate(percept = percept/100) -->
 
-data = data %>% mutate(across(percept, ~case_when(
-    . < 0.001 ~ 0.001,
-    . > 0.999 ~ 0.999,
-    TRUE ~ .
-  )))
+<!-- data = data %>% mutate(across(percept, ~case_when( -->
+<!--     . < 0.001 ~ 0.001, -->
+<!--     . > 0.999 ~ 0.999, -->
+<!--     TRUE ~ . -->
+<!--   ))) -->
 
-data1 = list(nsubs = length(unique(data$id)),
-            ntrials = nrow(data %>% filter(session == 1) %>% filter(id %in% unique(id)[1])),
-            sesions = length(unique(data$session)),
-            percept = get_3darray(data,variable = "percept"),
-            expectPain = get_3darray(data,variable = "pred"),
-            percept_bin = get_3darray(data,variable = "percept_bin"),
-            stim = get_3darray(data,variable = "stim"),
-            cues = get_3darray(data,variable = "cue"),
-            u = get_3darray(data,variable = "u")
-            )
+<!-- data1 = list(nsubs = length(unique(data$id)), -->
+<!--             ntrials = nrow(data %>% filter(session == 1) %>% filter(id %in% unique(id)[1])), -->
+<!--             sesions = length(unique(data$session)), -->
+<!--             percept = get_3darray(data,variable = "percept"), -->
+<!--             expectPain = get_3darray(data,variable = "pred"), -->
+<!--             percept_bin = get_3darray(data,variable = "percept_bin"), -->
+<!--             stim = get_3darray(data,variable = "stim"), -->
+<!--             cues = get_3darray(data,variable = "cue"), -->
+<!--             u = get_3darray(data,variable = "u") -->
+<!--             ) -->
 
-mod = cmdstan_model(here::here("Stan","fitting both sessions","myRW_correlation.stan"))
+<!-- mod = cmdstan_model(here::here("Stan","fitting both sessions","myRW_correlation.stan")) -->
 
-fit <- mod$sample(
-  data = data1,
-  chains = 4,
-  parallel_chains = 4,
-  refresh = 100,
-  adapt_delta = 0.90,
-  max_treedepth = 12
-)
+<!-- fit <- mod$sample( -->
+<!--   data = data1, -->
+<!--   chains = 4, -->
+<!--   parallel_chains = 4, -->
+<!--   refresh = 100, -->
+<!--   adapt_delta = 0.90, -->
+<!--   max_treedepth = 12 -->
+<!-- ) -->
 
-sum = fit$summary(variables = c("mu_alpha","mu_w1","sd_beta","sd_precision_percept", "kappa_alpha","kappa_w1","alpha","w1","beta","precision_percept"))
+<!-- sum = fit$summary(variables = c("mu_alpha","mu_w1","sd_beta","sd_precision_percept", "kappa_alpha","kappa_w1","alpha","w1","beta","precision_percept")) -->
 
-variabless = c("mu_alpha[1]","mu_w1[1]","sd_beta[1]","sd_precision_percept[1]","mu_alpha[2]","mu_w1[2]","sd_beta[2]","sd_precision_percept[2]")
+<!-- variabless = c("mu_alpha[1]","mu_w1[1]","sd_beta[1]","sd_precision_percept[1]","mu_alpha[2]","mu_w1[2]","sd_beta[2]","sd_precision_percept[2]") -->
 
-pairs = mcmc_pairs(fit$draws(variables = variabless), np = nuts_params(fit), pars = variabless,
-                   off_diag_args = list(size = 0.75))
-```
+<!-- pairs = mcmc_pairs(fit$draws(variables = variabless), np = nuts_params(fit), pars = variabless, -->
+<!--                    off_diag_args = list(size = 0.75)) -->
+<!-- ``` -->
 
-```{r hierachical session correlation (WB)}
+<!-- ```{r hierachical session correlation (WB)} -->
 
-df= read.csv(here::here("data_TPL_AC.csv")) %>%
-  rename_all(tolower) %>%
-  filter(trial != 0) %>%
-  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
-  mutate_all(replace_na, 0) %>% mutate(id = as.factor(id), trial = as.factor(trial), session = as.factor(session))
+<!-- df= read.csv(here::here("data_TPL_AC.csv")) %>% -->
+<!--   rename_all(tolower) %>% -->
+<!--   filter(trial != 0) %>% -->
+<!--   rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% -->
+<!--   mutate_all(replace_na, 0) %>% mutate(id = as.factor(id), trial = as.factor(trial), session = as.factor(session)) -->
 
-df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
-df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
+<!-- df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0)) -->
+<!-- df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0)) -->
 
-#fitting hierachically
-data = df %>% mutate(percept = percept/100)
+<!-- #fitting hierachically -->
+<!-- data = df %>% mutate(percept = percept/100) -->
 
-data = data %>% mutate(across(c(percept,stim), ~case_when(
-    . < 0.001 ~ 0.001,
-    . > 0.999 ~ 0.999,
-    TRUE ~ .
-  )))
+<!-- data = data %>% mutate(across(c(percept,stim), ~case_when( -->
+<!--     . < 0.001 ~ 0.001, -->
+<!--     . > 0.999 ~ 0.999, -->
+<!--     TRUE ~ . -->
+<!--   ))) -->
 
-data1 = list(nsubs = length(unique(data$id)),
-            ntrials = nrow(data %>% filter(session == 1) %>% filter(id %in% unique(id)[1])),
-            sesions = length(unique(data$session)),
-            percept = get_3darray(data,variable = "percept"),
-            pred = get_3darray(data,variable = "pred"),
-            percept_bin = get_3darray(data,variable = "percept_bin"),
-            stim = get_3darray(data,variable = "stim"),
-            cue = get_3darray(data,variable = "cue")
-            )
+<!-- data1 = list(nsubs = length(unique(data$id)), -->
+<!--             ntrials = nrow(data %>% filter(session == 1) %>% filter(id %in% unique(id)[1])), -->
+<!--             sesions = length(unique(data$session)), -->
+<!--             percept = get_3darray(data,variable = "percept"), -->
+<!--             pred = get_3darray(data,variable = "pred"), -->
+<!--             percept_bin = get_3darray(data,variable = "percept_bin"), -->
+<!--             stim = get_3darray(data,variable = "stim"), -->
+<!--             cue = get_3darray(data,variable = "cue") -->
+<!--             ) -->
 
-mod = cmdstan_model(here::here("Stan","fitting both sessions","hier_weighted_bayes_correlation.stan"))
+<!-- mod = cmdstan_model(here::here("Stan","fitting both sessions","hier_weighted_bayes_correlation.stan")) -->
 
-fit <- mod$sample(
-  data = data1,
-  chains = 4,
-  parallel_chains = 4,
-  refresh = 100,
-  adapt_delta = 0.90,
-  max_treedepth = 12
-)
+<!-- fit <- mod$sample( -->
+<!--   data = data1, -->
+<!--   chains = 4, -->
+<!--   parallel_chains = 4, -->
+<!--   refresh = 100, -->
+<!--   adapt_delta = 0.90, -->
+<!--   max_treedepth = 12 -->
+<!-- ) -->
 
-```
+<!-- ``` -->
 
-```{r fitting to real data tester hierachical RW session 1}
+<!-- ```{r fitting to both sessions to hierachiacal RW} -->
 
-df= read.csv(here::here("data_TPL_AC.csv")) %>%
-  rename_all(tolower) %>%
-  filter(trial != 0) %>%
-  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
-  mutate_all(replace_na, 0)
+<!-- df= read.csv(here::here("data_TPL_AC.csv")) %>% -->
+<!--   rename_all(tolower) %>% -->
+<!--   filter(trial != 0) %>% -->
+<!--   rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% -->
+<!--   mutate_all(replace_na, 0) -->
 
-df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
-df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
+<!-- df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0)) -->
+<!-- df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0)) -->
 
-df = df %>% filter(session == 1)
+<!-- #source(here::here("stan_functions.R")) -->
+<!-- #fitting hierachically -->
+<!-- data = df %>% mutate(percept = percept/100) -->
 
-#source(here::here("stan_functions.R"))
-#fitting hierachically
-data = df %>% mutate(percept = percept/100)
+<!-- data = data %>% mutate(across(percept, ~case_when( -->
+<!--     . < 0.001 ~ 0.001, -->
+<!--     . > 0.999 ~ 0.999, -->
+<!--     TRUE ~ . -->
+<!--   ))) -->
 
-data = data %>% mutate(across(percept, ~case_when(
-    . < 0.001 ~ 0.001,
-    . > 0.999 ~ 0.999,
-    TRUE ~ .
-  )))
+<!-- data1 = list(nsubs = length(unique(data$id)), -->
+<!--             ntrials = nrow(data %>% filter(session == 1) %>% filter(id %in% unique(id)[1])), -->
+<!--             sessions = 2, -->
+<!--             pred = get_3darray(data,variable = "pred"), -->
+<!--             u = get_3darray(data,variable = "u") -->
+<!--             ) -->
 
-data1 = list(nsubs = length(unique(data$id)),
-            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
-            pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
-            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL))
-            )
+<!-- mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier.stan")) -->
 
-mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier.stan"))
+<!-- rw_fit_ses1 <- mod$sample( -->
+<!--       data = data1, -->
+<!--       chains = 4, -->
+<!--       parallel_chains = 4, -->
+<!--       refresh = 100, -->
+<!--       adapt_delta = 0.90, -->
+<!--       max_treedepth = 12 -->
+<!--     ) -->
 
-rw_fit_ses1 <- mod$sample(
-      data = data1,
-      chains = 4,
-      parallel_chains = 4,
-      refresh = 100,
-      adapt_delta = 0.90,
-      max_treedepth = 12
-    )
+<!-- sum = rw_fit_ses1$summary(variables = c("alpha", "mu_alpha","sd_alpha","mu_mu_alpha","sd_sd_alpha","mu_sd_alpha","sd_mu_alpha")) -->
+<!-- ``` -->
 
-sum = rw_fit_ses1$summary(variables = c("alpha_1"))
+<!-- ```{r, fitting to real data tester hierachical RW sessions1} -->
+<!-- df= read.csv(here::here("data_TPL_AC.csv")) %>% -->
+<!--   rename_all(tolower) %>% -->
+<!--   filter(trial != 0) %>% -->
+<!--   rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% -->
+<!--   mutate_all(replace_na, 0) -->
 
-```
+<!-- df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0)) -->
+<!-- df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0)) -->
 
-```{r fitting to real data tester hierachical RW seesion2}
+<!-- df = df %>% filter(session == 1) -->
 
-df= read.csv(here::here("data_TPL_AC.csv")) %>%
-  rename_all(tolower) %>%
-  filter(trial != 0) %>%
-  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
-  mutate_all(replace_na, 0)
+<!-- #source(here::here("stan_functions.R")) -->
+<!-- #fitting hierachically -->
+<!-- data = df %>% mutate(percept = percept/100) -->
 
-df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
-df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
+<!-- data = data %>% mutate(across(percept, ~case_when( -->
+<!--     . < 0.001 ~ 0.001, -->
+<!--     . > 0.999 ~ 0.999, -->
+<!--     TRUE ~ . -->
+<!--   ))) -->
 
-df = df %>% filter(session == 2)
+<!-- data2 = list(nsubs = length(unique(data$id)), -->
+<!--             ntrials = nrow(data %>% filter(id %in% unique(id)[1])), -->
+<!--             pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)), -->
+<!--             u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL)) -->
+<!--             ) -->
 
-#source(here::here("stan_functions.R"))
-#fitting hierachically
-data = df %>% mutate(percept = percept/100)
+<!-- mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier.stan")) -->
 
-data = data %>% mutate(across(percept, ~case_when(
-    . < 0.001 ~ 0.001,
-    . > 0.999 ~ 0.999,
-    TRUE ~ .
-  )))
+<!-- rw_fit_ses1 <- mod$sample( -->
+<!--       data = data2, -->
+<!--       chains = 4, -->
+<!--       parallel_chains = 4, -->
+<!--       refresh = 100, -->
+<!--       adapt_delta = 0.90, -->
+<!--       max_treedepth = 12 -->
+<!--     ) -->
 
-data2 = list(nsubs = length(unique(data$id)),
-            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
-            pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
-            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL))
-            )
+<!-- ``` -->
 
-mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier.stan"))
+<!-- ```{r fitting to real data tester hierachical RW seesion2} -->
 
-rw_fit_ses2 <- mod$sample(
-      data = data2,
-      chains = 4,
-      parallel_chains = 4,
-      refresh = 100,
-      adapt_delta = 0.90,
-      max_treedepth = 12
-    )
+<!-- df= read.csv(here::here("data_TPL_AC.csv")) %>% -->
+<!--   rename_all(tolower) %>% -->
+<!--   filter(trial != 0) %>% -->
+<!--   rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% -->
+<!--   mutate_all(replace_na, 0) -->
 
-sums2 = rw_fit_ses2$summary(variables = c("alpha_1"))
+<!-- df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0)) -->
+<!-- df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0)) -->
 
-```
+<!-- df = df %>% filter(session == 2) -->
+
+<!-- #source(here::here("stan_functions.R")) -->
+<!-- #fitting hierachically -->
+<!-- data = df %>% mutate(percept = percept/100) -->
+
+<!-- data = data %>% mutate(across(percept, ~case_when( -->
+<!--     . < 0.001 ~ 0.001, -->
+<!--     . > 0.999 ~ 0.999, -->
+<!--     TRUE ~ . -->
+<!--   ))) -->
+
+<!-- data2 = list(nsubs = length(unique(data$id)), -->
+<!--             ntrials = nrow(data %>% filter(id %in% unique(id)[1])), -->
+<!--             pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)), -->
+<!--             u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL)) -->
+<!--             ) -->
+
+<!-- mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier.stan")) -->
+
+<!-- rw_fit_ses2 <- mod$sample( -->
+<!--       data = data2, -->
+<!--       chains = 4, -->
+<!--       parallel_chains = 4, -->
+<!--       refresh = 100, -->
+<!--       adapt_delta = 0.90, -->
+<!--       max_treedepth = 12 -->
+<!--     ) -->
+
+<!-- ``` -->

### 2023-05-23 scripts/visualize_parameters.R

@@ -239,3 +239,68 @@ WB = function(dd){
   
   
 }
+
+
+plot_parameterrecovery = function(pp, div, subs){
+  
+  if(div){
+  hier_pp <- do.call(rbind, lapply(pp, "[[", 1))
+  sub_pp <- do.call(rbind, lapply(pp, "[[", 2))
+  }else{
+    hier_pp <- do.call(rbind, lapply(pp, "[[", 1)) %>% filter(div < 1)
+    sub_pp <- do.call(rbind, lapply(pp, "[[", 2)) %>% filter(div < 1)
+  }
+  
+  hier = hier_pp %>% mutate(divergences = ifelse(div > 0,1,0)) %>% 
+    ggplot(aes(x = mean, y = reals.reals))+
+    {if(div)geom_point(aes(col = as.factor(divergences)))}+
+    geom_point()+
+    facet_wrap(~variable, scales = "free")+
+    theme_classic()+
+    geom_abline(slope = 1, intercept = 0)+
+    scale_color_manual("divergence?",values = c("black","red"))
+  
+
+  # Generate the regular expression pattern dynamically
+  pattern <- paste0("\\[", 1:subs, "\\]")
+  
+  # Filter the column
+  sub_pp <- sub_pp[grepl(paste(pattern, collapse = "|"), sub_pp$variable), ]
+  
+  
+  sub = sub_pp %>% mutate(divergences = ifelse(div > 0,1,0)) %>% 
+    ggplot(aes(x = mean, y = reals.reals))+
+    {if(div)geom_point(aes(col = as.factor(divergences)))}+
+    geom_point()+
+    facet_wrap(~variable, scales = "free", ncol = subs)+
+    theme_classic()+
+    geom_abline(slope = 1, intercept = 0)+
+    scale_color_manual("divergence?",values = c("black","red"))
+  
+  return(list(hier = hier,sub = sub))
+  
+}
+
+
+get_corplot = function(fit1,fit2,variable){
+  
+  df1 = (fit1$summary(variables = variable))
+  df2 = (fit2$summary(variables = variable))
+  
+  df1$sess = df2$mean
+  
+  df1$sess_sd = df2$sd
+  
+  
+  plot = df1 %>% ggplot(aes(x = mean, y = sess)) +
+    geom_point() +
+    geom_errorbar(aes(ymin = sess - sess_sd, ymax = sess + sess_sd), width = 0.005,linetype = "dashed") +
[…]

### 2023-05-24 Manuscript1.Rmd
updates

--- 2023-05-23 Manuscript.Rmd
@@
 
-#ratings
-df %>% filter(session == 2) %>% ggplot(aes(x = percept, fill = as.factor(stim))) + geom_histogram()
-#cue-contingency
-df %>% filter(session == 1, id == 1) %>% ggplot(aes(x = trial, y = u)) + geom_point()+theme_classic()
-
 df = df %>% filter(session == 1)
@@
 
+ppu_hier(fit = rw_fit_sess1,
+         parameters = c("alpha","w1","precision_percept"),
+         reals = NA)
+
+```
+
+```{r plotting 1 agent}
+
+percept = sum %>% filter(str_detect(variable, "painMu"))
+percept = percept[1:160,]
+
+expect = sum %>% filter(str_detect(variable, "expectMu"))
+expect = expect[1:160,]
+
+percept$stim = data$stim
+percept$expect = expect$mean
+
+percept %>% ggplot(aes(x=1:nrow(.), y = mean, col = as.factor(stim)))+geom_point()
+
+percept %>% ggplot(aes(x=expect, y = mean, col = as.factor(stim)))+geom_point()
+
+ass = sum %>% filter(str_detect(variable, "associ"))
+ass = ass[1:161,]
+
+ass %>% ggplot(aes(x=1:nrow(.), y = mean))+geom_line()+geom_point(data = data, aes(x = trial, y = u))
+
 rw_fit_sess1$diagnostic_summary()
+
+alpha = get_diag(rw_fit_sess1, "alpha")
+w1 = get_diag(rw_fit_sess1, "w1")
+pp = get_diag(rw_fit_sess1, "precision_percept")
+beta = get_diag(rw_fit_sess1, "beta")
+
 ```
@@
 df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
-
-#ratings
-df %>% filter(session == 2) %>% ggplot(aes(x = percept, fill = as.factor(stim))) + geom_histogram()
-#cue-contingency
-df %>% filter(session == 1, id == 1) %>% ggplot(aes(x = trial, y = u)) + geom_point()+theme_classic()
 
@@
 
-rw_fit_sess2$diagnostic_summary()
+ppu_hier(fit = rw_fit_sess2,
+         parameters = c("alpha","w1","precision_percept"),
+         reals = NA)
 
@@
 
-mod = cmdstan_model(here::here("Stan","no generated quantities","myKalmanfilter_v2_nogen_nocent.stan"))
+mod = cmdstan_model(here::here("Stan","myKalmanfilter_v3_nocent.stan"))
 
@@
 
-diag_sigmaEta = get_diag(fit = kalman_fit_sess1,
-         parameter = "sigmaEta")
+ppu_hier(fit = kalman_fit_sess1,
+         parameters = c("sigmaEta","sigmaPsi","sigmaEpsilon","precision_percept"),
+         reals = NA)
 
-diag_sigmaPsi = get_diag(fit = kalman_fit_sess1,
-         parameter = "sigmaPsi")
+# 
+# ppu_sub(fit = fit,
+#         parameter = "precision_percept",
+#         reals = df,
+#         lims = -1,
+#         lime = 10,
+#         nsubs = NA
+#         )
 
-diag_sigmaEpsilon = get_diag(fit = kalman_fit_sess1,
-         parameter = "sigmaEpsilon")
+get_diag(kalman_fit_sess1, "sigmaEta")
+get_diag(kalman_fit_sess1, "sigmaPsi")
+get_diag(kalman_fit_sess1, "sigmaEpsilon")
 
-diag_sigmabeta = get_diag(fit = kalman_fit_sess1,
-         parameter = "beta")
+sum = kalman_fit_sess1$summary()
 
-diag_precision_percept = get_diag(fit = kalman_fit_sess1,
-         parameter = "precision_percept")
+ass = sum %>% filter(str_detect(variable, "perceptmuu"))
+ass = ass[(161*2-1):(161*3-1),]
+
+exp = sum %>% filter(str_detect(variable, "exp_muu"))
+exp = exp[(161*2-1):(161*3-1),]
+
+ass$exp = exp$mean
+
+ass %>% ggplot(aes(x=exp, y = mean))+geom_point()
+
 ```
@@
 
-mod = cmdstan_model(here::here("Stan","no generated quantities","myKalmanfilter_v2_nogen_nocent.stan"))
+mod = cmdstan_model(here::here("Stan","myKalmanfilter_v2_nocent.stan"))
 
@@
     )
+
+wb_fit_sess1$diagnostic_summary()
+
+alpha = get_diag(wb_fit_sess1, "alpha")
+w1 = get_diag(wb_fit_sess1, "w1")
+w2 = get_diag(wb_fit_sess1, "w2")
+pp = get_diag(wb_fit_sess1, "percept_precision")
+beta = get_diag(wb_fit_sess1, "beta")
+
 ```
@@
 
-w7b_fit_sess2 <- mod$sample(
+wb_fit_sess2 <- mod$sample(
       data = data1,
@@
     )
+
+alpha = get_diag(wb_fit_sess1, "alpha")
+w1 = get_diag(wb_fit_sess1, "w1")
+w2 = get_diag(wb_fit_sess1, "w2")
+pp = get_diag(wb_fit_sess1, "percept_precision")
+beta = get_diag(wb_fit_sess1, "beta")
+
+```
+
+```{r}
+get_corplot(rw_fit_sess1, rw_fit_sess2, "alpha")
+get_corplot(rw_fit_sess1, rw_fit_sess2, "w1")
+get_corplot(rw_fit_sess1, rw_fit_sess2, "precision_percept")
+
+get_corplot(wb_fit_sess1, wb_fit_sess2, "alpha")
+get_corplot(wb_fit_sess1, wb_fit_sess2, "w1")
+get_corplot(wb_fit_sess1, wb_fit_sess2, "w2")
+get_corplot(wb_fit_sess1, wb_fit_sess2, "beta")
+get_corplot(wb_fit_sess1, wb_fit_sess2, "percept_precision")
 

### 2023-05-24 scripts/visualize_parameters.R

@@ -174,9 +174,6 @@ KALMAN_v2 = function(dd){
   
 }
 
-
-
-
 WB = function(dd){
   
   
@@ -283,7 +280,8 @@ plot_parameterrecovery = function(pp, div, subs){
 
 
 get_corplot = function(fit1,fit2,variable){
-  
+
+
   df1 = (fit1$summary(variables = variable))
   df2 = (fit2$summary(variables = variable))
   
@@ -292,12 +290,18 @@ get_corplot = function(fit1,fit2,variable){
   df1$sess_sd = df2$sd
   
   
+  fit <- lsfit(x = df1$sess, y = df1$mean, weights = list(x = df1$sess_sd, y = df1$sd))
+  
+  # Extract the correlation coefficient
+  correlation <- cor(fit$residuals$x, fit$residuals$y)
+  
+
   plot = df1 %>% ggplot(aes(x = mean, y = sess)) +
     geom_point() +
     geom_errorbar(aes(ymin = sess - sess_sd, ymax = sess + sess_sd), width = 0.005,linetype = "dashed") +
     geom_errorbarh(aes(xmin = mean - sd, xmax = mean + sd), height = 0.005,linetype = "dashed") +
     labs(x = "Session 1", y = "Session 2") +
-    ggtext::geom_richtext(aes(x = 0.1, y = 0.9,
+    ggtext::geom_richtext(aes(x = min(mean)+sd(mean), y = max(sess),
                               label = paste0("r = ",round(cor.test(df1$mean, df1$sess)$estimate[[1]],2), " [", round(cor.test(df1$mean, df1$sess)$conf.int[[1]],2)," ; ", round(cor.test(df1$mean, df1$sess)$conf.int[[2]],2),"]")))+ggtitle(paste0("test retest correlation of ",variable))+
     theme_classic()
   

### 2023-05-25 Manuscript1.Rmd
updates

@@
 
-mod = cmdstan_model(here::here("Stan","myKalmanfilter_v2_nocent.stan"))
+mod = cmdstan_model(here::here("Stan","myKalmanfilter_v3_nocent.stan"))
 
@@
     )
+
+ppu_hier(fit = kalman_fit_sess2,
+         parameters = c("sigmaEta","sigmaPsi","sigmaEpsilon","precision_percept"),
+         reals = NA)
+
 ```
@@
 
-<!-- ```{r hierachical session correlation (RW)} -->
+```{r}
+df= read.csv(here::here("data_TPL_AC.csv")) %>%
+  rename_all(tolower) %>%
+  filter(trial != 0) %>%
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
+  mutate_all(replace_na, 0)
 
-<!-- df= read.csv(here::here("data_TPL_AC.csv")) %>% -->
-<!--   rename_all(tolower) %>% -->
-<!--   filter(trial != 0) %>% -->
-<!--   rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% -->
-<!--   mutate_all(replace_na, 0) %>% mutate(id = as.factor(id), trial = as.factor(trial), session = as.factor(session)) -->
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
 
-<!-- df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0)) -->
-<!-- df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0)) -->
+df = df %>% filter(session == 1)
 
-<!-- #ratings -->
-<!-- df %>% filter(session == 2) %>% ggplot(aes(x = percept, fill = as.factor(stim))) + geom_histogram() -->
-<!-- #cue-contingency -->
-<!-- df %>% filter(session == 1, id == 1) %>% ggplot(aes(x = trial, y = u)) + geom_point()+theme_classic() -->
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
 
-<!-- #fitting hierachically -->
-<!-- data = df %>% mutate(percept = percept/100) -->
+data = data %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
 
-<!-- data = data %>% mutate(across(percept, ~case_when( -->
-<!--     . < 0.001 ~ 0.001, -->
-<!--     . > 0.999 ~ 0.999, -->
-<!--     TRUE ~ . -->
-<!--   ))) -->
+data1 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
+            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
+            expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
+            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
+            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)),
+            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL))
+            )
 
-<!-- data1 = list(nsubs = length(unique(data$id)), -->
-<!--             ntrials = nrow(data %>% filter(session == 1) %>% filter(id %in% unique(id)[1])), -->
-<!--             sesions = length(unique(data$session)), -->
-<!--             percept = get_3darray(data,variable = "percept"), -->
-<!--             expectPain = get_3darray(data,variable = "pred"), -->
-<!--             percept_bin = get_3darray(data,variable = "percept_bin"), -->
-<!--             stim = get_3darray(data,variable = "stim"), -->
-<!--             cues = get_3darray(data,variable = "cue"), -->
-<!--             u = get_3darray(data,variable = "u") -->
-<!--             ) -->
+mod = cmdstan_model(here::here("Stan","myKalmanfilter_v3_nocent.stan"))
 
-<!-- mod = cmdstan_model(here::here("Stan","fitting both sessions","myRW_correlation.stan")) -->
+kalman_fit_sess1 <- mod$sample(
+      data = data1,
+      chains = 4,
+      parallel_chains = 4,
+      refresh = 100,
+      adapt_delta = 0.90,
+      max_treedepth = 12
+    )
+```
 
-<!-- fit <- mod$sample( -->
-<!--   data = data1, -->
-<!--   chains = 4, -->
-<!--   parallel_chains = 4, -->
-<!--   refresh = 100, -->
-<!--   adapt_delta = 0.90, -->
-<!--   max_treedepth = 12 -->
-<!-- ) -->
+```{r hierachical session correlation (RW)}
 
-<!-- sum = fit$summary(variables = c("mu_alpha","mu_w1","sd_beta","sd_precision_percept", "kappa_alpha","kappa_w1","alpha","w1","beta","precision_percept")) -->
+df= read.csv(here::here("data_TPL_AC.csv")) %>%
+  rename_all(tolower) %>%
+  filter(trial != 0) %>%
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
+  mutate_all(replace_na, 0) %>% mutate(id = as.factor(id), trial = as.factor(trial), session = as.factor(session))
 
-<!-- variabless = c("mu_alpha[1]","mu_w1[1]","sd_beta[1]","sd_precision_percept[1]","mu_alpha[2]","mu_w1[2]","sd_beta[2]","sd_precision_percept[2]") -->
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
 
-<!-- pairs = mcmc_pairs(fit$draws(variables = variabless), np = nuts_params(fit), pars = variabless, -->
-<!--                    off_diag_args = list(size = 0.75)) -->
-<!-- ``` -->
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
 
-<!-- ```{r hierachical session correlation (WB)} -->
+data = data %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
 
-<!-- df= read.csv(here::here("data_TPL_AC.csv")) %>% -->
-<!--   rename_all(tolower) %>% -->
-<!--   filter(trial != 0) %>% -->
-<!--   rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% -->
-<!--   mutate_all(replace_na, 0) %>% mutate(id = as.factor(id), trial = as.factor(trial), session = as.factor(session)) -->
+data1 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(session == 1) %>% filter(id %in% unique(id)[1])),
+            sesions = length(unique(data$session)),
+            percept = get_3darray(data,variable = "percept"),
+            expectPain = get_3darray(data,variable = "pred"),
+            percept_bin = get_3darray(data,variable = "percept_bin"),
+            stim = get_3darray(data,variable = "stim"),
+            cues = get_3darray(data,variable = "cue"),
+            u = get_3darray(data,variable = "u")
+            )
 
-<!-- df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0)) -->
-<!-- df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0)) -->
+mod = cmdstan_model(here::here("Stan","fitting both sessions","myRW_real_both_sess.stan"))
 
-<!-- #fitting hierachically -->
-<!-- data = df %>% mutate(percept = percept/100) -->
+fit <- mod$sample(
+  data = data1,
+  chains = 4,
+  parallel_chains = 4,
+  refresh = 100,
+  adapt_delta = 0.90,
+  max_treedepth = 12
+)
 
-<!-- data = data %>% mutate(across(c(percept,stim), ~case_when( -->
-<!--     . < 0.001 ~ 0.001, -->
-<!--     . > 0.999 ~ 0.999, -->
-<!--     TRUE ~ . -->
-<!--   ))) -->
+sum = fit$summary(variables = c("mu_alpha","mu_w1","sd_beta","sd_precision_percept", "kappa_alpha","kappa_w1","alpha","w1","beta","precision_percept"))
 
-<!-- data1 = list(nsubs = length(unique(data$id)), -->
-<!--             ntrials = nrow(data %>% filter(session == 1) %>% filter(id %in% unique(id)[1])), -->
-<!--             sesions = length(unique(data$session)), -->
-<!--             percept = get_3darray(data,variable = "percept"), -->
-<!--             pred = get_3darray(data,variable = "pred"), -->
-<!--             percept_bin = get_3darray(data,variable = "percept_bin"), -->
-<!--             stim = get_3darray(data,variable = "stim"), -->
-<!--             cue = get_3darray(data,variable = "cue") -->
-<!--             ) -->
+variabless = c("mu_alpha[1]","mu_w1[1]","sd_beta[1]","sd_precision_percept[1]","mu_alpha[2]","mu_w1[2]","sd_beta[2]","sd_precision_percept[2]")
 
-<!-- mod = cmdstan_model(here::here("Stan","fitting both sessions","hier_weighted_bayes_correlation.stan")) -->
+pairs = mcmc_pairs(fit$draws(variables = variabless), np = nuts_params(fit), pars = variabless,
+                   off_diag_args = list(size = 0.75))
 
-<!-- fit <- mod$sample( -->
-<!--   data = data1, -->
-<!--   chains = 4, -->
-<!--   parallel_chains = 4, -->
-<!--   refresh = 100, -->
-<!--   adapt_delta = 0.90, -->
-<!--   max_treedepth = 12 -->
-<!-- ) -->
+mcmc_trace(fit$draws(variables = "alpha"))
 
-<!-- ``` -->
+alpha = fit$summary(variables = "alpha")
+w1 = fit$summary(variables = "w1")
+
+alphas1 <- w1 %>%
+  filter(grepl("1]$", variable))
+
+alphas2 <- w1 %>%
+  filter(grepl("2]$", variable))
+
+cor.test(alphas1$mean, alphas2$mean)
+
+correlation = as_draws_df(fit$draws(variables = "correlation_alpha"))
+hist(correlation$correlation_alpha)
+correlation = as_draws_df(fit$draws(variables = "correlation_w1"))
+hist(correlation$correlation_w1)
+```
+
+```{r hierachical session correlation (WB)}
+
+df= read.csv(here::here("data_TPL_AC.csv")) %>%
+  rename_all(tolower) %>%
+  filter(trial != 0) %>%
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
+  mutate_all(replace_na, 0) %>% mutate(id = as.factor(id), trial = as.factor(trial), session = as.factor(session))
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(c(percept,stim), ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data1 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(session == 1) %>% filter(id %in% unique(id)[1])),
+            sesions = length(unique(data$session)),
+            percept = get_3darray(data,variable = "percept"),
+            pred = get_3darray(data,variable = "pred"),
+            percept_bin = get_3darray(data,variable = "percept_bin"),
+            stim = get_3darray(data,variable = "stim"),
+            cue = get_3darray(data,variable = "cue")
+            )
+
+mod = cmdstan_model(here::here("Stan","fitting both sessions","hier_weighted_bayes_correlation.stan"))
+
+fit_wb_bs <- mod$sample(
+  data = data1,
+  chains = 4,
+  parallel_chains = 4,
+  refresh = 100,
+  adapt_delta = 0.90,
+  max_treedepth = 12
+)
+
+correlation = as_draws_df(fit_wb_bs$draws(variables = "correlation_alpha"))
+hist(correlation$correlation_alpha)
+correlation = as_draws_df(fit_wb_bs$draws(variables = "correlation_w1"))
+hist(correlation$correlation_w1)
+correlation = as_draws_df(fit_wb_bs$draws(variables = "correlation_w2"))
+hist(correlation$correlation_w2)
+
+```
 

### 2023-05-25 scripts/parameter_recovery.R

@@ -170,7 +170,7 @@ parameter_recovery_kalman = function(parameters){
                u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL))
   )
   
-  mod = cmdstan_model(here::here("Stan","no generated quantities","myKalmanfilter_v2_nogen_nocent.stan"))
+  mod = cmdstan_model(here::here("Stan","no generated quantities","myKalmanfilter_v2_nogen.stan"))
   
   
   fitter = function(){
@@ -183,16 +183,11 @@ parameter_recovery_kalman = function(parameters){
       max_treedepth = 12
     )
     
-        return(fit)
+    return(fit)
   }
   
   
-  fit <- tryCatch({
-    fit = withTimeout(fitter(), timeout = 1500, cpu = 1500)
-  }, error = function(e) {
-    print("An error occurred!")
-    return(NA)
-  })
+  fit <- fitter()
   
   
   

### 2023-05-25 scripts/parameter_recovery.R
updates

@@ -200,7 +200,8 @@ parameter_recovery_kalman = function(parameters){
     sub_parameters = c("sigmaEpsilon","sigmaEta","sigmaPsi")
     return(list(hier = data.frame(fit$summary(hier_parameters),
                                   reals = hier %>% dplyr::select(all_of(hier_parameters)) %>% pivot_longer(everything()) %>% rename(reals = value),
-                                  div = sum(fit$diagnostic_summary()$num_divergent),index = index),
+                                  div = sum(fit$diagnostic_summary()$num_divergent),
+                                  index = index),
                 sub = data.frame(fit$summary(sub_parameters) %>% arrange(variable),
                                  reals = df %>% filter(trial == 1) %>% mutate(ids = 1:nrow(.)) %>% dplyr::select(all_of(sub_parameters),ids) %>% pivot_longer(cols = -ids) %>% rename(reals =value) %>% mutate(names = paste0(name,"[",ids,"]")) %>% arrange(names) %>% select(names,reals),
                                  div = sum(fit$diagnostic_summary()$num_divergent),index = index)))}else{

### 2023-05-26 Manuscript1.Rmd
updates

@@
 knitr::opts_chunk$set(echo = TRUE)
-pacman::p_load(tidyverse, osfr, lmerTest, MuMIn, DHARMa, here, cmdstanr, tidybayes, bayesplot, posterior,future,furrr, patchwork, R.utils, brms, extraDistr)
+pacman::p_load(tidyverse, osfr, lmerTest, MuMIn, DHARMa, here, cmdstanr, tidybayes, bayesplot, posterior,future,furrr, patchwork, R.utils, brms, extraDistr,cowplot)
 
@@
 
-plot_spacer()+kalmanplot+rwplot+wbplot+plot_layout(design = layout)
-
+trial_struc = ggdraw() +
+  draw_image(magick::image_read(here::here("figures", "main-experiment.PNG")), scale = 1.5)
+
+trial_struc+kalmanplot+rwplot+wbplot+plot_layout(design = layout)+plot_annotation(tag_levels = 'A')
+
+RW_logistic = RW_logistic_vis(dd)
 ```
@@
 plot_parameterrecovery(wb_pp, div = F, subs = 5)
+
+plot_parameterrecovery(kalman_pp, div = T, subs = 5)
 
@@
 
-<!-- ```{r fitting to both sessions to hierachiacal RW} -->
-
-<!-- df= read.csv(here::here("data_TPL_AC.csv")) %>% -->
-<!--   rename_all(tolower) %>% -->
-<!--   filter(trial != 0) %>% -->
-<!--   rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% -->
-<!--   mutate_all(replace_na, 0) -->
-
-<!-- df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0)) -->
-<!-- df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0)) -->
-
-<!-- #source(here::here("stan_functions.R")) -->
-<!-- #fitting hierachically -->
-<!-- data = df %>% mutate(percept = percept/100) -->
-
-<!-- data = data %>% mutate(across(percept, ~case_when( -->
-<!--     . < 0.001 ~ 0.001, -->
-<!--     . > 0.999 ~ 0.999, -->
-<!--     TRUE ~ . -->
-<!--   ))) -->
-
-<!-- data1 = list(nsubs = length(unique(data$id)), -->
-<!--             ntrials = nrow(data %>% filter(session == 1) %>% filter(id %in% unique(id)[1])), -->
-<!--             sessions = 2, -->
-<!--             pred = get_3darray(data,variable = "pred"), -->
-<!--             u = get_3darray(data,variable = "u") -->
-<!--             ) -->
-
-<!-- mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier.stan")) -->
-
-<!-- rw_fit_ses1 <- mod$sample( -->
-<!--       data = data1, -->
-<!--       chains = 4, -->
-<!--       parallel_chains = 4, -->
-<!--       refresh = 100, -->
-<!--       adapt_delta = 0.90, -->
-<!--       max_treedepth = 12 -->
-<!--     ) -->
-
-<!-- sum = rw_fit_ses1$summary(variables = c("alpha", "mu_alpha","sd_alpha","mu_mu_alpha","sd_sd_alpha","mu_sd_alpha","sd_mu_alpha")) -->
-<!-- ``` -->
-
-<!-- ```{r, fitting to real data tester hierachical RW sessions1} -->
-<!-- df= read.csv(here::here("data_TPL_AC.csv")) %>% -->
-<!--   rename_all(tolower) %>% -->
-<!--   filter(trial != 0) %>% -->
-<!--   rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% -->
-<!--   mutate_all(replace_na, 0) -->
-
-<!-- df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0)) -->
-<!-- df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0)) -->
-
-<!-- df = df %>% filter(session == 1) -->
-
-<!-- #source(here::here("stan_functions.R")) -->
-<!-- #fitting hierachically -->
-<!-- data = df %>% mutate(percept = percept/100) -->
-
-<!-- data = data %>% mutate(across(percept, ~case_when( -->
-<!--     . < 0.001 ~ 0.001, -->
-<!--     . > 0.999 ~ 0.999, -->
-<!--     TRUE ~ . -->
-<!--   ))) -->
-
-<!-- data2 = list(nsubs = length(unique(data$id)), -->
-<!--             ntrials = nrow(data %>% filter(id %in% unique(id)[1])), -->
-<!--             pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)), -->
-<!--             u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL)) -->
-<!--             ) -->
-
-<!-- mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier.stan")) -->
-
-<!-- rw_fit_ses1 <- mod$sample( -->
-<!--       data = data2, -->
-<!--       chains = 4, -->
-<!--       parallel_chains = 4, -->
-<!--       refresh = 100, -->
-<!--       adapt_delta = 0.90, -->
-<!--       max_treedepth = 12 -->
-<!--     ) -->
-
-<!-- ``` -->
+```{r fitting to both sessions to hierachiacal RW}
+
+df= read.csv(here::here("data_TPL_AC.csv")) %>%
+  rename_all(tolower) %>%
+  filter(trial != 0) %>%
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
+  mutate_all(replace_na, 0)
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
+
+#source(here::here("stan_functions.R"))
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data1 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(session == 1) %>% filter(id %in% unique(id)[1])),
+            sessions = 2,
+            pred = get_3darray(data,variable = "pred"),
+            u = get_3darray(data,variable = "u")
+            )
+
+mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier.stan"))
+
+rw_fit_ses1 <- mod$sample(
+      data = data1,
+      chains = 4,
+      parallel_chains = 4,
+      refresh = 100,
+      adapt_delta = 0.90,
+      max_treedepth = 12
+    )
+
+sum = rw_fit_ses1$summary(variables = c("alpha", "mu_alpha","sd_alpha","mu_mu_alpha","sd_sd_alpha","mu_sd_alpha","sd_mu_alpha"))
+```
+
+```{r, fitting to real data tester hierachical RW sessions1}
+
+df= read.csv(here::here("data_TPL_AC.csv")) %>%
+  rename_all(tolower) %>%
+  filter(trial != 0) %>%
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
+  mutate_all(replace_na, 0)
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
+
+df = df %>% filter(session == 1)
+
+#source(here::here("stan_functions.R"))
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data2 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
+            pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
+            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
+            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
+            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL)),
+            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL))
+            )
+
+mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier_complete.stan"))
+
+rw_fit_ses1 <- mod$sample(
+      data = data2,
+      chains = 4,
+      parallel_chains = 4,
+      refresh = 100,
+      adapt_delta = 0.90,
+      max_treedepth = 12
+    )
+
+sum1 = rw_fit_ses1$summary()
+```
+
+```{r, fitting to real data tester hierachical RW sessions2}
+
+df= read.csv(here::here("data_TPL_AC.csv")) %>%
+  rename_all(tolower) %>%
+  filter(trial != 0) %>%
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
+  mutate_all(replace_na, 0)
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
+
+df = df %>% filter(session == 2)
+
+#source(here::here("stan_functions.R"))
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data2 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
+            pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
+            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
+            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
+            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL)),
+            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL))
+            )
+
+mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier_complete.stan"))
+
+rw_fit_ses2 <- mod$sample(
+      data = data2,
+      chains = 4,
+      parallel_chains = 4,
+      refresh = 100,
+      adapt_delta = 0.90,
+      max_treedepth = 12
+    )
+
+sum2 = rw_fit_ses2$summary()
+
+get_corplot(rw_fit_ses1,rw_fit_ses2, "b2_b")
+```
+
+```{r}
+
+df= read.csv(here::here("data_TPL_AC.csv")) %>%
+  rename_all(tolower) %>%
+  filter(trial != 0) %>%
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
+  mutate_all(replace_na, 0) %>% mutate(id = as.factor(id), trial = as.factor(trial), session = as.factor(session))
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
+
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data1 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(session == 1) %>% filter(id %in% unique(id)[1])),
+            sesions = length(unique(data$session)),
+            percept = get_3darray(data,variable = "percept"),
+            pred = get_3darray(data,variable = "pred"),
+            percept_bin = get_3darray(data,variable = "percept_bin"),
+            stim = get_3darray(data,variable = "stim"),
+            cues = get_3darray(data,variable = "cue"),
+            u = get_3darray(data,variable = "u")
+            )
+
+mod = cmdstan_model(here::here("Stan","fitting both sessions","rw_vs_rw_hier_complete_both_sessions.stan"))
+
+fit <- mod$sample(
+  data = data1,
+  chains = 4,
+  parallel_chains = 4,
+  refresh = 10,
+  adapt_delta = 0.90,
+  max_treedepth = 12
+)
+
+```
+
+```{r}
+mu_alpha = 0.3
+kappa_alpha = 30
+
+mu_b0 = -5
+sd_b0 = 1
+
+mu_b1 = -1
+sd_b1 = 1
+
+mu_b2 = 1.3
+sd_b2 = 1.3
+
+mu_b0_b = -5
+sd_b0_b = 2
+
+mu_b1_b = 0.5
+sd_b1_b = 0.5
+
+mu_b2_b = 0.5
+sd_b2_b = 0.5
+
+sd_percept_precision = 0.5
+
+nsubs = 10
+
+parameters = expand.grid(mu_alpha = mu_alpha,
+                         kappa_alpha = kappa_alpha,
+                         mu_b0 = mu_b0,
+                         sd_b0 = sd_b0,
+                         mu_b1 = mu_b1,
+                         sd_b1 = sd_b1,
+                         mu_b2 = mu_b2,
+                         sd_b2 = sd_b2,
+                         mu_b0_b = mu_b0_b,
+                         sd_b0_b = sd_b0_b,
+                         mu_b1_b = mu_b1_b,
+                         sd_b1_b = sd_b1_b,
+                         mu_b2_b = mu_b2_b,
+                         sd_b2_b = sd_b2_b,
+                         sd_percept_precision = sd_percept_precision,
+                         nsubs = nsubs)
+
+df = hier_rw_logistic(parameters)
+
+data = df[[1]]
+
+data2 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
+            pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
+            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
+            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
+            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL)),
+            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL))
+            )
+
+hier = df[[2]]
+df = df[[1]]
+
+mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier_complete.stan"))
+
+fit <- mod$sample(
+      data = data2,
+      chains = 4,
+      parallel_chains = 4,
+      refresh = 100,
+      adapt_delta = 0.90,
+      max_treedepth = 12
+    )
+
+hier_parameters = c("mu_b0","mu_b1","mu_b2","sd_b0","sd_b1","sd_b2","mu_b0_b","mu_b1_b","mu_b2_b","sd_b0_b","sd_b1_b","sd_b2_b","kappa_alpha","mu_alpha","sd_percept_precision")
+
+sub_parameters = c("b0","b1","b2","b0_b","b1_b","b2_b","alpha","percept_precision")
+
+list(hier = data.frame(fit$summary(hier_parameters),
+                                  reals = hier %>% dplyr::select(all_of(hier_parameters)) %>% pivot_longer(everything()) %>% rename(reals = value),
+                                  div = sum(fit$diagnostic_summary()$num_divergent),index = index),
+                sub = data.frame(fit$summary(sub_parameters) %>% arrange(variable),
+                                 reals = df %>% filter(trial == 1) %>% mutate(ids = 1:nrow(.)) %>% dplyr::select(all_of(sub_parameters),ids) %>% 
+                                 pivot_longer(cols = -ids) %>% rename(reals =value) %>% mutate(names = paste0(name,"[",ids,"]")) %>% arrange(names) %>% select(names,reals),
+                                 div = sum(fit$diagnostic_summary()$num_divergent),index = index))
+
+#sum = fit$summary()
+
+```
+
+```{r}
+mu_alpha = seq(0.1,0.5, length.out = 5)
+kappa_alpha = seq(10,100, length.out = 2)
+
+mu_b0 = -1.5
+sd_b0 = 0.5
+
+mu_b1 = 2
+sd_b1 = 0.5
+
+mu_b2 = 0.1
+sd_b2 = 0.5
+
+mu_b0_b = -4
+sd_b0_b = 0.5
+
+mu_b1_b = 7
+sd_b1_b = 0.5
+
+mu_b2_b = 0.7
+sd_b2_b = 0.5
+
+sd_percept_precision = 0.8
+
+nsubs = 10
+
+parameters = expand.grid(mu_alpha = mu_alpha,
+                         kappa_alpha = kappa_alpha,
+                         mu_b0 = mu_b0,
+                         sd_b0 = sd_b0,
+                         mu_b1 = mu_b1,
+                         sd_b1 = sd_b1,
+                         mu_b2 = mu_b2,
+                         sd_b2 = sd_b2,
+                         mu_b0_b = mu_b0_b,
+                         sd_b0_b = sd_b0_b,
+                         mu_b1_b = mu_b1_b,
+                         sd_b1_b = sd_b1_b,
+                         mu_b2_b = mu_b2_b,
+                         sd_b2_b = sd_b2_b,
+                         sd_percept_precision = sd_percept_precision,
+                         nsubs = nsubs)
+
+parameters$id = 1:nrow(parameters)
+
+data_list <- split(parameters, parameters$id)
+
+plan(multisession, workers = 5)
+
+rw_pp = furrr::future_map(data_list, ~parameter_recovery_logistic_rw(.x), .progress = TRUE, .options = furrr_options(seed = 123))
+
+```
 

### 2023-05-26 scripts/agent.R

@@ -182,7 +182,6 @@ our_hier_rw_agent = function(parameters){
 }
 
 
-
 our_kalman_agent = function(parameters,dd){
   
   cue = dd$cue
@@ -668,3 +667,188 @@ hier_Bayes_f = function(parameters){
   
   
 }
+
+
+
+rw_logistic = function(alpha,b0,b1,b2,b0_b,b1_b,b2_b,percept_precision){
+  
+  dd = get_experiment()
+  
+  cue = dd$cue
+  stim = dd$stim
+  u = dd$u
+  bias = dd$bias
+  
+  ntrials = nrow(dd)
+  pred = array(NA, ntrials)
+  belief = array(NA, ntrials)
+  expect = array(NA, ntrials)
+  percept = array(NA, ntrials)
+  percept_bin = array(NA, ntrials)
+  perceptmu = array(NA, ntrials)
+  thetapercept = array(NA, ntrials)
+
+  belief[1] = 0.5;
+  expect[1] = 0.5;
+  
+  pred[1] = rbinom(1,1,belief[1])
+  
+  perceptmu[1] = inv_logit_scaled(b0+b1*stim[1]+b2*expect[1])
+  
+  percept[1] = extraDistr::rprop(1,percept_precision,perceptmu[1])
+  
+  thetapercept[1] = inv_logit_scaled(b0_b+b1_b*stim[1]+b2_b*expect[1])
+  
+  percept_bin[1] = rbinom(1,1,thetapercept[1])
+  
+  
+  
+  for (t in 2:ntrials){
+    
+    
+    belief[t] = belief[t-1]+alpha*(u[t-1]-belief[t-1])
+    pred[t] = rbinom(1,1,belief[t])
+    
+    
+    if(cue[t] == 1){
+      expect[t] = belief[t]
+    }else{
+      expect[t] = 1-belief[t]
+    }
+    
+    perceptmu[t] = inv_logit_scaled(b0+b1*stim[t]+b2*expect[t])
+    
+    percept[t] = extraDistr::rprop(1,percept_precision,perceptmu[t])
+    
+    thetapercept[t] = inv_logit_scaled(b0_b+b1_b*stim[t]+b2_b*expect[t])
+    
+    percept_bin[t] = rbinom(1,1,thetapercept[t]);
+    
+    
+    
+  }
+    
+  df = data.frame(u = u[1:ntrials], cue = cue[1:ntrials], stim = stim[1:ntrials], expect = expect[1:ntrials], pred = pred[1:ntrials],
[…]

### 2023-05-26 scripts/parameter_recovery.R

@@ -28,7 +28,7 @@ parameter_recovery_rw = function(parameters){
   
   mod = cmdstan_model(here::here("Stan","no generated quantities","myRW_real_nogen.stan"))
   
-  
+
   
   fitter = function(){
     fit <- mod$sample(
@@ -210,3 +210,74 @@ parameter_recovery_kalman = function(parameters){
 }
 
 
+
+
+parameter_recovery_logistic_rw = function(parameters){
+  
+  df = hier_rw_logistic(parameters)[[1]]
+  hier = hier_rw_logistic(parameters)[[2]]
+  
+  #fitting hierachically
+  data = df %>% filter(id %in% unique(id)[1:nsubs])
+  
+  data = data %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+  
+  
+  
+  data1 = list(nsubs = length(unique(data$id)),
+               ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
+               pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+               percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
+               percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
+               stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
+               u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL)),
+               cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL))
+  )
+  
+  mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier_complete.stan"))
+  
+  
+  
+  fitter = function(){
+    fit <- mod$sample(
+      data = data1,
+      chains = 4, 
+      parallel_chains = 4,
+      refresh = 100,
+      adapt_delta = 0.90,
+      max_treedepth = 12
+    )
+    return(fit)
+  }
+  
+  
+  fit <- tryCatch({
+    fit = withTimeout(fitter(), timeout = 1000, cpu = 1000)
[…]

### 2023-05-26 scripts/visualize_parameters.R

@@ -237,6 +237,73 @@ WB = function(dd){
   
 }
 
+RW_logistic_vis = function(dd){
+  
+  
+  scripts = c("agent.R","parameter_recovery.R","stan_functions.R")
+  q = lapply(here("scripts", scripts), source)
+  
+  alpha = seq(0.1,0.5,length.out = 3)
+  b0 = -1.5
+  b1 = seq(0.1,2,length.out = 3)
+  b2 = seq(0.1,2,length.out = 3)
+  
+  b0_b = -4
+  b1_b = 7.8
+  b2_b = 0.7
+  
+  
+  #precision_percept = seq(10,100,50)
+  #beta = seq(1,50,20)
+  
+  percept_precision = seq(10,300,length.out = 3)
+  
+  parameters = expand.grid(alpha = alpha,b0=b0,b1=b1,b2=b2,b0_b=b0_b,b1_b=b1_b,b2_b=b2_b, percept_precision = percept_precision)
+  
+  
+  
+  parameters$id = 1:nrow(parameters)
+  
+  data_list <- split(parameters, parameters$id)
+  
+  plan(multisession, workers = 12)
+  
+  dd = get_experiment()
+  
+  dd = furrr::future_map_dfr(data_list, ~rw_logistic_v2(.x, dd), .progress = TRUE, .options = furrr_options(seed = 123))
+  
+  dd$stim = as.factor(dd$stim)
+  dd$percept_precision = as.factor(dd$percept_precision)
+  
+  
+  levels(dd$stim) = c("Warm","Hot")
+  
+  
+  plot1 = dd %>% 
+    ggplot()+
+    geom_line(aes(x = trial, y = belief))+
+    geom_point(aes(x = trial, y = u), col = "orange")+
+    geom_line(aes(x = trial, y = desired))+
+    facet_grid(alpha~b2, labeller = label_both)+
+    theme_classic()+
+    scale_y_continuous("Cue-stimulus association", breaks = scales::pretty_breaks(n = 5))+
+    scale_x_continuous("Trial", breaks = scales::pretty_breaks(n = 5))
+  
+  
+  plot2 = dd %>% filter(alpha == 0.1) %>% ggplot(aes(expect, y = percept,col = percept_precision, group = interaction(stim, percept_precision)))+
+    geom_point(aes(shape = stim))+
+    facet_grid(b1~b2, labeller = label_both)+
+    geom_smooth(method = "lm")+
+    theme_classic()+
[…]

### 2023-05-26 Manuscript1.Rmd
updates

@@
 ```{r}
+
+files = paste0(here::here("workspace","parameterrecovery"),"/",list.files(here::here("workspace","parameterrecovery")))
+
 #plot parameterrecovery
-plot_parameterrecovery(rw_pp, div = F, subs = 5)
-
-plot_parameterrecovery(wb_pp, div = F, subs = 5)
-
-plot_parameterrecovery(kalman_pp, div = T, subs = 5)
+load(files[[2]])
+q = lapply(here("scripts", scripts), source)
+rwplot = plot_parameterrecovery(rw_pp, div = T, subs = 5)
+load(files[[3]])
+q = lapply(here("scripts", scripts), source)
+wbplot = plot_parameterrecovery(wb_pp, div = T, subs = 5)
+load(files[[1]])
+q = lapply(here("scripts", scripts), source)
+kalmanplot = plot_parameterrecovery(kalman_pp, div = T, subs = 5)
+
+layout = (c(
+  area(1, 1, 2,3),
+  area(3, 1,5,3),
+  area(6, 1,6,3)
+
+))
+
+plot(layout)
+
+((rwplot[[1]]+wbplot[[1]]+kalmanplot[[1]])/(rwplot[[2]]+wbplot[[2]]+kalmanplot[[2]])/((rwplot[[3]]+wbplot[[3]]+kalmanplot[[3]])))+
+  plot_annotation(tag_levels = 'A')+
+  plot_layout(design = layout,guides = 'collect')
 
@@
 
-mu_b1 = 2
-sd_b1 = 0.5
-
-mu_b2 = 0.1
-sd_b2 = 0.5
+mu_b1 = seq(0.1,2,length.out = 5)
+sd_b1 = seq(0.1,2,length.out = 3)
+
+mu_b2 = seq(0.1,2,length.out = 5)
+sd_b2 = seq(0.1,2,length.out = 3)
 

### 2023-05-26 scripts/visualize_parameters.R

@@ -41,8 +41,8 @@ RW = function(dd){
     geom_line(aes(x = trial, y = desired))+
     facet_grid(alpha~w1, labeller = label_both)+
     theme_classic()+
-    scale_y_continuous("Cue-stimulus association", breaks = scales::pretty_breaks(n = 5))+
-    scale_x_continuous("Trial", breaks = scales::pretty_breaks(n = 5))
+    scale_y_continuous("Cue-stimulus association", breaks = scales::pretty_breaks(n = 3))+
+    scale_x_continuous("Trial", breaks = scales::pretty_breaks(n = 3))    
   
   
   plot2 = dd %>% ggplot(aes(exp, y = percept,col = precision_percept, group = interaction(stim, precision_percept)))+
@@ -50,8 +50,8 @@ RW = function(dd){
     facet_grid(alpha~w1, labeller = label_both)+
     geom_smooth(method = "lm")+
     theme_classic()+
-    scale_y_continuous("Mean of percept", breaks = scales::pretty_breaks(n = 4))+
-    scale_x_continuous("% Expectation of Stimulus being Hot", breaks = scales::pretty_breaks(n = 4))+ theme(legend.position = "top")
+    scale_y_continuous("Mean of percept", breaks = scales::pretty_breaks(n = 3))+
+    scale_x_continuous("% Expectation of Stimulus being Hot", breaks = scales::pretty_breaks(n = 3))+ theme(legend.position = "top")+ theme(text = element_text(size = 14))    
   
  
   plot1+plot2
@@ -95,8 +95,8 @@ KALMAN = function(){
     geom_line(aes(x = trial, y = desired))+
     facet_grid(sigmaEta~sigmaPsi, labeller = label_both)+
     theme_classic()+
-    scale_y_continuous("Cue-stimulus association", breaks = scales::pretty_breaks(n = 5))+
-    scale_x_continuous("Trial", breaks = scales::pretty_breaks(n = 5))+ theme(legend.position = "none")
+    scale_y_continuous("Cue-stimulus association", breaks = scales::pretty_breaks(n = 3))+
+    scale_x_continuous("Trial", breaks = scales::pretty_breaks(n = 3))+ theme(legend.position = "none")    
   
   
   
@@ -105,8 +105,8 @@ KALMAN = function(){
     geom_smooth(method = "lm")+
[…]

### 2023-05-26 Manuscript1.Rmd
updates

@@
 
-```{r parameters visualization, fig.height=10, fig.width=10}
+```{r parameters visualization, fig.height=10, fig.width=12}
 dd = get_experiment()
@@
 
-RW_logistic = RW_logistic_vis(dd)
+#RW_logistic = RW_logistic_vis(dd)
 ```
@@
 kalman_pp = furrr::future_map(data_list, ~parameter_recovery_kalman(.x), .progress = TRUE, .options = furrr_options(seed = 123))
+
+```
+
+```{r parameter recovery for logistic}
+mu_alpha = seq(0.1,0.5, length.out = 5)
+kappa_alpha = seq(10,100, length.out = 2)
+
+mu_b0 = -1.5
+sd_b0 = 0.5
+
+mu_b1 = seq(0.1,2,length.out = 5)
+sd_b1 = seq(0.1,2,length.out = 3)
+
+mu_b2 = seq(0.1,2,length.out = 5)
+sd_b2 = seq(0.1,2,length.out = 3)
+
+mu_b0_b = -4
+sd_b0_b = 0.5
+
+mu_b1_b = 7
+sd_b1_b = 0.5
+
+mu_b2_b = 0.7
+sd_b2_b = 0.5
+
+sd_percept_precision = 0.8
+
+nsubs = 10
+
+parameters = expand.grid(mu_alpha = mu_alpha,
+                         kappa_alpha = kappa_alpha,
+                         mu_b0 = mu_b0,
+                         sd_b0 = sd_b0,
+                         mu_b1 = mu_b1,
+                         sd_b1 = sd_b1,
+                         mu_b2 = mu_b2,
+                         sd_b2 = sd_b2,
+                         mu_b0_b = mu_b0_b,
+                         sd_b0_b = sd_b0_b,
+                         mu_b1_b = mu_b1_b,
+                         sd_b1_b = sd_b1_b,
+                         mu_b2_b = mu_b2_b,
+                         sd_b2_b = sd_b2_b,
+                         sd_percept_precision = sd_percept_precision,
+                         nsubs = nsubs)
+
+parameters$id = 1:nrow(parameters)
+
+data_list <- split(parameters, parameters$id)
+
+plan(multisession, workers = 5)
+
+rw_pp = furrr::future_map(data_list, ~parameter_recovery_logistic_rw(.x), .progress = TRUE, .options = furrr_options(seed = 123))
 
@@
 
-######################################### Kalman
-
-mu_sigmaEta = rep(0.1,100)
-mu_sigmaPsi = 0.1
-mu_sigmaEpsilon = 2
-sd_sigmaEta = 0.1
-sd_sigmaPsi = 0.1
-sd_sigmaEpsilon = 0.1
-nsubs = 10
-parameters = expand.grid(mu_sigmaEta = mu_sigmaEta,
-                         mu_sigmaPsi = mu_sigmaPsi,
-                         mu_sigmaEpsilon = mu_sigmaEpsilon,
-                         sd_sigmaEta = sd_sigmaEta,
-                         sd_sigmaPsi = sd_sigmaPsi,
-                         sd_sigmaEpsilon = sd_sigmaEpsilon,
-                         nsubs = nsubs)
-parameters$id = 1:nrow(parameters)
-data_list_kalman <- split(parameters, parameters$id)
+######################################### logistic RW
 
@@
 
-```{r}
-mu_alpha = seq(0.1,0.5, length.out = 5)
-kappa_alpha = seq(10,100, length.out = 2)
-
-mu_b0 = -1.5
-sd_b0 = 0.5
-
-mu_b1 = seq(0.1,2,length.out = 5)
-sd_b1 = seq(0.1,2,length.out = 3)
-
-mu_b2 = seq(0.1,2,length.out = 5)
-sd_b2 = seq(0.1,2,length.out = 3)
-
-mu_b0_b = -4
-sd_b0_b = 0.5
-
-mu_b1_b = 7
-sd_b1_b = 0.5
-
-mu_b2_b = 0.7
-sd_b2_b = 0.5
-
-sd_percept_precision = 0.8
-
-nsubs = 10
-
-parameters = expand.grid(mu_alpha = mu_alpha,
-                         kappa_alpha = kappa_alpha,
-                         mu_b0 = mu_b0,
-                         sd_b0 = sd_b0,
-                         mu_b1 = mu_b1,
-                         sd_b1 = sd_b1,
-                         mu_b2 = mu_b2,
-                         sd_b2 = sd_b2,
-                         mu_b0_b = mu_b0_b,
-                         sd_b0_b = sd_b0_b,
-                         mu_b1_b = mu_b1_b,
-                         sd_b1_b = sd_b1_b,
-                         mu_b2_b = mu_b2_b,
-                         sd_b2_b = sd_b2_b,
-                         sd_percept_precision = sd_percept_precision,
-                         nsubs = nsubs)
-
-parameters$id = 1:nrow(parameters)
-
-data_list <- split(parameters, parameters$id)
-
-plan(multisession, workers = 5)
-
-rw_pp = furrr::future_map(data_list, ~parameter_recovery_logistic_rw(.x), .progress = TRUE, .options = furrr_options(seed = 123))
-
-```
-
 <!-- ```{r fitting to real data tester hierachical RW seesion2} -->

### 2023-05-26 Manuscript1.Rmd
updates

@@
 
-```{r parameters visualization, fig.height=10, fig.width=12}
+```{r parameters visualization, fig.height=14, fig.width=16}
 dd = get_experiment()
@@
 layout = (c(
-  area(1, 1),
-  area(1, 2),
-  area(2, 1),
-  area(2, 2)
+  area(1, 1, 1,1),
+  area(1, 2, 1,2),
+  area(1, 3, 1,3)
 
 ))
-
-trial_struc = ggdraw() +
-  draw_image(magick::image_read(here::here("figures", "main-experiment.PNG")), scale = 1.5)
-
-trial_struc+kalmanplot+rwplot+wbplot+plot_layout(design = layout)+plot_annotation(tag_levels = 'A')
-
-#RW_logistic = RW_logistic_vis(dd)
+plot(layout)
+
+p1 = kalmanplot[[1]]+rwplot[[1]]+wbplot[[1]]+plot_layout(design = layout)+plot_annotation(tag_levels = list(c('B', 'C',"D","E","F","G")))
+p2 = kalmanplot[[2]]+rwplot[[2]]+wbplot[[2]]+plot_layout(design = layout)+plot_annotation(tag_levels = list(c("E","F","G")))
+
+p1
+p2
+
+RW_logistic = RW_logistic_vis(dd)
 ```
@@
 
-mu_alpha = rep(0.2,100)
+mu_alpha = rep(0.3,100)
 kappa_alpha = 50
-mu_w1 = 0.2
+mu_w1 = 0.3
 kappa_w1 = 50
-mu_w2 = 0.2
+mu_w2 = 0.3
 kappa_w2 = 50
@@
 
-######################################### fit data_rw:
-#loos = model_fitter_rwdata(data_list_rw[[1]])
-
-data_list = data_list_rw[1:5]
-
-plan(multisession, workers = 5)
-
-rw_loo = furrr::future_map(data_list, ~model_fitter_rwdata(.x), .progress = TRUE, .options = furrr_options(seed = 123))
-
-elpld_loo <- map_dfr(rw_loo, ~ .x[[1]])
-
-full_loo <- map_dfr(rw_loo, ~ .x[[2]])
-
-########################################## fit data_wb
-
-data_list = data_list_wb[1:100]
-
-plan(multisession, workers = 10)
-
-wb_loo = furrr::future_map(data_list, ~model_fitter_wbdata(.x), .progress = TRUE, .options = furrr_options(seed = 123))
-
-elpld_loo <- map_dfr(wb_loo, ~ .x[[1]])
-
-full_loo <- map_dfr(wb_loo, ~ .x[[2]])
-
-########################################### fit kalman data
-
-data_list = data_list_kalman[1]
-
-plan(multisession, workers = 5)
-
-kalman_loo = furrr::future_map(data_list, ~model_fitter_kalmandata(.x), .progress = TRUE, .options = furrr_options(seed = 123))
-
-elpld_loo <- map_dfr(kalman_loo, ~ .x[[1]])
-
-full_loo <- map_dfr(kalman_loo, ~ .x[[2]])
-
-```
-
-```{r model recovery table:}
-
-get_value = function(loo){
-  get_from_means <- do.call(rbind, lapply(loo, "[[", 1))
-
-  get_from_means$id = as.factor(get_from_means$id)
-# Group by ID and find the model with the minimum value
-  min_values <- get_from_means %>%
-  group_by(id) %>%
-  filter(means == min(means))
-
-# Count the occurrences of each model with the minimum value per run
-  model_counts <- min_values %>%
-    group_by(names) %>%
-    summarize(Count = n())
-
-  get_from_loo <- do.call(rbind, lapply(loo, "[[", 2))
-
-  get_from_loo = get_from_loo %>% filter(elpd_diff == 0) %>% mutate(model = row.names(.)) %>% mutate(realmodel = sub("^[0-9]+\\.(.*)", "\\1", model)) %>% group_by(realmodel) %>% summarize(Count = n())
-
-  return(list(fromloo = get_from_loo, frommean = model_counts))
-}
-
-get_value(rw_loo)
-```
-
-```{r fitting RW model to session 1}
-df= read.csv(here::here("data_TPL_AC.csv")) %>% 
-  rename_all(tolower) %>% 
-  filter(trial != 0) %>% 
-  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% 
-  mutate_all(replace_na, 0)
-
-df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
-
-df = df %>% filter(session == 1)
-
-#fitting hierachically
-data = df %>% mutate(percept = percept/100)
-
-data = data %>% mutate(across(percept, ~case_when(
-    . < 0.001 ~ 0.001,
-    . > 0.999 ~ 0.999,
-    TRUE ~ .
-  )))
-
-data1 = list(nsubs = length(unique(data$id)),
-            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
-            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
-            expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
-            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
-            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
-            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)))
-
-mod = cmdstan_model(here::here("Stan","myRW_real.stan"))
-
-rw_fit_sess1 <- mod$sample(
-      data = data1,
-      chains = 4, 
-      parallel_chains = 4,
-      refresh = 100,
-      adapt_delta = 0.90,
-      max_treedepth = 12
-    )
-
-ppu_hier(fit = rw_fit_sess1,
-         parameters = c("alpha","w1","precision_percept"),
-         reals = NA)
-
-```
-
-```{r plotting 1 agent}
-
-percept = sum %>% filter(str_detect(variable, "painMu"))
-percept = percept[1:160,]
-
-expect = sum %>% filter(str_detect(variable, "expectMu"))
-expect = expect[1:160,]
-
-percept$stim = data$stim
-percept$expect = expect$mean
-
-percept %>% ggplot(aes(x=1:nrow(.), y = mean, col = as.factor(stim)))+geom_point()
-
-percept %>% ggplot(aes(x=expect, y = mean, col = as.factor(stim)))+geom_point()
-
-ass = sum %>% filter(str_detect(variable, "associ"))
-ass = ass[1:161,]
-
-ass %>% ggplot(aes(x=1:nrow(.), y = mean))+geom_line()+geom_point(data = data, aes(x = trial, y = u))
-
-rw_fit_sess1$diagnostic_summary()
-
-alpha = get_diag(rw_fit_sess1, "alpha")
-w1 = get_diag(rw_fit_sess1, "w1")
-pp = get_diag(rw_fit_sess1, "precision_percept")
-beta = get_diag(rw_fit_sess1, "beta")
-
-```
-
-```{r fitting RW model to session 2}
-df= read.csv(here::here("data_TPL_AC.csv")) %>% 
-  rename_all(tolower) %>% 
-  filter(trial != 0) %>% 
-  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% 
-  mutate_all(replace_na, 0)
-
-df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
-
-df = df %>% filter(session == 2)
-
-#fitting hierachically
-data = df %>% mutate(percept = percept/100)
-
-data = data %>% mutate(across(percept, ~case_when(
-    . < 0.001 ~ 0.001,
-    . > 0.999 ~ 0.999,
-    TRUE ~ .
-  )))
-
-data1 = list(nsubs = length(unique(data$id)),
-            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
-            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
-            expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
-            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
-            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
-            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)))
-
-mod = cmdstan_model(here::here("Stan","myRW_real.stan"))
-
-rw_fit_sess2 <- mod$sample(
-      data = data1,
-      chains = 4, 
-      parallel_chains = 4,
-      refresh = 100,
-      adapt_delta = 0.90,
-      max_treedepth = 12
-    )
-
-ppu_hier(fit = rw_fit_sess2,
-         parameters = c("alpha","w1","precision_percept"),
-         reals = NA)
-
-```
-
-```{r fitting Kalman model to session 1}
-df= read.csv(here::here("data_TPL_AC.csv")) %>%
-  rename_all(tolower) %>%
-  filter(trial != 0) %>%
-  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
-  mutate_all(replace_na, 0)
-
-df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
-
-df = df %>% filter(session == 1)
-
-#fitting hierachically
-data = df %>% mutate(percept = percept/100)
-
-data = data %>% mutate(across(percept, ~case_when(
-    . < 0.001 ~ 0.001,
-    . > 0.999 ~ 0.999,
-    TRUE ~ .
-  )))
-
-data1 = list(nsubs = length(unique(data$id)),
-            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
-            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
-            expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
-            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
-            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
-            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)),
-            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL))
-            )
-
-mod = cmdstan_model(here::here("Stan","myKalmanfilter_v3_nocent.stan"))
-
-kalman_fit_sess1 <- mod$sample(
-      data = data1,
-      chains = 4,
-      parallel_chains = 4,
-      refresh = 100,
-      adapt_delta = 0.90,
-      max_treedepth = 12
-    )
-
-ppu_hier(fit = kalman_fit_sess1,
-         parameters = c("sigmaEta","sigmaPsi","sigmaEpsilon","precision_percept"),
-         reals = NA)
-
-# 
-# ppu_sub(fit = fit,
-#         parameter = "precision_percept",
-#         reals = df,
-#         lims = -1,
-#         lime = 10,
-#         nsubs = NA
-#         )
-
-get_diag(kalman_fit_sess1, "sigmaEta")
-get_diag(kalman_fit_sess1, "sigmaPsi")
-get_diag(kalman_fit_sess1, "sigmaEpsilon")
-
-sum = kalman_fit_sess1$summary()
-
-ass = sum %>% filter(str_detect(variable, "perceptmuu"))
-ass = ass[(161*2-1):(161*3-1),]
-
-exp = sum %>% filter(str_detect(variable, "exp_muu"))
-exp = exp[(161*2-1):(161*3-1),]
-
-ass$exp = exp$mean
-
-ass %>% ggplot(aes(x=exp, y = mean))+geom_point()
-
-```
-
-```{r fitting Kalman model to session 2}
-df= read.csv(here::here("data_TPL_AC.csv")) %>%
-  rename_all(tolower) %>%
-  filter(trial != 0) %>%
-  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
-  mutate_all(replace_na, 0)
-
-df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
-
-df = df %>% filter(session == 2)
-
-#fitting hierachically
-data = df %>% mutate(percept = percept/100)
-
-data = data %>% mutate(across(percept, ~case_when(
-    . < 0.001 ~ 0.001,
-    . > 0.999 ~ 0.999,
-    TRUE ~ .
-  )))
-
-data1 = list(nsubs = length(unique(data$id)),
-            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
-            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
-            expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
-            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
-            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
-            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)),
-            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL))
-            )
-
-mod = cmdstan_model(here::here("Stan","myKalmanfilter_v3_nocent.stan"))
-
-kalman_fit_sess2 <- mod$sample(
-      data = data1,
-      chains = 4,
-      parallel_chains = 4,
-      refresh = 100,
-      adapt_delta = 0.90,
-      max_treedepth = 12
-    )
-
-ppu_hier(fit = kalman_fit_sess2,
-         parameters = c("sigmaEta","sigmaPsi","sigmaEpsilon","precision_percept"),
-         reals = NA)
-
-```
-
-```{r fitting WB model to session 1}
-df= read.csv(here::here("data_TPL_AC.csv")) %>% 
-  rename_all(tolower) %>% 
-  filter(trial != 0) %>% 
-  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% 
-  mutate_all(replace_na, 0)
-
-df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
-
-df = df %>% filter(session == 1)
-
-#fitting hierachically
-data = df %>% mutate(percept = percept/100)
-
-data = data %>% mutate(across(c(percept,stim), ~case_when(
-    . < 0.001 ~ 0.001,
-    . > 0.999 ~ 0.999,
-    TRUE ~ .
-  )))
-
-data1 = list(nsubs = length(unique(data$id)),
-            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
-            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
-            pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
-            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
-            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
-            cue = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL))
-            )
-
-mod = cmdstan_model(here::here("Stan","hier_weighted_bayes.stan"))
-
-wb_fit_sess1  <- mod$sample(
-      data = data1,
-      chains = 4, 
-      parallel_chains = 4,
-      refresh = 100,
-      adapt_delta = 0.90,
-      max_treedepth = 12
-    )
-
-wb_fit_sess1$diagnostic_summary()
-
-alpha = get_diag(wb_fit_sess1, "alpha")
-w1 = get_diag(wb_fit_sess1, "w1")
-w2 = get_diag(wb_fit_sess1, "w2")
-pp = get_diag(wb_fit_sess1, "percept_precision")
-beta = get_diag(wb_fit_sess1, "beta")
-
-```
-
-```{r fitting WB model to session 2}
-
-df= read.csv(here::here("data_TPL_AC.csv")) %>% 
-  rename_all(tolower) %>% 
-  filter(trial != 0) %>% 
-  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% 
-  mutate_all(replace_na, 0)
-
-df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
-
-df = df %>% filter(session == 2)
-
-#fitting hierachically
-data = df %>% mutate(percept = percept/100)
-
-data = data %>% mutate(across(c(percept,stim), ~case_when(
-    . < 0.001 ~ 0.001,
-    . > 0.999 ~ 0.999,
-    TRUE ~ .
-  )))
-
-data1 = list(nsubs = length(unique(data$id)),
-            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
-            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
-            pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
-            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
-            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
-            cue = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL))
-            )
-
-mod = cmdstan_model(here::here("Stan","hier_weighted_bayes.stan"))
-
-wb_fit_sess2 <- mod$sample(
-      data = data1,
-      chains = 4, 
-      parallel_chains = 4,
-      refresh = 100,
-      adapt_delta = 0.90,
-      max_treedepth = 12
-    )
-
-alpha = get_diag(wb_fit_sess1, "alpha")
-w1 = get_diag(wb_fit_sess1, "w1")
-w2 = get_diag(wb_fit_sess1, "w2")
-pp = get_diag(wb_fit_sess1, "percept_precision")
-beta = get_diag(wb_fit_sess1, "beta")
-
-```
-
-```{r}
-get_corplot(rw_fit_sess1, rw_fit_sess2, "alpha")
-get_corplot(rw_fit_sess1, rw_fit_sess2, "w1")
-get_corplot(rw_fit_sess1, rw_fit_sess2, "precision_percept")
-
-get_corplot(wb_fit_sess1, wb_fit_sess2, "alpha")
-get_corplot(wb_fit_sess1, wb_fit_sess2, "w1")
-get_corplot(wb_fit_sess1, wb_fit_sess2, "w2")
-get_corplot(wb_fit_sess1, wb_fit_sess2, "beta")
-get_corplot(wb_fit_sess1, wb_fit_sess2, "percept_precision")
-
-```
-
-```{r}
-df= read.csv(here::here("data_TPL_AC.csv")) %>%
-  rename_all(tolower) %>%
-  filter(trial != 0) %>%
-  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
-  mutate_all(replace_na, 0)
-
-df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
-df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
-
-df = df %>% filter(session == 1)
-
-#fitting hierachically
-data = df %>% mutate(percept = percept/100)
-
-data = data %>% mutate(across(percept, ~case_when(
-    . < 0.001 ~ 0.001,
-    . > 0.999 ~ 0.999,
-    TRUE ~ .
-  )))
-
-data1 = list(nsubs = length(unique(data$id)),
-            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
-            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
-            expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
-            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
-            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
-            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)),
-            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL))
-            )
-
-mod = cmdstan_model(here::here("Stan","myKalmanfilter_v3_nocent.stan"))
-
-kalman_fit_sess1 <- mod$sample(
-      data = data1,
-      chains = 4,
-      parallel_chains = 4,
-      refresh = 100,
-      adapt_delta = 0.90,
-      max_treedepth = 12
-    )
-```
-
-```{r hierachical session correlation (RW)}
-
-df= read.csv(here::here("data_TPL_AC.csv")) %>%
-  rename_all(tolower) %>%
-  filter(trial != 0) %>%
-  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
-  mutate_all(replace_na, 0) %>% mutate(id = as.factor(id), trial = as.factor(trial), session = as.factor(session))
-
-df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
-
-#fitting hierachically
-data = df %>% mutate(percept = percept/100)
-
-data = data %>% mutate(across(percept, ~case_when(
-    . < 0.001 ~ 0.001,
-    . > 0.999 ~ 0.999,
-    TRUE ~ .
-  )))
-
-data1 = list(nsubs = length(unique(data$id)),
-            ntrials = nrow(data %>% filter(session == 1) %>% filter(id %in% unique(id)[1])),
-            sesions = length(unique(data$session)),
-            percept = get_3darray(data,variable = "percept"),
-            expectPain = get_3darray(data,variable = "pred"),
-            percept_bin = get_3darray(data,variable = "percept_bin"),
-            stim = get_3darray(data,variable = "stim"),
-            cues = get_3darray(data,variable = "cue"),
-            u = get_3darray(data,variable = "u")
-            )
-
-mod = cmdstan_model(here::here("Stan","fitting both sessions","myRW_real_both_sess.stan"))
-
-fit <- mod$sample(
-  data = data1,
-  chains = 4,
-  parallel_chains = 4,
-  refresh = 100,
-  adapt_delta = 0.90,
-  max_treedepth = 12
-)
-
-sum = fit$summary(variables = c("mu_alpha","mu_w1","sd_beta","sd_precision_percept", "kappa_alpha","kappa_w1","alpha","w1","beta","precision_percept"))
-
-variabless = c("mu_alpha[1]","mu_w1[1]","sd_beta[1]","sd_precision_percept[1]","mu_alpha[2]","mu_w1[2]","sd_beta[2]","sd_precision_percept[2]")
-
-pairs = mcmc_pairs(fit$draws(variables = variabless), np = nuts_params(fit), pars = variabless,
-                   off_diag_args = list(size = 0.75))
-
-mcmc_trace(fit$draws(variables = "alpha"))
-
-alpha = fit$summary(variables = "alpha")
-w1 = fit$summary(variables = "w1")
-
-alphas1 <- w1 %>%
-  filter(grepl("1]$", variable))
-
-alphas2 <- w1 %>%
-  filter(grepl("2]$", variable))
-
-cor.test(alphas1$mean, alphas2$mean)
-
-correlation = as_draws_df(fit$draws(variables = "correlation_alpha"))
-hist(correlation$correlation_alpha)
-correlation = as_draws_df(fit$draws(variables = "correlation_w1"))
-hist(correlation$correlation_w1)
-```
-
-```{r hierachical session correlation (WB)}
-
-df= read.csv(here::here("data_TPL_AC.csv")) %>%
-  rename_all(tolower) %>%
-  filter(trial != 0) %>%
-  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
-  mutate_all(replace_na, 0) %>% mutate(id = as.factor(id), trial = as.factor(trial), session = as.factor(session))
-
-df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
-
-#fitting hierachically
-data = df %>% mutate(percept = percept/100)
-
-data = data %>% mutate(across(c(percept,stim), ~case_when(
-    . < 0.001 ~ 0.001,
-    . > 0.999 ~ 0.999,
-    TRUE ~ .
-  )))
-
-data1 = list(nsubs = length(unique(data$id)),
-            ntrials = nrow(data %>% filter(session == 1) %>% filter(id %in% unique(id)[1])),
-            sesions = length(unique(data$session)),
-            percept = get_3darray(data,variable = "percept"),
-            pred = get_3darray(data,variable = "pred"),
-            percept_bin = get_3darray(data,variable = "percept_bin"),
-            stim = get_3darray(data,variable = "stim"),
-            cue = get_3darray(data,variable = "cue")
-            )
-
-mod = cmdstan_model(here::here("Stan","fitting both sessions","hier_weighted_bayes_correlation.stan"))
-
-fit_wb_bs <- mod$sample(
-  data = data1,
-  chains = 4,
-  parallel_chains = 4,
-  refresh = 100,
-  adapt_delta = 0.90,
-  max_treedepth = 12
-)
-
-correlation = as_draws_df(fit_wb_bs$draws(variables = "correlation_alpha"))
-hist(correlation$correlation_alpha)
-correlation = as_draws_df(fit_wb_bs$draws(variables = "correlation_w1"))
-hist(correlation$correlation_w1)
-correlation = as_draws_df(fit_wb_bs$draws(variables = "correlation_w2"))
-hist(correlation$correlation_w2)
-
-```
-
-```{r fitting to both sessions to hierachiacal RW}
-
-df= read.csv(here::here("data_TPL_AC.csv")) %>%
-  rename_all(tolower) %>%
-  filter(trial != 0) %>%
-  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
-  mutate_all(replace_na, 0)
-
-df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
-df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
-
-#source(here::here("stan_functions.R"))
-#fitting hierachically
-data = df %>% mutate(percept = percept/100)
-
-data = data %>% mutate(across(percept, ~case_when(
-    . < 0.001 ~ 0.001,
-    . > 0.999 ~ 0.999,
-    TRUE ~ .
-  )))
-
-data1 = list(nsubs = length(unique(data$id)),
-            ntrials = nrow(data %>% filter(session == 1) %>% filter(id %in% unique(id)[1])),
-            sessions = 2,
-            pred = get_3darray(data,variable = "pred"),
-            u = get_3darray(data,variable = "u")
-            )
-
-mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier.stan"))
-
-rw_fit_ses1 <- mod$sample(
-      data = data1,
-      chains = 4,
-      parallel_chains = 4,
-      refresh = 100,
-      adapt_delta = 0.90,
-      max_treedepth = 12
-    )
-
-sum = rw_fit_ses1$summary(variables = c("alpha", "mu_alpha","sd_alpha","mu_mu_alpha","sd_sd_alpha","mu_sd_alpha","sd_mu_alpha"))
-```
-
-```{r, fitting to real data tester hierachical RW sessions1}
-
-df= read.csv(here::here("data_TPL_AC.csv")) %>%
-  rename_all(tolower) %>%
-  filter(trial != 0) %>%
-  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
-  mutate_all(replace_na, 0)
-
-df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
-df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
-
-df = df %>% filter(session == 1)
-
-#source(here::here("stan_functions.R"))
-#fitting hierachically
-data = df %>% mutate(percept = percept/100)
-
-data = data %>% mutate(across(percept, ~case_when(
-    . < 0.001 ~ 0.001,
-    . > 0.999 ~ 0.999,
-    TRUE ~ .
-  )))
-
-data2 = list(nsubs = length(unique(data$id)),
-            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
-            pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
-            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
-            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
-            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
-            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL)),
-            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL))
-            )
-
-mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier_complete.stan"))
-
-rw_fit_ses1 <- mod$sample(
-      data = data2,
-      chains = 4,
-      parallel_chains = 4,
-      refresh = 100,
-      adapt_delta = 0.90,
-      max_treedepth = 12
-    )
-
-sum1 = rw_fit_ses1$summary()
-```
-
-```{r, fitting to real data tester hierachical RW sessions2}
-
-df= read.csv(here::here("data_TPL_AC.csv")) %>%
-  rename_all(tolower) %>%
-  filter(trial != 0) %>%
-  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
-  mutate_all(replace_na, 0)
-
-df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
-df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
-
-df = df %>% filter(session == 2)
-
-#source(here::here("stan_functions.R"))
-#fitting hierachically
-data = df %>% mutate(percept = percept/100)
-
-data = data %>% mutate(across(percept, ~case_when(
-    . < 0.001 ~ 0.001,
-    . > 0.999 ~ 0.999,
-    TRUE ~ .
-  )))
-
-data2 = list(nsubs = length(unique(data$id)),
-            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
-            pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
-            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
-            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
-            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
-            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL)),
-            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL))
-            )
-
-mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier_complete.stan"))
-
-rw_fit_ses2 <- mod$sample(
-      data = data2,
-      chains = 4,
-      parallel_chains = 4,
-      refresh = 100,
-      adapt_delta = 0.90,
-      max_treedepth = 12
-    )
-
-sum2 = rw_fit_ses2$summary()
-
-get_corplot(rw_fit_ses1,rw_fit_ses2, "b2_b")
-```
-
-```{r}
-
-df= read.csv(here::here("data_TPL_AC.csv")) %>%
-  rename_all(tolower) %>%
-  filter(trial != 0) %>%
-  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
-  mutate_all(replace_na, 0) %>% mutate(id = as.factor(id), trial = as.factor(trial), session = as.factor(session))
-
-df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
-df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
-
-#fitting hierachically
-data = df %>% mutate(percept = percept/100)
-
-data = data %>% mutate(across(percept, ~case_when(
-    . < 0.001 ~ 0.001,
-    . > 0.999 ~ 0.999,
-    TRUE ~ .
-  )))
-
-data1 = list(nsubs = length(unique(data$id)),
-            ntrials = nrow(data %>% filter(session == 1) %>% filter(id %in% unique(id)[1])),
-            sesions = length(unique(data$session)),
-            percept = get_3darray(data,variable = "percept"),
-            pred = get_3darray(data,variable = "pred"),
-            percept_bin = get_3darray(data,variable = "percept_bin"),
-            stim = get_3darray(data,variable = "stim"),
-            cues = get_3darray(data,variable = "cue"),
-            u = get_3darray(data,variable = "u")
-            )
-
-mod = cmdstan_model(here::here("Stan","fitting both sessions","rw_vs_rw_hier_complete_both_sessions.stan"))
-
-fit <- mod$sample(
-  data = data1,
-  chains = 4,
-  parallel_chains = 4,
-  refresh = 10,
-  adapt_delta = 0.90,
-  max_treedepth = 12
-)
-
-```
-
-```{r}
-mu_alpha = 0.3
-kappa_alpha = 30
-
-mu_b0 = -5
-sd_b0 = 1
-
-mu_b1 = -1
+mu_alpha = rep(0.3,100)
+kappa_alpha = 50
+
+mu_b0 = -1.5
+sd_b0 = 0.5
+
+mu_b1 = 2
 sd_b1 = 1
 
-mu_b2 = 1.3
-sd_b2 = 1.3
-
-mu_b0_b = -5
-sd_b0_b = 2
-
-mu_b1_b = 0.5
+mu_b2 = 2
+sd_b2 = 1
+
+mu_b0_b = -4
+sd_b0_b = 0.5
+
+mu_b1_b = 7
 sd_b1_b = 0.5
 
-mu_b2_b = 0.5
+mu_b2_b = 0.7
 sd_b2_b = 0.5
@@
 
-df = hier_rw_logistic(parameters)
-
-data = df[[1]]
+parameters$id = 1:nrow(parameters)
+
+data_list_logs <- split(parameters, parameters$id)
+
+######################################### fit data_rw:
+#loos = model_fitter_rwdata(data_list_rw[[1]])
+
+data_list = data_list_rw
+
+plan(multisession, workers = availableCores()-1)
+
+rw_loo = furrr::future_map(data_list, ~model_fitter_rwdata(.x), .progress = TRUE, .options = furrr_options(seed = 123))
+
+elpld_loo <- map_dfr(rw_loo, ~ .x[[1]])
+
+full_loo <- map_dfr(rw_loo, ~ .x[[2]])
+
+########################################## fit data_wb
+
+data_list = data_list_wb
+
+plan(multisession, workers = availableCores()-1)
+
+wb_loo = furrr::future_map(data_list, ~model_fitter_wbdata(.x), .progress = TRUE, .options = furrr_options(seed = 123))
+
+elpld_loo <- map_dfr(wb_loo, ~ .x[[1]])
+
+full_loo <- map_dfr(wb_loo, ~ .x[[2]])
+
+########################################### fit kalman data
+
+data_list = data_list_logs
+
+plan(multisession, workers = availableCores()-1)
+
+plan(multisession, workers = 5)
+
+kalman_loo = furrr::future_map(data_list, ~model_fitter_kalmandata(.x), .progress = TRUE, .options = furrr_options(seed = 123))
+
+elpld_loo <- map_dfr(kalman_loo, ~ .x[[1]])
+
+full_loo <- map_dfr(kalman_loo, ~ .x[[2]])
+
+```
+
+```{r model recovery table:}
+
+get_value = function(loo){
+  get_from_means <- do.call(rbind, lapply(loo, "[[", 1))
+
+  get_from_means$id = as.factor(get_from_means$id)
+# Group by ID and find the model with the minimum value
+  min_values <- get_from_means %>%
+  group_by(id) %>%
+  filter(means == min(means))
+
+# Count the occurrences of each model with the minimum value per run
+  model_counts <- min_values %>%
+    group_by(names) %>%
+    summarize(Count = n())
+
+  get_from_loo <- do.call(rbind, lapply(loo, "[[", 2))
+
+  get_from_loo = get_from_loo %>% filter(elpd_diff == 0) %>% mutate(model = row.names(.)) %>% mutate(realmodel = sub("^[0-9]+\\.(.*)", "\\1", model)) %>% group_by(realmodel) %>% summarize(Count = n())
+
+  return(list(fromloo = get_from_loo, frommean = model_counts))
+}
+
+get_value(rw_loo)
+```
+
+```{r fitting RW model to session 1}
+df= read.csv(here::here("data_TPL_AC.csv")) %>% 
+  rename_all(tolower) %>% 
+  filter(trial != 0) %>% 
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% 
+  mutate_all(replace_na, 0)
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+
+df = df %>% filter(session == 1)
+
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data1 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
+            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
+            expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
+            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
+            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)))
+
+mod = cmdstan_model(here::here("Stan","myRW_real.stan"))
+
+rw_fit_sess1 <- mod$sample(
+      data = data1,
+      chains = 4, 
+      parallel_chains = 4,
+      refresh = 100,
+      adapt_delta = 0.90,
+      max_treedepth = 12
+    )
+
+ppu_hier(fit = rw_fit_sess1,
+         parameters = c("alpha","w1","precision_percept"),
+         reals = NA)
+
+```
+
+```{r plotting 1 agent}
+
+percept = sum %>% filter(str_detect(variable, "painMu"))
+percept = percept[1:160,]
+
+expect = sum %>% filter(str_detect(variable, "expectMu"))
+expect = expect[1:160,]
+
+percept$stim = data$stim
+percept$expect = expect$mean
+
+percept %>% ggplot(aes(x=1:nrow(.), y = mean, col = as.factor(stim)))+geom_point()
+
+percept %>% ggplot(aes(x=expect, y = mean, col = as.factor(stim)))+geom_point()
+
+ass = sum %>% filter(str_detect(variable, "associ"))
+ass = ass[1:161,]
+
+ass %>% ggplot(aes(x=1:nrow(.), y = mean))+geom_line()+geom_point(data = data, aes(x = trial, y = u))
+
+rw_fit_sess1$diagnostic_summary()
+
+alpha = get_diag(rw_fit_sess1, "alpha")
+w1 = get_diag(rw_fit_sess1, "w1")
+pp = get_diag(rw_fit_sess1, "precision_percept")
+beta = get_diag(rw_fit_sess1, "beta")
+
+```
+
+```{r fitting RW model to session 2}
+df= read.csv(here::here("data_TPL_AC.csv")) %>% 
+  rename_all(tolower) %>% 
+  filter(trial != 0) %>% 
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% 
+  mutate_all(replace_na, 0)
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+
+df = df %>% filter(session == 2)
+
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data1 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
+            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
+            expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
+            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
+            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)))
+
+mod = cmdstan_model(here::here("Stan","myRW_real.stan"))
+
+rw_fit_sess2 <- mod$sample(
+      data = data1,
+      chains = 4, 
+      parallel_chains = 4,
+      refresh = 100,
+      adapt_delta = 0.90,
+      max_treedepth = 12
+    )
+
+ppu_hier(fit = rw_fit_sess2,
+         parameters = c("alpha","w1","precision_percept"),
+         reals = NA)
+
+```
+
+```{r fitting Kalman model to session 1}
+df= read.csv(here::here("data_TPL_AC.csv")) %>%
+  rename_all(tolower) %>%
+  filter(trial != 0) %>%
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
+  mutate_all(replace_na, 0)
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+
+df = df %>% filter(session == 1)
+
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data1 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
+            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
+            expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
+            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
+            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)),
+            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL))
+            )
+
+mod = cmdstan_model(here::here("Stan","myKalmanfilter_v3_nocent.stan"))
+
+kalman_fit_sess1 <- mod$sample(
+      data = data1,
+      chains = 4,
+      parallel_chains = 4,
+      refresh = 100,
+      adapt_delta = 0.90,
+      max_treedepth = 12
+    )
+
+ppu_hier(fit = kalman_fit_sess1,
+         parameters = c("sigmaEta","sigmaPsi","sigmaEpsilon","precision_percept"),
+         reals = NA)
+
+# 
+# ppu_sub(fit = fit,
+#         parameter = "precision_percept",
+#         reals = df,
+#         lims = -1,
+#         lime = 10,
+#         nsubs = NA
+#         )
+
+get_diag(kalman_fit_sess1, "sigmaEta")
+get_diag(kalman_fit_sess1, "sigmaPsi")
+get_diag(kalman_fit_sess1, "sigmaEpsilon")
+
+sum = kalman_fit_sess1$summary()
+
+ass = sum %>% filter(str_detect(variable, "perceptmuu"))
+ass = ass[(161*2-1):(161*3-1),]
+
+exp = sum %>% filter(str_detect(variable, "exp_muu"))
+exp = exp[(161*2-1):(161*3-1),]
+
+ass$exp = exp$mean
+
+ass %>% ggplot(aes(x=exp, y = mean))+geom_point()
+
+```
+
+```{r fitting Kalman model to session 2}
+df= read.csv(here::here("data_TPL_AC.csv")) %>%
+  rename_all(tolower) %>%
+  filter(trial != 0) %>%
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
+  mutate_all(replace_na, 0)
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+
+df = df %>% filter(session == 2)
+
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data1 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
+            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
+            expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
+            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
+            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)),
+            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL))
+            )
+
+mod = cmdstan_model(here::here("Stan","myKalmanfilter_v3_nocent.stan"))
+
+kalman_fit_sess2 <- mod$sample(
+      data = data1,
+      chains = 4,
+      parallel_chains = 4,
+      refresh = 100,
+      adapt_delta = 0.90,
+      max_treedepth = 12
+    )
+
+ppu_hier(fit = kalman_fit_sess2,
+         parameters = c("sigmaEta","sigmaPsi","sigmaEpsilon","precision_percept"),
+         reals = NA)
+
+```
+
+```{r fitting WB model to session 1}
+df= read.csv(here::here("data_TPL_AC.csv")) %>% 
+  rename_all(tolower) %>% 
+  filter(trial != 0) %>% 
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% 
+  mutate_all(replace_na, 0)
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+
+df = df %>% filter(session == 1)
+
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(c(percept,stim), ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data1 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
+            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
+            pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
+            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
+            cue = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL))
+            )
+
+mod = cmdstan_model(here::here("Stan","hier_weighted_bayes.stan"))
+
+wb_fit_sess1  <- mod$sample(
+      data = data1,
+      chains = 4, 
+      parallel_chains = 4,
+      refresh = 100,
+      adapt_delta = 0.90,
+      max_treedepth = 12
+    )
+
+wb_fit_sess1$diagnostic_summary()
+
+alpha = get_diag(wb_fit_sess1, "alpha")
+w1 = get_diag(wb_fit_sess1, "w1")
+w2 = get_diag(wb_fit_sess1, "w2")
+pp = get_diag(wb_fit_sess1, "percept_precision")
+beta = get_diag(wb_fit_sess1, "beta")
+
+```
+
+```{r fitting WB model to session 2}
+
+df= read.csv(here::here("data_TPL_AC.csv")) %>% 
+  rename_all(tolower) %>% 
+  filter(trial != 0) %>% 
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% 
+  mutate_all(replace_na, 0)
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+
+df = df %>% filter(session == 2)
+
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(c(percept,stim), ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data1 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
+            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
+            pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
+            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
+            cue = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL))
+            )
+
+mod = cmdstan_model(here::here("Stan","hier_weighted_bayes.stan"))
+
+wb_fit_sess2 <- mod$sample(
+      data = data1,
+      chains = 4, 
+      parallel_chains = 4,
+      refresh = 100,
+      adapt_delta = 0.90,
+      max_treedepth = 12
+    )
+
+alpha = get_diag(wb_fit_sess1, "alpha")
+w1 = get_diag(wb_fit_sess1, "w1")
+w2 = get_diag(wb_fit_sess1, "w2")
+pp = get_diag(wb_fit_sess1, "percept_precision")
+beta = get_diag(wb_fit_sess1, "beta")
+
+```
+
+```{r}
+get_corplot(rw_fit_sess1, rw_fit_sess2, "alpha")
+get_corplot(rw_fit_sess1, rw_fit_sess2, "w1")
+get_corplot(rw_fit_sess1, rw_fit_sess2, "precision_percept")
+
+get_corplot(wb_fit_sess1, wb_fit_sess2, "alpha")
+get_corplot(wb_fit_sess1, wb_fit_sess2, "w1")
+get_corplot(wb_fit_sess1, wb_fit_sess2, "w2")
+get_corplot(wb_fit_sess1, wb_fit_sess2, "beta")
+get_corplot(wb_fit_sess1, wb_fit_sess2, "percept_precision")
+
+```
+
+```{r}
+df= read.csv(here::here("data_TPL_AC.csv")) %>%
+  rename_all(tolower) %>%
+  filter(trial != 0) %>%
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
+  mutate_all(replace_na, 0)
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
+
+df = df %>% filter(session == 1)
+
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data1 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
+            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
+            expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
+            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
+            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)),
+            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL))
+            )
+
+mod = cmdstan_model(here::here("Stan","myKalmanfilter_v3_nocent.stan"))
+
+kalman_fit_sess1 <- mod$sample(
+      data = data1,
+      chains = 4,
+      parallel_chains = 4,
+      refresh = 100,
+      adapt_delta = 0.90,
+      max_treedepth = 12
+    )
+```
+
+```{r hierachical session correlation (RW)}
+
+df= read.csv(here::here("data_TPL_AC.csv")) %>%
+  rename_all(tolower) %>%
+  filter(trial != 0) %>%
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
+  mutate_all(replace_na, 0) %>% mutate(id = as.factor(id), trial = as.factor(trial), session = as.factor(session))
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data1 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(session == 1) %>% filter(id %in% unique(id)[1])),
+            sesions = length(unique(data$session)),
+            percept = get_3darray(data,variable = "percept"),
+            expectPain = get_3darray(data,variable = "pred"),
+            percept_bin = get_3darray(data,variable = "percept_bin"),
+            stim = get_3darray(data,variable = "stim"),
+            cues = get_3darray(data,variable = "cue"),
+            u = get_3darray(data,variable = "u")
+            )
+
+mod = cmdstan_model(here::here("Stan","fitting both sessions","myRW_real_both_sess.stan"))
+
+fit <- mod$sample(
+  data = data1,
+  chains = 4,
+  parallel_chains = 4,
+  refresh = 100,
+  adapt_delta = 0.90,
+  max_treedepth = 12
+)
+
+sum = fit$summary(variables = c("mu_alpha","mu_w1","sd_beta","sd_precision_percept", "kappa_alpha","kappa_w1","alpha","w1","beta","precision_percept"))
+
+variabless = c("mu_alpha[1]","mu_w1[1]","sd_beta[1]","sd_precision_percept[1]","mu_alpha[2]","mu_w1[2]","sd_beta[2]","sd_precision_percept[2]")
+
+pairs = mcmc_pairs(fit$draws(variables = variabless), np = nuts_params(fit), pars = variabless,
+                   off_diag_args = list(size = 0.75))
+
+mcmc_trace(fit$draws(variables = "alpha"))
+
+alpha = fit$summary(variables = "alpha")
+w1 = fit$summary(variables = "w1")
+
+alphas1 <- w1 %>%
+  filter(grepl("1]$", variable))
+
+alphas2 <- w1 %>%
+  filter(grepl("2]$", variable))
+
+cor.test(alphas1$mean, alphas2$mean)
+
+correlation = as_draws_df(fit$draws(variables = "correlation_alpha"))
+hist(correlation$correlation_alpha)
+correlation = as_draws_df(fit$draws(variables = "correlation_w1"))
+hist(correlation$correlation_w1)
+```
+
+```{r hierachical session correlation (WB)}
+
+df= read.csv(here::here("data_TPL_AC.csv")) %>%
+  rename_all(tolower) %>%
+  filter(trial != 0) %>%
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
+  mutate_all(replace_na, 0) %>% mutate(id = as.factor(id), trial = as.factor(trial), session = as.factor(session))
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(c(percept,stim), ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data1 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(session == 1) %>% filter(id %in% unique(id)[1])),
+            sesions = length(unique(data$session)),
+            percept = get_3darray(data,variable = "percept"),
+            pred = get_3darray(data,variable = "pred"),
+            percept_bin = get_3darray(data,variable = "percept_bin"),
+            stim = get_3darray(data,variable = "stim"),
+            cue = get_3darray(data,variable = "cue")
+            )
+
+mod = cmdstan_model(here::here("Stan","fitting both sessions","hier_weighted_bayes_correlation.stan"))
+
+fit_wb_bs <- mod$sample(
+  data = data1,
+  chains = 4,
+  parallel_chains = 4,
+  refresh = 100,
+  adapt_delta = 0.90,
+  max_treedepth = 12
+)
+
+correlation = as_draws_df(fit_wb_bs$draws(variables = "correlation_alpha"))
+hist(correlation$correlation_alpha)
+correlation = as_draws_df(fit_wb_bs$draws(variables = "correlation_w1"))
+hist(correlation$correlation_w1)
+correlation = as_draws_df(fit_wb_bs$draws(variables = "correlation_w2"))
+hist(correlation$correlation_w2)
+
+```
+
+```{r fitting to both sessions to hierachiacal RW}
+
+df= read.csv(here::here("data_TPL_AC.csv")) %>%
+  rename_all(tolower) %>%
+  filter(trial != 0) %>%
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
+  mutate_all(replace_na, 0)
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
+
+#source(here::here("stan_functions.R"))
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data1 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(session == 1) %>% filter(id %in% unique(id)[1])),
+            sessions = 2,
+            pred = get_3darray(data,variable = "pred"),
+            u = get_3darray(data,variable = "u")
+            )
+
+mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier.stan"))
+
+rw_fit_ses1 <- mod$sample(
+      data = data1,
+      chains = 4,
+      parallel_chains = 4,
+      refresh = 100,
+      adapt_delta = 0.90,
+      max_treedepth = 12
+    )
+
+sum = rw_fit_ses1$summary(variables = c("alpha", "mu_alpha","sd_alpha","mu_mu_alpha","sd_sd_alpha","mu_sd_alpha","sd_mu_alpha"))
+```
+
+```{r, fitting to real data tester hierachical RW sessions1}
+
+df= read.csv(here::here("data_TPL_AC.csv")) %>%
+  rename_all(tolower) %>%
+  filter(trial != 0) %>%
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
+  mutate_all(replace_na, 0)
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
+
+df = df %>% filter(session == 1)
+
+#source(here::here("stan_functions.R"))
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
 
@@
 
+mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier_complete.stan"))
+
+rw_fit_ses1 <- mod$sample(
+      data = data2,
+      chains = 4,
+      parallel_chains = 4,
+      refresh = 100,
+      adapt_delta = 0.90,
+      max_treedepth = 12
+    )
+
+sum1 = rw_fit_ses1$summary()
+```
+
+```{r, fitting to real data tester hierachical RW sessions2}
+
+df= read.csv(here::here("data_TPL_AC.csv")) %>%
+  rename_all(tolower) %>%
+  filter(trial != 0) %>%
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
+  mutate_all(replace_na, 0)
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
+
+df = df %>% filter(session == 2)
+
+#source(here::here("stan_functions.R"))
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data2 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
+            pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
+            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
+            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
+            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL)),
+            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL))
+            )
+
+mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier_complete.stan"))
+
+rw_fit_ses2 <- mod$sample(
+      data = data2,
+      chains = 4,
+      parallel_chains = 4,
+      refresh = 100,
+      adapt_delta = 0.90,
+      max_treedepth = 12
+    )
+
+sum2 = rw_fit_ses2$summary()
+
+get_corplot(rw_fit_ses1,rw_fit_ses2, "b2_b")
+```
+
+```{r}
+
+df= read.csv(here::here("data_TPL_AC.csv")) %>%
+  rename_all(tolower) %>%
+  filter(trial != 0) %>%
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
+  mutate_all(replace_na, 0) %>% mutate(id = as.factor(id), trial = as.factor(trial), session = as.factor(session))
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
+
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data1 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(session == 1) %>% filter(id %in% unique(id)[1])),
+            sesions = length(unique(data$session)),
+            percept = get_3darray(data,variable = "percept"),
+            pred = get_3darray(data,variable = "pred"),
+            percept_bin = get_3darray(data,variable = "percept_bin"),
+            stim = get_3darray(data,variable = "stim"),
+            cues = get_3darray(data,variable = "cue"),
+            u = get_3darray(data,variable = "u")
+            )
+
+mod = cmdstan_model(here::here("Stan","fitting both sessions","rw_vs_rw_hier_complete_both_sessions.stan"))
+
+fit <- mod$sample(
+  data = data1,
+  chains = 4,
+  parallel_chains = 4,
+  refresh = 10,
+  adapt_delta = 0.90,
+  max_treedepth = 12
+)
+
+```
+
+```{r}
+mu_alpha = 0.3
+kappa_alpha = 30
+
+mu_b0 = -5
+sd_b0 = 1
+
+mu_b1 = -1
+sd_b1 = 1
+
+mu_b2 = 1.3
+sd_b2 = 1.3
+
+mu_b0_b = -5
+sd_b0_b = 2
+
+mu_b1_b = 0.5
+sd_b1_b = 0.5
+
+mu_b2_b = 0.5
+sd_b2_b = 0.5
+
+sd_percept_precision = 0.5
+
+nsubs = 10
+
+parameters = expand.grid(mu_alpha = mu_alpha,
+                         kappa_alpha = kappa_alpha,
+                         mu_b0 = mu_b0,
+                         sd_b0 = sd_b0,
+                         mu_b1 = mu_b1,
+                         sd_b1 = sd_b1,
+                         mu_b2 = mu_b2,
+                         sd_b2 = sd_b2,
+                         mu_b0_b = mu_b0_b,
+                         sd_b0_b = sd_b0_b,
+                         mu_b1_b = mu_b1_b,
+                         sd_b1_b = sd_b1_b,
+                         mu_b2_b = mu_b2_b,
+                         sd_b2_b = sd_b2_b,
+                         sd_percept_precision = sd_percept_precision,
+                         nsubs = nsubs)
+
+df = hier_rw_logistic(parameters)
+
+data = df[[1]]
+
+data2 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
+            pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
+            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
+            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
+            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL)),
+            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL))
+            )
+
 hier = df[[2]]
@@
 ```
-
-<!-- ```{r fitting to real data tester hierachical RW seesion2} -->
-
-<!-- df= read.csv(here::here("data_TPL_AC.csv")) %>% -->
-<!--   rename_all(tolower) %>% -->
-<!--   filter(trial != 0) %>% -->
-<!--   rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% -->
-<!--   mutate_all(replace_na, 0) -->
-
-<!-- df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0)) -->
-<!-- df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0)) -->
-
-<!-- df = df %>% filter(session == 2) -->
-
-<!-- #source(here::here("stan_functions.R")) -->
-<!-- #fitting hierachically -->
-<!-- data = df %>% mutate(percept = percept/100) -->
-
-<!-- data = data %>% mutate(across(percept, ~case_when( -->
-<!--     . < 0.001 ~ 0.001, -->
-<!--     . > 0.999 ~ 0.999, -->
-<!--     TRUE ~ . -->
-<!--   ))) -->
-
-<!-- data2 = list(nsubs = length(unique(data$id)), -->
-<!--             ntrials = nrow(data %>% filter(id %in% unique(id)[1])), -->
-<!--             pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)), -->
-<!--             u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL)) -->
-<!--             ) -->
-
-<!-- mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier.stan")) -->
-
-<!-- rw_fit_ses2 <- mod$sample( -->
-<!--       data = data2, -->
-<!--       chains = 4, -->
-<!--       parallel_chains = 4, -->
-<!--       refresh = 100, -->
-<!--       adapt_delta = 0.90, -->
-<!--       max_treedepth = 12 -->
-<!--     ) -->
-
-<!-- ``` -->

### 2023-05-26 scripts/model recovery.R

@@ -30,31 +30,31 @@ model_fitter_rwdata = function(parameters_rw){
   
   rw_model = here::here("Stan","myRW_real.stan")
   wb_model = here::here("Stan","hier_weighted_bayes.stan")
-  kalman_model = here::here("Stan","myKalmanfilter_v2.stan")
-  
+  logs = here::here("Stan","rw_vs_rw_hier_complete.stan")
   
   data1_rw_wb = data1_rw
-  data1_rw_kalman = data1_rw
+  data1_rw_logs = data1_rw
   
   names(data1_rw_wb) = c("nsubs","ntrials","percept","pred","percept_bin","stim","cue")
+  names(data1_rw_logs) = c("nsubs","ntrials","percept","pred","percept_bin","stim","cues")
   data1_rw_wb$stim = ifelse(data1_rw_wb$stim == 1, 0.999, 0.001)
   
-  data1_rw_kalman$u = as.matrix(data_rw %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL))
+  data1_rw_logs$u = as.matrix(data_rw %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL))
   
   
   loo_rw_rw = get_loo(rw_model, data1_rw)
   loo_rw_wb = get_loo(wb_model, data1_rw_wb)
-  loo_rw_kalman = get_loo(kalman_model, data1_rw_kalman)
+  loo_rw_logs = get_loo(logs, data1_rw_logs)
   
   
-  comparison = data.frame(loo_compare(list(loo_rw_rw[[3]],loo_rw_wb[[3]],loo_rw_kalman[[3]])))
+  comparison = data.frame(loo_compare(list(loo_rw_rw[[3]],loo_rw_wb[[3]],loo_rw_logs[[3]])))
   comparison$id = id
 
   return(list(data.frame(names = c("rw",
                                    "wb",
-                                   "kalman"),
-                         means = c(loo_rw_rw[[1]],loo_rw_wb[[1]],loo_rw_kalman[[1]]),
-                         sds = c(loo_rw_rw[[2]],loo_rw_wb[[2]],loo_rw_kalman[[2]]),
+                                   "logs"),
+                         means = c(loo_rw_rw[[1]],loo_rw_wb[[1]],loo_rw_logs[[1]]),
+                         sds = c(loo_rw_rw[[2]],loo_rw_wb[[2]],loo_rw_logs[[2]]),
                          id = id),
[…]

### 2023-05-26 scripts/visualize_parameters.R

@@ -42,7 +42,7 @@ RW = function(dd){
     facet_grid(alpha~w1, labeller = label_both)+
     theme_classic()+
     scale_y_continuous("Cue-stimulus association", breaks = scales::pretty_breaks(n = 3))+
-    scale_x_continuous("Trial", breaks = scales::pretty_breaks(n = 3))    
+    scale_x_continuous("Trial", breaks = scales::pretty_breaks(n = 3))+theme(text = element_text(size = 20))
   
   
   plot2 = dd %>% ggplot(aes(exp, y = percept,col = precision_percept, group = interaction(stim, precision_percept)))+
@@ -51,7 +51,7 @@ RW = function(dd){
     geom_smooth(method = "lm")+
     theme_classic()+
     scale_y_continuous("Mean of percept", breaks = scales::pretty_breaks(n = 3))+
-    scale_x_continuous("% Expectation of Stimulus being Hot", breaks = scales::pretty_breaks(n = 3))+ theme(legend.position = "top")+ theme(text = element_text(size = 14))    
+    scale_x_continuous("% Expectation of Stimulus being Hot", breaks = scales::pretty_breaks(n = 3))+ theme(legend.position = "top")+ theme(text = element_text(size = 20))    
   
  
   plot1+plot2
@@ -154,7 +154,7 @@ KALMAN_v2 = function(dd){
     facet_grid(sigmaEta~sigmaPsi, labeller = label_both)+
     theme_classic()+
     scale_y_continuous("Cue-stimulus association", breaks = scales::pretty_breaks(n = 3))+
-    scale_x_continuous("Trial", breaks = scales::pretty_breaks(n = 3))+theme(legend.position = "top")    
+    scale_x_continuous("Trial", breaks = scales::pretty_breaks(n = 3))+theme(legend.position = "top")+theme(text = element_text(size = 20))    
   
   
   
@@ -166,7 +166,7 @@ KALMAN_v2 = function(dd){
     theme_classic()+
     scale_y_continuous("Mean of percept", breaks = scales::pretty_breaks(n = 3))+
     scale_x_continuous("% Expectation of Stimulus being Hot", breaks = scales::pretty_breaks(n = 3))+theme(legend.position = "top")+
-    ggtitle("precision percept = 155")    
+    ggtitle("precision percept = 155")+theme(text = element_text(size = 20))
   
   
   plot1+plot2
@@ -216,7 +216,7 @@ WB = function(dd){
[…]

### 2023-05-29 Manuscript1.Rmd
cleaning

@@
 
+### loading packages
 ```{r setup, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
-pacman::p_load(tidyverse, osfr, lmerTest, MuMIn, DHARMa, here, cmdstanr, tidybayes, bayesplot, posterior,future,furrr, patchwork, R.utils, brms, extraDistr,cowplot)
+pacman::p_load(tidyverse, osfr, lmerTest, MuMIn, DHARMa, here, cmdstanr, tidybayes, bayesplot, posterior,future,furrr, patchwork, R.utils, brms, extraDistr,cowplot,HDInterval)
 
@@
 
-## R Markdown
-
-```{r parameters visualization, fig.height=14, fig.width=16}
+### parameter visualization for the four models (figure 1 & 2)
+```{r parameter visualization, fig.height=10, fig.width=12}
 dd = get_experiment()
@@
 wbplot = WB(dd)
+
+RW_logistic = RW_logistic_vis(dd)
 
@@
   area(1, 1, 1,1),
-  area(1, 2, 1,2),
-  area(1, 3, 1,3)
+  area(1, 2, 1,2)
 
@@
 
-p1 = kalmanplot[[1]]+rwplot[[1]]+wbplot[[1]]+plot_layout(design = layout)+plot_annotation(tag_levels = list(c('B', 'C',"D","E","F","G")))
-p2 = kalmanplot[[2]]+rwplot[[2]]+wbplot[[2]]+plot_layout(design = layout)+plot_annotation(tag_levels = list(c("E","F","G")))
+p1 = RW_logistic[[1]]+rwplot[[1]]+scale_y_continuous(" ")+plot_layout(design = layout)+plot_annotation(tag_levels = list(c('B', 'C')))
+p2 = wbplot[[1]]+kalmanplot[[1]]+scale_y_continuous(" ")+plot_layout(design = layout)+plot_annotation(tag_levels = list(c("D","E")))
+p3 = RW_logistic[[2]]+rwplot[[2]]+scale_y_continuous(" ")+plot_layout(design = layout)+plot_annotation(tag_levels = list(c("A","B")))
+p4  = wbplot[[2]]+kalmanplot[[2]]+scale_y_continuous(" ")+plot_layout(design = layout)+plot_annotation(tag_levels = list(c("C","D")))
 
@@
 p2
-
-RW_logistic = RW_logistic_vis(dd)
-```
-
+p3
+p4
+
+```
+
+### parameter recovery for the four models
 ```{r parameter recovery for RW}
@@
 rw_pp = furrr::future_map(data_list, ~parameter_recovery_rw(.x), .progress = TRUE, .options = furrr_options(seed = 123))
-
 ```
@@
 
+#plotting parameter recovery (figure 3)
 ```{r}
-
 files = paste0(here::here("workspace","parameterrecovery"),"/",list.files(here::here("workspace","parameterrecovery")))
@@
 #plot parameterrecovery
-load(files[[2]])
-q = lapply(here("scripts", scripts), source)
-rwplot = plot_parameterrecovery(rw_pp, div = T, subs = 5)
-load(files[[3]])
-q = lapply(here("scripts", scripts), source)
-wbplot = plot_parameterrecovery(wb_pp, div = T, subs = 5)
 load(files[[1]])
@@
 kalmanplot = plot_parameterrecovery(kalman_pp, div = T, subs = 5)
+load(files[[2]])
+q = lapply(here("scripts", scripts), source)
+logisticplot = plot_parameterrecovery(rw_pp_logs, div = F, subs = 5)
+load(files[[3]])
+q = lapply(here("scripts", scripts), source)
+rwplot = plot_parameterrecovery(rw_pp, div = T, subs = 5)
+load(files[[4]])
+q = lapply(here("scripts", scripts), source)
+wbplot = plot_parameterrecovery(wb_pp, div = T, subs = 5)
 
@@
 
-plot(layout)
-
-((rwplot[[1]]+wbplot[[1]]+kalmanplot[[1]])/(rwplot[[2]]+wbplot[[2]]+kalmanplot[[2]])/((rwplot[[3]]+wbplot[[3]]+kalmanplot[[3]])))+
+((rwplot[[1]]+wbplot[[1]])/(kalmanplot[[1]]+logisticplot[[1]]))+
   plot_annotation(tag_levels = 'A')+
-  plot_layout(design = layout,guides = 'collect')
-
-```
-
+  plot_layout(guides = 'collect')
+
+((rwplot[[2]]+wbplot[[2]])/(kalmanplot[[2]]+logisticplot[[2]]))+
+  plot_annotation(tag_levels = 'A')+
+  plot_layout(guides = 'collect')
+
+```
+
+### model recovery for the three computation models
 ```{r model recovery}
@@
 kappa_alpha = 50
-mu_w1 = rep(0.3,100)
+mu_w1 = 0.3
 kappa_w1 = 50
@@
 
-mu_b2 = 2
+mu_b2 = 1
 sd_b2 = 1
 
-mu_b0_b = -4
+mu_b0_b = -3
 sd_b0_b = 0.5
 
-mu_b1_b = 7
+mu_b1_b = 5
 sd_b1_b = 0.5
@@
 
+plan(multisession, workers = 10)
+
+rw_loo = furrr::future_map(data_list, ~model_fitter_rwdata(.x), .progress = TRUE, .options = furrr_options(seed = 123))
+
+elpld_loo <- map_dfr(rw_loo, ~ .x[[1]])
+
+full_loo <- map_dfr(rw_loo, ~ .x[[2]])
+
+########################################## fit data_wb
+
+data_list = data_list_wb
+
 plan(multisession, workers = availableCores()-1)
 
-rw_loo = furrr::future_map(data_list, ~model_fitter_rwdata(.x), .progress = TRUE, .options = furrr_options(seed = 123))
-
-elpld_loo <- map_dfr(rw_loo, ~ .x[[1]])
-
-full_loo <- map_dfr(rw_loo, ~ .x[[2]])
-
-########################################## fit data_wb
-
-data_list = data_list_wb
-
-plan(multisession, workers = availableCores()-1)
-
 wb_loo = furrr::future_map(data_list, ~model_fitter_wbdata(.x), .progress = TRUE, .options = furrr_options(seed = 123))
@@
 
-data_list = data_list_logs
-
-plan(multisession, workers = availableCores()-1)
-
-plan(multisession, workers = 5)
+data_list = data_list_logs[1:50]
+
+plan(multisession, workers = 10)
 
@@
 
-```{r model recovery table:}
+### table 1
+```{r model recovery table}
+
+files = paste0(here::here("workspace","model recovery"),"/",list.files(here::here("workspace","model recovery")))
+
+#plot parameterrecovery
+load(files[[1]])
 
@@
 
-get_value(rw_loo)
-```
+kalmandata = get_value(kalman_loo)
+rwdata = get_value(rw_loo)
+wbdata = get_value(wb_loo)
+
+```
+
+### fitting the models to session 1's data
 
@@
 
-```{r plotting 1 agent}
-
-percept = sum %>% filter(str_detect(variable, "painMu"))
-percept = percept[1:160,]
-
-expect = sum %>% filter(str_detect(variable, "expectMu"))
-expect = expect[1:160,]
-
-percept$stim = data$stim
-percept$expect = expect$mean
-
-percept %>% ggplot(aes(x=1:nrow(.), y = mean, col = as.factor(stim)))+geom_point()
-
-percept %>% ggplot(aes(x=expect, y = mean, col = as.factor(stim)))+geom_point()
-
-ass = sum %>% filter(str_detect(variable, "associ"))
-ass = ass[1:161,]
-
-ass %>% ggplot(aes(x=1:nrow(.), y = mean))+geom_line()+geom_point(data = data, aes(x = trial, y = u))
-
-rw_fit_sess1$diagnostic_summary()
-
-alpha = get_diag(rw_fit_sess1, "alpha")
-w1 = get_diag(rw_fit_sess1, "w1")
-pp = get_diag(rw_fit_sess1, "precision_percept")
-beta = get_diag(rw_fit_sess1, "beta")
-
-```
+```{r fitting WB model to session 1}
+df= read.csv(here::here("data_TPL_AC.csv")) %>% 
+  rename_all(tolower) %>% 
+  filter(trial != 0) %>% 
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% 
+  mutate_all(replace_na, 0)
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+
+df = df %>% filter(session == 1)
+
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(c(percept,stim), ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data1 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
+            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
+            pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
+            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
+            cue = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL))
+            )
+
+mod = cmdstan_model(here::here("Stan","hier_weighted_bayes.stan"))
+
+wb_fit_sess1  <- mod$sample(
+      data = data1,
+      chains = 4, 
+      parallel_chains = 4,
+      refresh = 100,
+      adapt_delta = 0.90,
+      max_treedepth = 12
+    )
+
+wb_fit_sess1$diagnostic_summary()
+
+alpha = get_diag(wb_fit_sess1, "alpha")
+w1 = get_diag(wb_fit_sess1, "w1")
+w2 = get_diag(wb_fit_sess1, "w2")
+pp = get_diag(wb_fit_sess1, "percept_precision")
+beta = get_diag(wb_fit_sess1, "beta")
+
+```
+
+```{r, fitting to real data tester hierachical logs RW sessions1}
+
+df= read.csv(here::here("data_TPL_AC.csv")) %>%
+  rename_all(tolower) %>%
+  filter(trial != 0) %>%
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
+  mutate_all(replace_na, 0)
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
+
+df = df %>% filter(session == 1)
+
+#source(here::here("stan_functions.R"))
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data2 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
+            pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
+            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
+            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
+            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL)),
+            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL))
+            )
+
+mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier_complete.stan"))
+
+rw_logs_fit_ses1 <- mod$sample(
+      data = data2,
+      chains = 4,
+      parallel_chains = 4,
+      refresh = 100,
+      adapt_delta = 0.90,
+      max_treedepth = 12
+    )
+
+sum1 = rw_logs_fit_ses1$summary()
+```
+
+### Model comparison on sessions 1 (table 2)
+```{r, model comparison}
+#rw = rw_fit_sess1$loo()
+#wb = wb_fit_sess1$loo()
+#rw_logs = rw_logs_fit_ses1$loo()
+
+rw = as_draws_df(rw_fit_sess1$draws(variables = "log_lik"))
+wb = as_draws_df(wb_fit_sess1$draws(variables = "log_lik"))
+rw_logs = as_draws_df(rw_logs_fit_ses1$draws(variables = "log_lik"))
+
+rows_with_na <- which(apply(is.na(wb), 1, any))
+wb = wb[-rows_with_na,]
+rw = rw[-rows_with_na,]
+rw_logs = rw_logs[-rows_with_na, ]
+
+wb = loo::loo(as.matrix(wb))
+rw = loo::loo(as.matrix(rw))
+rw_logs = loo::loo(as.matrix(rw_logs))
+
+loo_compare(rw,wb,rw_logs)
+loo_model_weights(list(rw,wb,rw_logs))
+```
+
+### fitting the models to session 2's data
 
@@
 
-```{r fitting Kalman model to session 1}
+### fitting the models to session 2's data
+
+```{r fitting WB model to session 2}
+
 df= read.csv(here::here("data_TPL_AC.csv")) %>% 
@@
 
-df = df %>% filter(session == 1)
-
-#fitting hierachically
-data = df %>% mutate(percept = percept/100)
-
-data = data %>% mutate(across(percept, ~case_when(
-    . < 0.001 ~ 0.001,
-    . > 0.999 ~ 0.999,
-    TRUE ~ .
-  )))
-
-data1 = list(nsubs = length(unique(data$id)),
-            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
-            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
-            expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
-            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
-            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
-            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)),
-            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL))
-            )
-
-mod = cmdstan_model(here::here("Stan","myKalmanfilter_v3_nocent.stan"))
-
-kalman_fit_sess1 <- mod$sample(
-      data = data1,
-      chains = 4,
-      parallel_chains = 4,
-      refresh = 100,
-      adapt_delta = 0.90,
-      max_treedepth = 12
-    )
-
-ppu_hier(fit = kalman_fit_sess1,
-         parameters = c("sigmaEta","sigmaPsi","sigmaEpsilon","precision_percept"),
-         reals = NA)
-
-# 
-# ppu_sub(fit = fit,
-#         parameter = "precision_percept",
-#         reals = df,
-#         lims = -1,
-#         lime = 10,
-#         nsubs = NA
-#         )
-
-get_diag(kalman_fit_sess1, "sigmaEta")
-get_diag(kalman_fit_sess1, "sigmaPsi")
-get_diag(kalman_fit_sess1, "sigmaEpsilon")
-
-sum = kalman_fit_sess1$summary()
-
-ass = sum %>% filter(str_detect(variable, "perceptmuu"))
-ass = ass[(161*2-1):(161*3-1),]
-
-exp = sum %>% filter(str_detect(variable, "exp_muu"))
-exp = exp[(161*2-1):(161*3-1),]
-
-ass$exp = exp$mean
-
-ass %>% ggplot(aes(x=exp, y = mean))+geom_point()
-
-```
-
-```{r fitting Kalman model to session 2}
-df= read.csv(here::here("data_TPL_AC.csv")) %>%
-  rename_all(tolower) %>%
-  filter(trial != 0) %>%
-  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
-  mutate_all(replace_na, 0)
-
-df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
-
 df = df %>% filter(session == 2)
-
-#fitting hierachically
-data = df %>% mutate(percept = percept/100)
-
-data = data %>% mutate(across(percept, ~case_when(
-    . < 0.001 ~ 0.001,
-    . > 0.999 ~ 0.999,
-    TRUE ~ .
-  )))
-
-data1 = list(nsubs = length(unique(data$id)),
-            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
-            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
-            expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
-            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
-            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
-            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)),
-            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL))
-            )
-
-mod = cmdstan_model(here::here("Stan","myKalmanfilter_v3_nocent.stan"))
-
-kalman_fit_sess2 <- mod$sample(
-      data = data1,
-      chains = 4,
-      parallel_chains = 4,
-      refresh = 100,
-      adapt_delta = 0.90,
-      max_treedepth = 12
-    )
-
-ppu_hier(fit = kalman_fit_sess2,
-         parameters = c("sigmaEta","sigmaPsi","sigmaEpsilon","precision_percept"),
-         reals = NA)
-
-```
-
-```{r fitting WB model to session 1}
-df= read.csv(here::here("data_TPL_AC.csv")) %>% 
-  rename_all(tolower) %>% 
-  filter(trial != 0) %>% 
-  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% 
-  mutate_all(replace_na, 0)
-
-df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
-
-df = df %>% filter(session == 1)
 
@@
 
-wb_fit_sess1  <- mod$sample(
-      data = data1,
-      chains = 4, 
-      parallel_chains = 4,
-      refresh = 100,
-      adapt_delta = 0.90,
-      max_treedepth = 12
-    )
-
-wb_fit_sess1$diagnostic_summary()
-
-alpha = get_diag(wb_fit_sess1, "alpha")
-w1 = get_diag(wb_fit_sess1, "w1")
-w2 = get_diag(wb_fit_sess1, "w2")
-pp = get_diag(wb_fit_sess1, "percept_precision")
-beta = get_diag(wb_fit_sess1, "beta")
-
-```
-
-```{r fitting WB model to session 2}
-
-df= read.csv(here::here("data_TPL_AC.csv")) %>% 
-  rename_all(tolower) %>% 
-  filter(trial != 0) %>% 
-  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% 
-  mutate_all(replace_na, 0)
-
-df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
-
-df = df %>% filter(session == 2)
-
-#fitting hierachically
-data = df %>% mutate(percept = percept/100)
-
-data = data %>% mutate(across(c(percept,stim), ~case_when(
-    . < 0.001 ~ 0.001,
-    . > 0.999 ~ 0.999,
-    TRUE ~ .
-  )))
-
-data1 = list(nsubs = length(unique(data$id)),
-            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
-            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
-            pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
-            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
-            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
-            cue = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL))
-            )
-
-mod = cmdstan_model(here::here("Stan","hier_weighted_bayes.stan"))
-
 wb_fit_sess2 <- mod$sample(
@@
 
+wb_fit_sess2$diagnostic_summary()
+
 alpha = get_diag(wb_fit_sess1, "alpha")
@@
 
-```{r}
-get_corplot(rw_fit_sess1, rw_fit_sess2, "alpha")
-get_corplot(rw_fit_sess1, rw_fit_sess2, "w1")
-get_corplot(rw_fit_sess1, rw_fit_sess2, "precision_percept")
-
-get_corplot(wb_fit_sess1, wb_fit_sess2, "alpha")
-get_corplot(wb_fit_sess1, wb_fit_sess2, "w1")
-get_corplot(wb_fit_sess1, wb_fit_sess2, "w2")
-get_corplot(wb_fit_sess1, wb_fit_sess2, "beta")
-get_corplot(wb_fit_sess1, wb_fit_sess2, "percept_precision")
-
-```
-
-```{r}
+### fitting the models to session 2's data
+
+```{r, fitting to real data tester hierachical logs RW sessions2}
+
 df= read.csv(here::here("data_TPL_AC.csv")) %>%
@@
 
-df = df %>% filter(session == 1)
-
+df = df %>% filter(session == 2)
+
+#source(here::here("stan_functions.R"))
 #fitting hierachically
@@
 
-data1 = list(nsubs = length(unique(data$id)),
+data2 = list(nsubs = length(unique(data$id)),
             ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
+            pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
             percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
-            expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
-            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
             stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
-            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)),
-            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL))
-            )
-
-mod = cmdstan_model(here::here("Stan","myKalmanfilter_v3_nocent.stan"))
-
-kalman_fit_sess1 <- mod$sample(
-      data = data1,
+            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL)),
+            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL))
+            )
+
+mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier_complete.stan"))
+
+rw_logs_fit_ses2 <- mod$sample(
+      data = data2,
       chains = 4,
@@
     )
-```
+
+```
+
+### Model comparison on sessions 2 (table 2)
+
+```{r, model comparison}
+#rw = rw_fit_sess1$loo()
+#wb = wb_fit_sess1$loo()
+#rw_logs = rw_logs_fit_ses1$loo()
+
+rw = as_draws_df(rw_fit_sess2$draws(variables = "log_lik"))
+wb = as_draws_df(wb_fit_sess2$draws(variables = "log_lik"))
+rw_logs = as_draws_df(rw_logs_fit_ses2$draws(variables = "log_lik"))
+
+rows_with_na <- which(apply(is.na(wb), 1, any))
+wb = wb[-rows_with_na,]
+rw = rw[-rows_with_na,]
+rw_logs = rw_logs[-rows_with_na, ]
+
+wb = loo::loo(as.matrix(wb))
+rw = loo::loo(as.matrix(rw))
+rw_logs = loo::loo(as.matrix(rw_logs))
+
+loo_compare(rw_logs,rw,wb)
+
+loo_model_weights(list(rw_logs,rw,wb))
+```
+
+### Fitting the models to both sessions
 
 ```{r hierachical session correlation (RW)}
-
 df= read.csv(here::here("data_TPL_AC.csv")) %>%
@@
 
-fit <- mod$sample(
+fit_rw_bs <- mod$sample(
   data = data1,
@@
 
-sum = fit$summary(variables = c("mu_alpha","mu_w1","sd_beta","sd_precision_percept", "kappa_alpha","kappa_w1","alpha","w1","beta","precision_percept"))
-
-variabless = c("mu_alpha[1]","mu_w1[1]","sd_beta[1]","sd_precision_percept[1]","mu_alpha[2]","mu_w1[2]","sd_beta[2]","sd_precision_percept[2]")
-
-pairs = mcmc_pairs(fit$draws(variables = variabless), np = nuts_params(fit), pars = variabless,
-                   off_diag_args = list(size = 0.75))
-
-mcmc_trace(fit$draws(variables = "alpha"))
-
-alpha = fit$summary(variables = "alpha")
-w1 = fit$summary(variables = "w1")
-
-alphas1 <- w1 %>%
-  filter(grepl("1]$", variable))
-
-alphas2 <- w1 %>%
-  filter(grepl("2]$", variable))
-
-cor.test(alphas1$mean, alphas2$mean)
-
-correlation = as_draws_df(fit$draws(variables = "correlation_alpha"))
-hist(correlation$correlation_alpha)
-correlation = as_draws_df(fit$draws(variables = "correlation_w1"))
-hist(correlation$correlation_w1)
+alpha_wb = get_corplotreal(fit_rw_bs, "alpha", ymin = 0.1, ymax = 0.2, xmin = 0.2, xmax = 0.3)
+w1_wb = get_corplotreal(fit_rw_bs, "w1", ymin = 0.125, ymax = 0.3, xmin = 0.6, xmax = 0.75)
+
+HDInterval::hdi(as_draws_df(fit_rw_bs$draws(variables = "correlation_alpha")) %>% select(starts_with("correlation")))
+
+HDInterval::hdi(as_draws_df(fit_rw_bs$draws(variables = "correlation_w1")) %>% select(starts_with("correlation")))
+
 ```
@@
   parallel_chains = 4,
-  refresh = 100,
+  refresh = 50,
   adapt_delta = 0.90,
@@
 )
+
+fit_wb_bs$diagnostic_summary()
 
@@
 
-```
-
-```{r fitting to both sessions to hierachiacal RW}
-
-df= read.csv(here::here("data_TPL_AC.csv")) %>%
-  rename_all(tolower) %>%
-  filter(trial != 0) %>%
-  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
-  mutate_all(replace_na, 0)
-
-df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
-df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
-
-#source(here::here("stan_functions.R"))
-#fitting hierachically
-data = df %>% mutate(percept = percept/100)
-
-data = data %>% mutate(across(percept, ~case_when(
-    . < 0.001 ~ 0.001,
-    . > 0.999 ~ 0.999,
-    TRUE ~ .
-  )))
-
-data1 = list(nsubs = length(unique(data$id)),
-            ntrials = nrow(data %>% filter(session == 1) %>% filter(id %in% unique(id)[1])),
-            sessions = 2,
-            pred = get_3darray(data,variable = "pred"),
-            u = get_3darray(data,variable = "u")
-            )
-
-mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier.stan"))
-
-rw_fit_ses1 <- mod$sample(
-      data = data1,
-      chains = 4,
-      parallel_chains = 4,
-      refresh = 100,
-      adapt_delta = 0.90,
-      max_treedepth = 12
-    )
-
-sum = rw_fit_ses1$summary(variables = c("alpha", "mu_alpha","sd_alpha","mu_mu_alpha","sd_sd_alpha","mu_sd_alpha","sd_mu_alpha"))
-```
-
-```{r, fitting to real data tester hierachical RW sessions1}
-
-df= read.csv(here::here("data_TPL_AC.csv")) %>%
-  rename_all(tolower) %>%
-  filter(trial != 0) %>%
-  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
-  mutate_all(replace_na, 0)
-
-df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
-df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
-
-df = df %>% filter(session == 1)
-
-#source(here::here("stan_functions.R"))
-#fitting hierachically
-data = df %>% mutate(percept = percept/100)
-
-data = data %>% mutate(across(percept, ~case_when(
-    . < 0.001 ~ 0.001,
-    . > 0.999 ~ 0.999,
-    TRUE ~ .
-  )))
-
-data2 = list(nsubs = length(unique(data$id)),
-            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
-            pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
-            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
-            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
-            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
-            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL)),
-            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL))
-            )
-
-mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier_complete.stan"))
-
-rw_fit_ses1 <- mod$sample(
-      data = data2,
-      chains = 4,
-      parallel_chains = 4,
-      refresh = 100,
-      adapt_delta = 0.90,
-      max_treedepth = 12
-    )
-
-sum1 = rw_fit_ses1$summary()
-```
-
-```{r, fitting to real data tester hierachical RW sessions2}
-
-df= read.csv(here::here("data_TPL_AC.csv")) %>%
-  rename_all(tolower) %>%
-  filter(trial != 0) %>%
-  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
-  mutate_all(replace_na, 0)
-
-df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
-df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
-
-df = df %>% filter(session == 2)
-
-#source(here::here("stan_functions.R"))
-#fitting hierachically
-data = df %>% mutate(percept = percept/100)
-
-data = data %>% mutate(across(percept, ~case_when(
-    . < 0.001 ~ 0.001,
-    . > 0.999 ~ 0.999,
-    TRUE ~ .
-  )))
-
-data2 = list(nsubs = length(unique(data$id)),
-            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
-            pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
-            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
-            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
-            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
-            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL)),
-            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL))
-            )
-
-mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier_complete.stan"))
-
-rw_fit_ses2 <- mod$sample(
-      data = data2,
-      chains = 4,
-      parallel_chains = 4,
-      refresh = 100,
-      adapt_delta = 0.90,
-      max_treedepth = 12
-    )
-
-sum2 = rw_fit_ses2$summary()
-
-get_corplot(rw_fit_ses1,rw_fit_ses2, "b2_b")
-```
-
-```{r}
-
+alphaplot1 = get_corplot(wb_fit_sess1, wb_fit_sess2, "alpha")
+
+alpha_wb = get_corplotreal(fit_wb_bs, "alpha", ymin = -0.075, ymax = 0.325, xmin = 0.65, xmax = 1)
+w1_wb = get_corplotreal(fit_wb_bs, "w1", ymin = 0.02, ymax = 0.12, xmin = 0.19, xmax = 0.27)
+w2_wb = get_corplotreal(fit_wb_bs, "w2", ymin = 0.1, ymax = 0.2, xmin = 0.4, xmax = 0.6)
+
+HDInterval::hdi(as_draws_df(fit_wb_bs$draws(variables = "correlation_alpha")) %>% select(starts_with("correlation")))
+
+HDInterval::hdi(as_draws_df(fit_wb_bs$draws(variables = "correlation_w1")) %>% select(starts_with("correlation")))
+
+HDInterval::hdi(as_draws_df(fit_wb_bs$draws(variables = "correlation_w2")) %>% select(starts_with("correlation")))
+
+```
+
+```{r logistic both sessions}
 df= read.csv(here::here("data_TPL_AC.csv")) %>%
@@
 
-fit <- mod$sample(
+fit_rw_logs_bs <- mod$sample(
   data = data1,
@@
   parallel_chains = 4,
-  refresh = 10,
+  refresh = 50,
   adapt_delta = 0.90,
@@
 
-```
-
-```{r}
-mu_alpha = 0.3
-kappa_alpha = 30
-
-mu_b0 = -5
-sd_b0 = 1
-
-mu_b1 = -1
-sd_b1 = 1
-
-mu_b2 = 1.3
-sd_b2 = 1.3
-
-mu_b0_b = -5
-sd_b0_b = 2
-
-mu_b1_b = 0.5
-sd_b1_b = 0.5
-
-mu_b2_b = 0.5
-sd_b2_b = 0.5
-
-sd_percept_precision = 0.5
-
-nsubs = 10
-
-parameters = expand.grid(mu_alpha = mu_alpha,
-                         kappa_alpha = kappa_alpha,
-                         mu_b0 = mu_b0,
-                         sd_b0 = sd_b0,
-                         mu_b1 = mu_b1,
-                         sd_b1 = sd_b1,
-                         mu_b2 = mu_b2,
-                         sd_b2 = sd_b2,
-                         mu_b0_b = mu_b0_b,
-                         sd_b0_b = sd_b0_b,
-                         mu_b1_b = mu_b1_b,
-                         sd_b1_b = sd_b1_b,
-                         mu_b2_b = mu_b2_b,
-                         sd_b2_b = sd_b2_b,
-                         sd_percept_precision = sd_percept_precision,
-                         nsubs = nsubs)
-
-df = hier_rw_logistic(parameters)
-
-data = df[[1]]
-
-data2 = list(nsubs = length(unique(data$id)),
+HDInterval::hdi(get_correlation(rw_logs_fit_ses1,rw_logs_fit_ses2,"alpha"))
+
+HDInterval::hdi(get_correlation(rw_logs_fit_ses1,rw_logs_fit_ses2,"b1"))
+
+HDInterval::hdi(get_correlation(rw_logs_fit_ses1,rw_logs_fit_ses2,"b2"))
+
+```
+
+### plotting the correlation (figure 4)
+
+```{r correlation plots}
+
+#logs
+
+alpha_logs = get_corplot(rw_logs_fit_ses1,rw_logs_fit_ses2,"alpha",ymin = 0, ymax = 0.3, xmin = 0.55, xmax = 0.85)
+#b0_logs = get_corplot(rw_logs_fit_ses1,rw_logs_fit_ses2,"b0",ymin = -4.25, ymax = -3, xmin = -3, xmax = -2)
+b1_logs = get_corplot(rw_logs_fit_ses1,rw_logs_fit_ses2,"b1",ymin = 0.2, ymax = 1.5, xmin = 2.5, xmax = 3.4)
+b2_logs = get_corplot(rw_logs_fit_ses1,rw_logs_fit_ses2,"b2",ymin = -0.2, ymax = 0, xmin = 0.3, xmax = 0.575)
+
+rw_logs = alpha_logs+b1_logs+b2_logs
+#wb
+alpha_wb = get_corplotreal(fit_wb_bs, "alpha", ymin = -0.075, ymax = 0.275, xmin = 0.56, xmax = 0.91)
+w1_wb = get_corplotreal(fit_wb_bs, "w1", ymin = 0.02, ymax = 0.1, xmin = 0.17, xmax = 0.25)
+w2_wb = get_corplotreal(fit_wb_bs, "w2", ymin = 0.1, ymax = 0.21, xmin = 0.3, xmax = 0.55)
+
+wb = alpha_wb+w1_wb+w2_wb
+#rw
+alpha_rw = get_corplotreal(fit_rw_bs, "alpha", ymin = 0.1, ymax = 0.2, xmin = 0.2, xmax = 0.3)
+w1_rw = get_corplotreal(fit_rw_bs, "w1", ymin = 0.125, ymax = 0.3, xmin = 0.6, xmax = 0.75)
+
+rw = alpha_rw+w1_rw
+
+rw+plot_annotation(tag_levels = list(c("A",'B')))
+wb+plot_annotation(tag_levels = list(c("C",'D',"E")))
+rw_logs+plot_annotation(tag_levels = list(c("F",'G',"H")))
+```
+
+### fitting the kalman model just to see
+
+```{r fitting Kalman model to session 1}
+df= read.csv(here::here("data_TPL_AC.csv")) %>%
+  rename_all(tolower) %>%
+  filter(trial != 0) %>%
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
+  mutate_all(replace_na, 0)
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+
+df = df %>% filter(session == 1)
+
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data1 = list(nsubs = length(unique(data$id)),
             ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
-            pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
+            expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
             percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
-            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
             stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
-            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL)),
-            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL))
-            )
-
-hier = df[[2]]
-df = df[[1]]
-
-mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier_complete.stan"))
-
-fit <- mod$sample(
-      data = data2,
+            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)),
+            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL))
+            )
+
+mod = cmdstan_model(here::here("Stan","myKalmanfilter_v3_nocent.stan"))
+
+kalman_fit_sess1 <- mod$sample(
+      data = data1,
       chains = 4,
@@
 
-hier_parameters = c("mu_b0","mu_b1","mu_b2","sd_b0","sd_b1","sd_b2","mu_b0_b","mu_b1_b","mu_b2_b","sd_b0_b","sd_b1_b","sd_b2_b","kappa_alpha","mu_alpha","sd_percept_precision")
-
-sub_parameters = c("b0","b1","b2","b0_b","b1_b","b2_b","alpha","percept_precision")
-
-list(hier = data.frame(fit$summary(hier_parameters),
-                                  reals = hier %>% dplyr::select(all_of(hier_parameters)) %>% pivot_longer(everything()) %>% rename(reals = value),
-                                  div = sum(fit$diagnostic_summary()$num_divergent),index = index),
-                sub = data.frame(fit$summary(sub_parameters) %>% arrange(variable),
-                                 reals = df %>% filter(trial == 1) %>% mutate(ids = 1:nrow(.)) %>% dplyr::select(all_of(sub_parameters),ids) %>% 
-                                 pivot_longer(cols = -ids) %>% rename(reals =value) %>% mutate(names = paste0(name,"[",ids,"]")) %>% arrange(names) %>% select(names,reals),
-                                 div = sum(fit$diagnostic_summary()$num_divergent),index = index))
-
-#sum = fit$summary()
-
-```
+ppu_hier(fit = kalman_fit_sess1,
+         parameters = c("sigmaEta","sigmaPsi","sigmaEpsilon","precision_percept"),
+         reals = NA)
+
+# 
+# ppu_sub(fit = fit,
+#         parameter = "precision_percept",
+#         reals = df,
+#         lims = -1,
+#         lime = 10,
+#         nsubs = NA
+#         )
+
+get_diag(kalman_fit_sess1, "sigmaEta")
+get_diag(kalman_fit_sess1, "sigmaPsi")
+get_diag(kalman_fit_sess1, "sigmaEpsilon")
+
+sum = kalman_fit_sess1$summary()
+
+ass = sum %>% filter(str_detect(variable, "perceptmuu"))
+ass = ass[(161*2-1):(161*3-1),]
+
+exp = sum %>% filter(str_detect(variable, "exp_muu"))
+exp = exp[(161*2-1):(161*3-1),]
+
+ass$exp = exp$mean
+
+ass %>% ggplot(aes(x=exp, y = mean))+geom_point()
+
+```
+
+```{r fitting Kalman model to session 2}
+df= read.csv(here::here("data_TPL_AC.csv")) %>%
+  rename_all(tolower) %>%
+  filter(trial != 0) %>%
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
+  mutate_all(replace_na, 0)
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+
+df = df %>% filter(session == 2)
+
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data1 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
+            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
+            expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
+            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
+            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)),
+            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL))
+            )
+
+mod = cmdstan_model(here::here("Stan","myKalmanfilter_v3_nocent.stan"))
+
+kalman_fit_sess2 <- mod$sample(
+      data = data1,
+      chains = 4,
+      parallel_chains = 4,
+      refresh = 100,
+      adapt_delta = 0.90,
+      max_treedepth = 12
+    )
+
+ppu_hier(fit = kalman_fit_sess2,
+         parameters = c("sigmaEta","sigmaPsi","sigmaEpsilon","precision_percept"),
+         reals = NA)
+
+```

### 2023-05-29 equations.Rmd
updates
cleaning

@@
 output:
+  pdf_document: default
+  html_document: default
   word_document: default
-  html_document: default
 ---
@@
 For the derivation of equation 15 and 16 readers are refereed to the supplementary material.
+
+#supplementary
+
+showing equation (15 and 16)
+Starting of with the mean of the precept
+
+$$
+\begin{equation}
+\mu_{\psi_t} = \frac{\sigma_{s}^2}{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_{E_t}^2}*\mu_{E_{t-1}}+\frac{\sigma_{\psi}^2+\sigma_{E_t}^2}{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_{E_t}^2}*S_t
+\end{equation}
+$$
+using (13) we need to show the following
+
+$$
+\begin{equation}
+(1-\gamma) = \frac{\sigma_{\psi}^2+\sigma_{E_t}^2}{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_{E_t}^2}
+\end{equation}
+$$
+Now uterlising the fact that if $x = \frac{a}{b}$ then $1-x = \frac{(b-a)}{b}$
+
+$$
+\begin{equation}
+(1-\gamma) = \frac{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_{E_t}^2-\sigma_{s}^2}{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_{E_t}^2}
+\end{equation}
+$$
+which gives exactly
+
+$$
+\begin{equation}
+(1-\gamma) = \frac{\sigma_{\psi}^2+\sigma_{E_t}^2}{\sigma_{s}^2+\sigma_{\psi}^2+\sigma_{E_t}^2}
+\end{equation}
+$$

### 2023-05-29 scripts/model recovery.R

@@ -151,7 +151,7 @@ model_fitter_kalmandata = function(parameters_kalman){
   
   
   rw_model = here::here("Stan","myRW_real.stan")
-  wb_model = here::here("Stan","hier_weighted_bayes.stan")
+  wb_model = here::here("Stan","hier_weighted_bayes2.stan")
   logs = here::here("Stan","rw_vs_rw_hier_complete.stan")
   
   
@@ -169,7 +169,7 @@ model_fitter_kalmandata = function(parameters_kalman){
   
   loo_kalman_rw = get_loo(rw_model, data1_kalman_rw)
   loo_kalman_wb = get_loo(wb_model, data1_kalman_wb)
-  loo_kalman_kalman = get_loo(kalman_model, data1_kalman)
+  loo_kalman_kalman = get_loo(logs, data1_kalman)
 
   id = rnorm(1,0,1)
   
@@ -200,7 +200,7 @@ get_loo = function(file, data1){
     seed = 123, 
     chains = 4, 
     parallel_chains = 4,
-    refresh = 500
+    refresh = 100
   )
   
   loglik = as_draws_df(fit$draws(variables = "log_lik")) %>% drop_na()

### 2023-05-29 scripts/visualize_parameters.R

@@ -315,6 +315,10 @@ plot_parameterrecovery = function(pp, div, subs){
     hier_pp <- do.call(rbind, lapply(pp, "[[", 1)) %>% filter(div < 1)%>% drop_na()
     sub_pp <- do.call(rbind, lapply(pp, "[[", 2)) %>% filter(div < 1)%>% drop_na()
   }
+  if(length(unique(hier_pp$variable)) == 15){
+    hier_pp <- hier_pp[!grepl("_b$", hier_pp$variable), ]
+    
+  }
   
   hier = hier_pp %>% mutate(divergences = ifelse(div > 0,"yes","no")) %>% 
     ggplot(aes(x = mean, y = reals.reals))+
@@ -324,8 +328,8 @@ plot_parameterrecovery = function(pp, div, subs){
     theme_classic()+
     geom_abline(slope = 1, intercept = 0)+
     scale_color_manual("divergence",values = c("black","red"))+
-    scale_y_continuous("simulated value",breaks = scales::pretty_breaks(n = 4))+
-    scale_x_continuous("Recovered value", breaks = scales::pretty_breaks(n = 4))
+    scale_y_continuous("simulated value",breaks = scales::pretty_breaks(n = 2))+
+    scale_x_continuous("Recovered value", breaks = scales::pretty_breaks(n = 2))+theme(text = element_text(size = 20))
   
 
   # Generate the regular expression pattern dynamically
@@ -344,16 +348,16 @@ plot_parameterrecovery = function(pp, div, subs){
     theme_classic()+
     geom_abline(slope = 1, intercept = 0)+
     scale_color_manual("divergence",values = c("black","red"))+
-    scale_y_continuous("simulated value",breaks = scales::pretty_breaks(n = 4))+
-    scale_x_continuous("Recovered value", breaks = scales::pretty_breaks(n = 4))
+    scale_y_continuous("simulated value",breaks = scales::pretty_breaks(n = 2))+
+    scale_x_continuous("Recovered value", breaks = scales::pretty_breaks(n = 2))+theme(text = element_text(size = 20))
   
   
   
   div = hier_pp %>% group_by(index) %>%
     slice(1) %>%
     ungroup() %>% ggplot(aes(x = div))+geom_histogram()+theme_classic()+
-    scale_y_continuous(breaks = scales::pretty_breaks(n = 4))+
[…]

### 2023-05-29 Manuscript.Rmd
updates

--- 2023-05-23 Manuscript.Rmd
@@
 
+### loading packages
 ```{r setup, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
-pacman::p_load(tidyverse, osfr, lmerTest, MuMIn, DHARMa, here, cmdstanr, tidybayes, bayesplot, posterior,future,furrr, patchwork, R.utils, brms, extraDistr)
+pacman::p_load(tidyverse, osfr, lmerTest, MuMIn, DHARMa, here, cmdstanr, tidybayes, bayesplot, posterior,future,furrr, patchwork, R.utils, brms, extraDistr,cowplot,HDInterval)
 
@@
 
-## R Markdown
-
-```{r parameters visualization}
+### parameter visualization for the four models (figure 1 & 2)
+```{r parameter visualization, fig.height=10, fig.width=12}
 dd = get_experiment()
@@
 
+RW_logistic = RW_logistic_vis(dd)
+
 layout = (c(
-  area(1, 1),
-  area(1, 2),
-  area(2, 1),
-  area(2, 2)
+  area(1, 1, 1,1),
+  area(1, 2, 1,2)
 
 ))
+plot(layout)
 
-plot_spacer()+kalmanplot+rwplot+wbplot+plot_layout(design = layout)
+p1 = RW_logistic[[1]]+rwplot[[1]]+scale_y_continuous(" ")+plot_layout(design = layout)+plot_annotation(tag_levels = list(c('B', 'C')))
+p2 = wbplot[[1]]+kalmanplot[[1]]+scale_y_continuous(" ")+plot_layout(design = layout)+plot_annotation(tag_levels = list(c("D","E")))
+p3 = RW_logistic[[2]]+rwplot[[2]]+scale_y_continuous(" ")+plot_layout(design = layout)+plot_annotation(tag_levels = list(c("A","B")))
+p4  = wbplot[[2]]+kalmanplot[[2]]+scale_y_continuous(" ")+plot_layout(design = layout)+plot_annotation(tag_levels = list(c("C","D")))
+
+p1
+p2
+p3
+p4
 
@@
 
+### parameter recovery for the four models
 ```{r parameter recovery for RW}
@@
 
-```{r}
-#plot parameterrecovery
-hier_pp <- do.call(rbind, lapply(rw_pp, "[[", 1))
-hier_pp %>% mutate(divergences = ifelse(div > 0,1,0)) %>% 
-  ggplot(aes(x = mean, y = reals.reals))+
-  geom_point(aes(col = as.factor(divergences)))+
-  facet_wrap(~variable, scales = "free")+
-  theme_classic()+
-  geom_abline(slope = 1, intercept = 0)+
-  scale_color_manual("divergence?",values = c("black","red"))
+```{r parameter recovery for logistic}
+mu_alpha = seq(0.1,0.5, length.out = 5)
+kappa_alpha = seq(10,100, length.out = 2)
 
-sub_pp <- do.call(rbind, lapply(rw_pp, "[[", 2))
-sub_pp %>% mutate(divergences = ifelse(div > 0,1,0)) %>% 
-  ggplot(aes(x = mean, y = reals.reals))+
-  geom_point(aes(col = as.factor(divergences)))+
-  facet_wrap(~variable, scales = "free")+
-  theme_classic()+
-  geom_abline(slope = 1, intercept = 0)+
-  scale_color_manual("divergence?",values = c("black","red"))
+mu_b0 = -1.5
+sd_b0 = 0.5
+
+mu_b1 = seq(0.1,2,length.out = 5)
+sd_b1 = seq(0.1,2,length.out = 3)
+
+mu_b2 = seq(0.1,2,length.out = 5)
+sd_b2 = seq(0.1,2,length.out = 3)
+
+mu_b0_b = -4
+sd_b0_b = 0.5
+
+mu_b1_b = 7
+sd_b1_b = 0.5
+
+mu_b2_b = 0.7
+sd_b2_b = 0.5
+
+sd_percept_precision = 0.8
+
+nsubs = 10
+
+parameters = expand.grid(mu_alpha = mu_alpha,
+                         kappa_alpha = kappa_alpha,
+                         mu_b0 = mu_b0,
+                         sd_b0 = sd_b0,
+                         mu_b1 = mu_b1,
+                         sd_b1 = sd_b1,
+                         mu_b2 = mu_b2,
+                         sd_b2 = sd_b2,
+                         mu_b0_b = mu_b0_b,
+                         sd_b0_b = sd_b0_b,
+                         mu_b1_b = mu_b1_b,
+                         sd_b1_b = sd_b1_b,
+                         mu_b2_b = mu_b2_b,
+                         sd_b2_b = sd_b2_b,
+                         sd_percept_precision = sd_percept_precision,
+                         nsubs = nsubs)
+
+parameters$id = 1:nrow(parameters)
+
+data_list <- split(parameters, parameters$id)
+
+plan(multisession, workers = 5)
+
+rw_pp = furrr::future_map(data_list, ~parameter_recovery_logistic_rw(.x), .progress = TRUE, .options = furrr_options(seed = 123))
 
@@
 
+#plotting parameter recovery (figure 3)
+```{r}
+files = paste0(here::here("workspace","parameterrecovery"),"/",list.files(here::here("workspace","parameterrecovery")))
+
+#plot parameterrecovery
+load(files[[1]])
+q = lapply(here("scripts", scripts), source)
+kalmanplot = plot_parameterrecovery(kalman_pp, div = T, subs = 5)
+load(files[[2]])
+q = lapply(here("scripts", scripts), source)
+logisticplot = plot_parameterrecovery(rw_pp_logs, div = F, subs = 5)
+load(files[[3]])
+q = lapply(here("scripts", scripts), source)
+rwplot = plot_parameterrecovery(rw_pp, div = T, subs = 5)
+load(files[[4]])
+q = lapply(here("scripts", scripts), source)
+wbplot = plot_parameterrecovery(wb_pp, div = T, subs = 5)
+
+layout = (c(
+  area(1, 1, 2,3),
+  area(3, 1,5,3),
+  area(6, 1,6,3)
+
+))
+
+((rwplot[[1]]+wbplot[[1]])/(kalmanplot[[1]]+logisticplot[[1]]))+
+  plot_annotation(tag_levels = 'A')+
+  plot_layout(guides = 'collect')
+
+((rwplot[[2]]+wbplot[[2]])/(kalmanplot[[2]]+logisticplot[[2]]))+
+  plot_annotation(tag_levels = 'A')+
+  plot_layout(guides = 'collect')
+
+```
+
+### model recovery for the three computation models
 ```{r model recovery}
 ########################################### Resorla wagner parameters:
-mu_alpha = seq(0.1,0.3,length.out = 10)
+mu_alpha = rep(0.3,100)
 kappa_alpha = 50
-mu_w1 = seq(0.1,0.3,length.out = 10)
+mu_w1 = 0.3
 kappa_w1 = 50
@@
 
-######################################### Kalman
+######################################### logistic RW
 
-mu_sigmaEta = rep(0.1,100)
-mu_sigmaPsi = 0.1
-mu_sigmaEpsilon = 2
-sd_sigmaEta = 0.1
-sd_sigmaPsi = 0.1
-sd_sigmaEpsilon = 0.1
+mu_alpha = rep(0.3,100)
+kappa_alpha = 50
+
+mu_b0 = -1.5
+sd_b0 = 0.5
+
+mu_b1 = 2
+sd_b1 = 1
+
+mu_b2 = 1
+sd_b2 = 1
+
+mu_b0_b = -3
+sd_b0_b = 0.5
+
+mu_b1_b = 5
+sd_b1_b = 0.5
+
+mu_b2_b = 0.7
+sd_b2_b = 0.5
+
+sd_percept_precision = 0.5
+
 nsubs = 10
-parameters = expand.grid(mu_sigmaEta = mu_sigmaEta,
-                         mu_sigmaPsi = mu_sigmaPsi,
-                         mu_sigmaEpsilon = mu_sigmaEpsilon,
-                         sd_sigmaEta = sd_sigmaEta,
-                         sd_sigmaPsi = sd_sigmaPsi,
-                         sd_sigmaEpsilon = sd_sigmaEpsilon,
+
+parameters = expand.grid(mu_alpha = mu_alpha,
+                         kappa_alpha = kappa_alpha,
+                         mu_b0 = mu_b0,
+                         sd_b0 = sd_b0,
+                         mu_b1 = mu_b1,
+                         sd_b1 = sd_b1,
+                         mu_b2 = mu_b2,
+                         sd_b2 = sd_b2,
+                         mu_b0_b = mu_b0_b,
+                         sd_b0_b = sd_b0_b,
+                         mu_b1_b = mu_b1_b,
+                         sd_b1_b = sd_b1_b,
+                         mu_b2_b = mu_b2_b,
+                         sd_b2_b = sd_b2_b,
+                         sd_percept_precision = sd_percept_precision,
                          nsubs = nsubs)
+
 parameters$id = 1:nrow(parameters)
-data_list_kalman <- split(parameters, parameters$id)
+
+data_list_logs <- split(parameters, parameters$id)
 
@@
 
-data_list = data_list_rw[1:5]
+data_list = data_list_rw
 
-plan(multisession, workers = 5)
+plan(multisession, workers = 10)
 
@@
 
-data_list = data_list_wb[1:100]
+data_list = data_list_wb
 
-plan(multisession, workers = 10)
+plan(multisession, workers = availableCores()-1)
 
@@
 
-data_list = data_list_kalman[1]
+data_list = data_list_logs[1:50]
 
-plan(multisession, workers = 5)
+plan(multisession, workers = 10)
 
@@
 
+### table 1
+```{r model recovery table}
+
+files = paste0(here::here("workspace","model recovery"),"/",list.files(here::here("workspace","model recovery")))
+
+#plot parameterrecovery
+load(files[[1]])
+
+get_value = function(loo){
+  get_from_means <- do.call(rbind, lapply(loo, "[[", 1))
+
+  get_from_means$id = as.factor(get_from_means$id)
+# Group by ID and find the model with the minimum value
+  min_values <- get_from_means %>%
+  group_by(id) %>%
+  filter(means == min(means))
+
+# Count the occurrences of each model with the minimum value per run
+  model_counts <- min_values %>%
+    group_by(names) %>%
+    summarize(Count = n())
+
+  get_from_loo <- do.call(rbind, lapply(loo, "[[", 2))
+
+  get_from_loo = get_from_loo %>% filter(elpd_diff == 0) %>% mutate(model = row.names(.)) %>% mutate(realmodel = sub("^[0-9]+\\.(.*)", "\\1", model)) %>% group_by(realmodel) %>% summarize(Count = n())
+
+  return(list(fromloo = get_from_loo, frommean = model_counts))
+}
+
+kalmandata = get_value(kalman_loo)
+rwdata = get_value(rw_loo)
+wbdata = get_value(wb_loo)
+
+```
+
+### fitting the models to session 1's data
+
 ```{r fitting RW model to session 1}
-df= read.csv(here::here("data_TPL_AC.csv")) %>% 
+df= read.csv(here::here("data","data_TPL_AC.csv")) %>% 
   rename_all(tolower) %>% 
@@
 
-rw_fit_sess1$diagnostic_summary()
-```
-
-```{r fitting RW model to session 2}
-df= read.csv(here::here("data_TPL_AC.csv")) %>% 
-  rename_all(tolower) %>% 
-  filter(trial != 0) %>% 
-  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% 
-  mutate_all(replace_na, 0)
-
-df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
-
-#ratings
-df %>% filter(session == 2) %>% ggplot(aes(x = percept, fill = as.factor(stim))) + geom_histogram()
-#cue-contingency
-df %>% filter(session == 1, id == 1) %>% ggplot(aes(x = trial, y = u)) + geom_point()+theme_classic()
-
-df = df %>% filter(session == 2)
-
-#fitting hierachically
-data = df %>% mutate(percept = percept/100)
-
-data = data %>% mutate(across(percept, ~case_when(
-    . < 0.001 ~ 0.001,
-    . > 0.999 ~ 0.999,
-    TRUE ~ .
-  )))
-
-data1 = list(nsubs = length(unique(data$id)),
-            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
-            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
-            expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
-            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
-            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
-            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)))
-
-mod = cmdstan_model(here::here("Stan","myRW_real.stan"))
-
-rw_fit_sess2 <- mod$sample(
-      data = data1,
-      chains = 4, 
-      parallel_chains = 4,
-      refresh = 100,
-      adapt_delta = 0.90,
-      max_treedepth = 12
-    )
-
-rw_fit_sess2$diagnostic_summary()
+ppu_hier(fit = rw_fit_sess1,
+         parameters = c("alpha","w1","precision_percept"),
+         reals = NA)
 
@@
 
-```{r fitting Kalman model to session 1}
-df= read.csv(here::here("data_TPL_AC.csv")) %>%
-  rename_all(tolower) %>%
-  filter(trial != 0) %>%
-  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
-  mutate_all(replace_na, 0)
-
-df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
-
-df = df %>% filter(session == 1)
-
-#fitting hierachically
-data = df %>% mutate(percept = percept/100)
-
-data = data %>% mutate(across(percept, ~case_when(
-    . < 0.001 ~ 0.001,
-    . > 0.999 ~ 0.999,
-    TRUE ~ .
-  )))
-
-data1 = list(nsubs = length(unique(data$id)),
-            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
-            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
-            expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
-            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
-            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
-            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)),
-            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL))
-            )
-
-mod = cmdstan_model(here::here("Stan","no generated quantities","myKalmanfilter_v2_nogen_nocent.stan"))
-
-kalman_fit_sess1 <- mod$sample(
-      data = data1,
-      chains = 4,
-      parallel_chains = 4,
-      refresh = 100,
-      adapt_delta = 0.90,
-      max_treedepth = 12
-    )
-
-diag_sigmaEta = get_diag(fit = kalman_fit_sess1,
-         parameter = "sigmaEta")
-
-diag_sigmaPsi = get_diag(fit = kalman_fit_sess1,
-         parameter = "sigmaPsi")
-
-diag_sigmaEpsilon = get_diag(fit = kalman_fit_sess1,
-         parameter = "sigmaEpsilon")
-
-diag_sigmabeta = get_diag(fit = kalman_fit_sess1,
-         parameter = "beta")
-
-diag_precision_percept = get_diag(fit = kalman_fit_sess1,
-         parameter = "precision_percept")
-```
-
-```{r fitting Kalman model to session 2}
-df= read.csv(here::here("data_TPL_AC.csv")) %>%
-  rename_all(tolower) %>%
-  filter(trial != 0) %>%
-  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
-  mutate_all(replace_na, 0)
-
-df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
-
-df = df %>% filter(session == 2)
-
-#fitting hierachically
-data = df %>% mutate(percept = percept/100)
-
-data = data %>% mutate(across(percept, ~case_when(
-    . < 0.001 ~ 0.001,
-    . > 0.999 ~ 0.999,
-    TRUE ~ .
-  )))
-
-data1 = list(nsubs = length(unique(data$id)),
-            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
-            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
-            expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
-            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
-            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
-            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)),
-            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL))
-            )
-
-mod = cmdstan_model(here::here("Stan","no generated quantities","myKalmanfilter_v2_nogen_nocent.stan"))
-
-kalman_fit_sess2 <- mod$sample(
-      data = data1,
-      chains = 4,
-      parallel_chains = 4,
-      refresh = 100,
-      adapt_delta = 0.90,
-      max_treedepth = 12
-    )
-```
-
 ```{r fitting WB model to session 1}
-df= read.csv(here::here("data_TPL_AC.csv")) %>% 
+df= read.csv(here::here("data","data_TPL_AC.csv")) %>% 
   rename_all(tolower) %>% 
@@
     )
+
+wb_fit_sess1$diagnostic_summary()
+
+alpha = get_diag(wb_fit_sess1, "alpha")
+w1 = get_diag(wb_fit_sess1, "w1")
+w2 = get_diag(wb_fit_sess1, "w2")
+pp = get_diag(wb_fit_sess1, "percept_precision")
+beta = get_diag(wb_fit_sess1, "beta")
+
 ```
+
+```{r, fitting to real data tester hierachical logs RW sessions1}
+
+df= read.csv(here::here("data","data_TPL_AC.csv")) %>%
+  rename_all(tolower) %>%
+  filter(trial != 0) %>%
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
+  mutate_all(replace_na, 0)
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
+
+df = df %>% filter(session == 1)
+
+#source(here::here("stan_functions.R"))
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data2 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
+            pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
+            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
+            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
+            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL)),
+            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL))
+            )
+
+mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier_complete.stan"))
+
+rw_logs_fit_ses1 <- mod$sample(
+      data = data2,
+      chains = 4,
+      parallel_chains = 4,
+      refresh = 100,
+      adapt_delta = 0.90,
+      max_treedepth = 12
+    )
+
+sum1 = rw_logs_fit_ses1$summary()
+```
+
+### Model comparison on sessions 1 (table 2)
+```{r, model comparison}
+#rw = rw_fit_sess1$loo()
+#wb = wb_fit_sess1$loo()
+#rw_logs = rw_logs_fit_ses1$loo()
+
+rw = as_draws_df(rw_fit_sess1$draws(variables = "log_lik"))
+wb = as_draws_df(wb_fit_sess1$draws(variables = "log_lik"))
+rw_logs = as_draws_df(rw_logs_fit_ses1$draws(variables = "log_lik"))
+
+rows_with_na <- which(apply(is.na(wb), 1, any))
+wb = wb[-rows_with_na,]
+rw = rw[-rows_with_na,]
+rw_logs = rw_logs[-rows_with_na, ]
+
+wb = loo::loo(as.matrix(wb))
+rw = loo::loo(as.matrix(rw))
+rw_logs = loo::loo(as.matrix(rw_logs))
+
+loo_compare(rw,wb,rw_logs)
+loo_model_weights(list(rw,wb,rw_logs))
+```
+
+### fitting the models to session 2's data
+
+```{r fitting RW model to session 2}
+df= read.csv(here::here("data","data_TPL_AC.csv")) %>% 
+  rename_all(tolower) %>% 
+  filter(trial != 0) %>% 
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>% 
+  mutate_all(replace_na, 0)
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+
+df = df %>% filter(session == 2)
+
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data1 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
+            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
+            expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
+            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
+            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)))
+
+mod = cmdstan_model(here::here("Stan","myRW_real.stan"))
+
+rw_fit_sess2 <- mod$sample(
+      data = data1,
+      chains = 4, 
+      parallel_chains = 4,
+      refresh = 100,
+      adapt_delta = 0.90,
+      max_treedepth = 12
+    )
+
+ppu_hier(fit = rw_fit_sess2,
+         parameters = c("alpha","w1","precision_percept"),
+         reals = NA)
+
+```
+
+### fitting the models to session 2's data
 
@@
 
-df= read.csv(here::here("data_TPL_AC.csv")) %>% 
+df= read.csv(here::here("data","data_TPL_AC.csv")) %>% 
   rename_all(tolower) %>% 
@@
 
-```
+wb_fit_sess2$diagnostic_summary()
 
-```{r hierachical session correlation (RW)}
-
-df= read.csv(here::here("data_TPL_AC.csv")) %>%
-  rename_all(tolower) %>%
-  filter(trial != 0) %>%
-  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
-  mutate_all(replace_na, 0) %>% mutate(id = as.factor(id), trial = as.factor(trial), session = as.factor(session))
-
-df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
-df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
-
-#ratings
-df %>% filter(session == 2) %>% ggplot(aes(x = percept, fill = as.factor(stim))) + geom_histogram()
-#cue-contingency
-df %>% filter(session == 1, id == 1) %>% ggplot(aes(x = trial, y = u)) + geom_point()+theme_classic()
-
-#fitting hierachically
-data = df %>% mutate(percept = percept/100)
-
-data = data %>% mutate(across(percept, ~case_when(
-    . < 0.001 ~ 0.001,
-    . > 0.999 ~ 0.999,
-    TRUE ~ .
-  )))
-
-data1 = list(nsubs = length(unique(data$id)),
-            ntrials = nrow(data %>% filter(session == 1) %>% filter(id %in% unique(id)[1])),
-            sesions = length(unique(data$session)),
-            percept = get_3darray(data,variable = "percept"),
-            expectPain = get_3darray(data,variable = "pred"),
-            percept_bin = get_3darray(data,variable = "percept_bin"),
-            stim = get_3darray(data,variable = "stim"),
-            cues = get_3darray(data,variable = "cue"),
-            u = get_3darray(data,variable = "u")
-            )
-
-mod = cmdstan_model(here::here("Stan","fitting both sessions","myRW_correlation.stan"))
-
-fit <- mod$sample(
-  data = data1,
-  chains = 4,
-  parallel_chains = 4,
-  refresh = 100,
-  adapt_delta = 0.90,
-  max_treedepth = 12
-)
-
-sum = fit$summary(variables = c("mu_alpha","mu_w1","sd_beta","sd_precision_percept", "kappa_alpha","kappa_w1","alpha","w1","beta","precision_percept"))
-
-variabless = c("mu_alpha[1]","mu_w1[1]","sd_beta[1]","sd_precision_percept[1]","mu_alpha[2]","mu_w1[2]","sd_beta[2]","sd_precision_percept[2]")
-
-pairs = mcmc_pairs(fit$draws(variables = variabless), np = nuts_params(fit), pars = variabless,
-                   off_diag_args = list(size = 0.75))
-```
-
-```{r hierachical session correlation (WB)}
-
-df= read.csv(here::here("data_TPL_AC.csv")) %>%
-  rename_all(tolower) %>%
-  filter(trial != 0) %>%
-  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
-  mutate_all(replace_na, 0) %>% mutate(id = as.factor(id), trial = as.factor(trial), session = as.factor(session))
-
-df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
-df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
-
-#fitting hierachically
-data = df %>% mutate(percept = percept/100)
-
-data = data %>% mutate(across(c(percept,stim), ~case_when(
-    . < 0.001 ~ 0.001,
-    . > 0.999 ~ 0.999,
-    TRUE ~ .
-  )))
-
-data1 = list(nsubs = length(unique(data$id)),
-            ntrials = nrow(data %>% filter(session == 1) %>% filter(id %in% unique(id)[1])),
-            sesions = length(unique(data$session)),
-            percept = get_3darray(data,variable = "percept"),
-            pred = get_3darray(data,variable = "pred"),
-            percept_bin = get_3darray(data,variable = "percept_bin"),
-            stim = get_3darray(data,variable = "stim"),
-            cue = get_3darray(data,variable = "cue")
-            )
-
-mod = cmdstan_model(here::here("Stan","fitting both sessions","hier_weighted_bayes_correlation.stan"))
-
-fit <- mod$sample(
-  data = data1,
-  chains = 4,
-  parallel_chains = 4,
-  refresh = 100,
-  adapt_delta = 0.90,
-  max_treedepth = 12
-)
+alpha = get_diag(wb_fit_sess1, "alpha")
+w1 = get_diag(wb_fit_sess1, "w1")
+w2 = get_diag(wb_fit_sess1, "w2")
+pp = get_diag(wb_fit_sess1, "percept_precision")
+beta = get_diag(wb_fit_sess1, "beta")
 
@@
 
-```{r fitting to real data tester hierachical RW session 1}
+### fitting the models to session 2's data
 
-df= read.csv(here::here("data_TPL_AC.csv")) %>%
-  rename_all(tolower) %>%
-  filter(trial != 0) %>%
-  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
-  mutate_all(replace_na, 0)
+```{r, fitting to real data tester hierachical logs RW sessions2}
 
-df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
-df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
-
-df = df %>% filter(session == 1)
-
-#source(here::here("stan_functions.R"))
-#fitting hierachically
-data = df %>% mutate(percept = percept/100)
-
-data = data %>% mutate(across(percept, ~case_when(
-    . < 0.001 ~ 0.001,
-    . > 0.999 ~ 0.999,
-    TRUE ~ .
-  )))
-
-data1 = list(nsubs = length(unique(data$id)),
-            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
-            pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
-            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL))
-            )
-
-mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier.stan"))
-
-rw_fit_ses1 <- mod$sample(
-      data = data1,
-      chains = 4,
-      parallel_chains = 4,
-      refresh = 100,
-      adapt_delta = 0.90,
-      max_treedepth = 12
-    )
-
-sum = rw_fit_ses1$summary(variables = c("alpha_1"))
-
-```
-
-```{r fitting to real data tester hierachical RW seesion2}
-
-df= read.csv(here::here("data_TPL_AC.csv")) %>%
+df= read.csv(here::here("data","data_TPL_AC.csv")) %>%
   rename_all(tolower) %>%
@@
             pred = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
-            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL))
+            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
+            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
+            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
+            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL)),
+            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL))
             )
 
-mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier.stan"))
+mod = cmdstan_model(here::here("Stan","rw_vs_rw_hier_complete.stan"))
 
-rw_fit_ses2 <- mod$sample(
+rw_logs_fit_ses2 <- mod$sample(
       data = data2,
@@
 
-sums2 = rw_fit_ses2$summary(variables = c("alpha_1"))
+```
+
+### Model comparison on sessions 2 (table 2)
+
+```{r, model comparison}
+#rw = rw_fit_sess1$loo()
+#wb = wb_fit_sess1$loo()
+#rw_logs = rw_logs_fit_ses1$loo()
+
+rw = as_draws_df(rw_fit_sess2$draws(variables = "log_lik"))
+wb = as_draws_df(wb_fit_sess2$draws(variables = "log_lik"))
+rw_logs = as_draws_df(rw_logs_fit_ses2$draws(variables = "log_lik"))
+
+rows_with_na <- which(apply(is.na(wb), 1, any))
+wb = wb[-rows_with_na,]
+rw = rw[-rows_with_na,]
+rw_logs = rw_logs[-rows_with_na, ]
+
+wb = loo::loo(as.matrix(wb))
+rw = loo::loo(as.matrix(rw))
+rw_logs = loo::loo(as.matrix(rw_logs))
+
+loo_compare(rw_logs,rw,wb)
+
+loo_model_weights(list(rw_logs,rw,wb))
+```
+
+### Fitting the models to both sessions
+
+```{r hierachical session correlation (RW)}
+df= read.csv(here::here("data","data_TPL_AC.csv")) %>%
+  rename_all(tolower) %>%
+  filter(trial != 0) %>%
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
+  mutate_all(replace_na, 0) %>% mutate(id = as.factor(id), trial = as.factor(trial), session = as.factor(session))
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data1 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(session == 1) %>% filter(id %in% unique(id)[1])),
+            sesions = length(unique(data$session)),
+            percept = get_3darray(data,variable = "percept"),
+            expectPain = get_3darray(data,variable = "pred"),
+            percept_bin = get_3darray(data,variable = "percept_bin"),
+            stim = get_3darray(data,variable = "stim"),
+            cues = get_3darray(data,variable = "cue"),
+            u = get_3darray(data,variable = "u")
+            )
+
+mod = cmdstan_model(here::here("Stan","fitting both sessions","myRW_real_both_sess.stan"))
+
+fit_rw_bs <- mod$sample(
+  data = data1,
+  chains = 4,
+  parallel_chains = 4,
+  refresh = 100,
+  adapt_delta = 0.90,
+  max_treedepth = 12
+)
+
+alpha_wb = get_corplotreal(fit_rw_bs, "alpha", ymin = 0.1, ymax = 0.2, xmin = 0.2, xmax = 0.3)
+w1_wb = get_corplotreal(fit_rw_bs, "w1", ymin = 0.125, ymax = 0.3, xmin = 0.6, xmax = 0.75)
+
+HDInterval::hdi(as_draws_df(fit_rw_bs$draws(variables = "correlation_alpha")) %>% select(starts_with("correlation")))
+
+HDInterval::hdi(as_draws_df(fit_rw_bs$draws(variables = "correlation_w1")) %>% select(starts_with("correlation")))
 
 ```
+
+```{r hierachical session correlation (WB)}
+
+df= read.csv(here::here("data","data_TPL_AC.csv")) %>%
+  rename_all(tolower) %>%
+  filter(trial != 0) %>%
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
+  mutate_all(replace_na, 0) %>% mutate(id = as.factor(id), trial = as.factor(trial), session = as.factor(session))
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(c(percept,stim), ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data1 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(session == 1) %>% filter(id %in% unique(id)[1])),
+            sesions = length(unique(data$session)),
+            percept = get_3darray(data,variable = "percept"),
+            pred = get_3darray(data,variable = "pred"),
+            percept_bin = get_3darray(data,variable = "percept_bin"),
+            stim = get_3darray(data,variable = "stim"),
+            cue = get_3darray(data,variable = "cue")
+            )
+
+mod = cmdstan_model(here::here("Stan","fitting both sessions","hier_weighted_bayes_correlation.stan"))
+
+fit_wb_bs <- mod$sample(
+  data = data1,
+  chains = 4,
+  parallel_chains = 4,
+  refresh = 50,
+  adapt_delta = 0.90,
+  max_treedepth = 12
+)
+
+fit_wb_bs$diagnostic_summary()
+
+correlation = as_draws_df(fit_wb_bs$draws(variables = "correlation_alpha"))
+hist(correlation$correlation_alpha)
+correlation = as_draws_df(fit_wb_bs$draws(variables = "correlation_w1"))
+hist(correlation$correlation_w1)
+correlation = as_draws_df(fit_wb_bs$draws(variables = "correlation_w2"))
+hist(correlation$correlation_w2)
+
+alphaplot1 = get_corplot(wb_fit_sess1, wb_fit_sess2, "alpha")
+
+alpha_wb = get_corplotreal(fit_wb_bs, "alpha", ymin = -0.075, ymax = 0.325, xmin = 0.65, xmax = 1)
+w1_wb = get_corplotreal(fit_wb_bs, "w1", ymin = 0.02, ymax = 0.12, xmin = 0.19, xmax = 0.27)
+w2_wb = get_corplotreal(fit_wb_bs, "w2", ymin = 0.1, ymax = 0.2, xmin = 0.4, xmax = 0.6)
+
+HDInterval::hdi(as_draws_df(fit_wb_bs$draws(variables = "correlation_alpha")) %>% select(starts_with("correlation")))
+
+HDInterval::hdi(as_draws_df(fit_wb_bs$draws(variables = "correlation_w1")) %>% select(starts_with("correlation")))
+
+HDInterval::hdi(as_draws_df(fit_wb_bs$draws(variables = "correlation_w2")) %>% select(starts_with("correlation")))
+
+```
+
+```{r logistic both sessions}
+df= read.csv(here::here("data","data_TPL_AC.csv")) %>%
+  rename_all(tolower) %>%
+  filter(trial != 0) %>%
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
+  mutate_all(replace_na, 0) %>% mutate(id = as.factor(id), trial = as.factor(trial), session = as.factor(session))
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+df$pred = ifelse(df$cue == 1 & df$pred == 1, 1, ifelse(df$cue == 0 & df$pred == 0, 1,0))
+
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data1 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(session == 1) %>% filter(id %in% unique(id)[1])),
+            sesions = length(unique(data$session)),
+            percept = get_3darray(data,variable = "percept"),
+            pred = get_3darray(data,variable = "pred"),
+            percept_bin = get_3darray(data,variable = "percept_bin"),
+            stim = get_3darray(data,variable = "stim"),
+            cues = get_3darray(data,variable = "cue"),
+            u = get_3darray(data,variable = "u")
+            )
+
+mod = cmdstan_model(here::here("Stan","fitting both sessions","rw_vs_rw_hier_complete_both_sessions.stan"))
+
+fit_rw_logs_bs <- mod$sample(
+  data = data1,
+  chains = 4,
+  parallel_chains = 4,
+  refresh = 50,
+  adapt_delta = 0.90,
+  max_treedepth = 12
+)
+
+HDInterval::hdi(get_correlation(rw_logs_fit_ses1,rw_logs_fit_ses2,"alpha"))
+
+HDInterval::hdi(get_correlation(rw_logs_fit_ses1,rw_logs_fit_ses2,"b1"))
+
+HDInterval::hdi(get_correlation(rw_logs_fit_ses1,rw_logs_fit_ses2,"b2"))
+
+```
+
+### plotting the correlation (figure 4)
+
+```{r correlation plots}
+
+#logs
+
+alpha_logs = get_corplot(rw_logs_fit_ses1,rw_logs_fit_ses2,"alpha",ymin = 0, ymax = 0.3, xmin = 0.55, xmax = 0.85)
+#b0_logs = get_corplot(rw_logs_fit_ses1,rw_logs_fit_ses2,"b0",ymin = -4.25, ymax = -3, xmin = -3, xmax = -2)
+b1_logs = get_corplot(rw_logs_fit_ses1,rw_logs_fit_ses2,"b1",ymin = 0.2, ymax = 1.5, xmin = 2.5, xmax = 3.4)
+b2_logs = get_corplot(rw_logs_fit_ses1,rw_logs_fit_ses2,"b2",ymin = -0.2, ymax = 0, xmin = 0.3, xmax = 0.575)
+
+rw_logs = alpha_logs+b1_logs+b2_logs
+#wb
+alpha_wb = get_corplotreal(fit_wb_bs, "alpha", ymin = -0.075, ymax = 0.275, xmin = 0.56, xmax = 0.91)
+w1_wb = get_corplotreal(fit_wb_bs, "w1", ymin = 0.02, ymax = 0.1, xmin = 0.17, xmax = 0.25)
+w2_wb = get_corplotreal(fit_wb_bs, "w2", ymin = 0.1, ymax = 0.21, xmin = 0.3, xmax = 0.55)
+
+wb = alpha_wb+w1_wb+w2_wb
+#rw
+alpha_rw = get_corplotreal(fit_rw_bs, "alpha", ymin = 0.1, ymax = 0.2, xmin = 0.2, xmax = 0.3)
+w1_rw = get_corplotreal(fit_rw_bs, "w1", ymin = 0.125, ymax = 0.3, xmin = 0.6, xmax = 0.75)
+
+rw = alpha_rw+w1_rw
+
+rw+plot_annotation(tag_levels = list(c("A",'B')))
+wb+plot_annotation(tag_levels = list(c("C",'D',"E")))
+rw_logs+plot_annotation(tag_levels = list(c("F",'G',"H")))
+```
+
+### fitting the kalman model just to see
+
+```{r fitting Kalman model to session 1}
+df= read.csv(here::here("data","data_TPL_AC.csv")) %>%
+  rename_all(tolower) %>%
+  filter(trial != 0) %>%
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
+  mutate_all(replace_na, 0)
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+
+df = df %>% filter(session == 1)
+
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data1 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
+            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
+            expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
+            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
+            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)),
+            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL))
+            )
+
+mod = cmdstan_model(here::here("Stan","myKalmanfilter_v3_nocent.stan"))
+
+kalman_fit_sess1 <- mod$sample(
+      data = data1,
+      chains = 4,
+      parallel_chains = 4,
+      refresh = 100,
+      adapt_delta = 0.90,
+      max_treedepth = 12
+    )
+
+ppu_hier(fit = kalman_fit_sess1,
+         parameters = c("sigmaEta","sigmaPsi","sigmaEpsilon","precision_percept"),
+         reals = NA)
+
+# 
+# ppu_sub(fit = fit,
+#         parameter = "precision_percept",
+#         reals = df,
+#         lims = -1,
+#         lime = 10,
+#         nsubs = NA
+#         )
+
+get_diag(kalman_fit_sess1, "sigmaEta")
+get_diag(kalman_fit_sess1, "sigmaPsi")
+get_diag(kalman_fit_sess1, "sigmaEpsilon")
+
+sum = kalman_fit_sess1$summary()
+
+ass = sum %>% filter(str_detect(variable, "perceptmuu"))
+ass = ass[(161*2-1):(161*3-1),]
+
+exp = sum %>% filter(str_detect(variable, "exp_muu"))
+exp = exp[(161*2-1):(161*3-1),]
+
+ass$exp = exp$mean
+
+ass %>% ggplot(aes(x=exp, y = mean))+geom_point()
+
+```
+
+```{r fitting Kalman model to session 2}
+df= read.csv(here::here("data","data_TPL_AC.csv")) %>%
+  rename_all(tolower) %>%
+  filter(trial != 0) %>%
+  rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
+  mutate_all(replace_na, 0)
+
+df$u = ifelse(df$cue == 1 & df$stim == 1, 1, ifelse(df$cue == 0 & df$stim == 0, 1,0))
+
+df = df %>% filter(session == 2)
+
+#fitting hierachically
+data = df %>% mutate(percept = percept/100)
+
+data = data %>% mutate(across(percept, ~case_when(
+    . < 0.001 ~ 0.001,
+    . > 0.999 ~ 0.999,
+    TRUE ~ .
+  )))
+
+data1 = list(nsubs = length(unique(data$id)),
+            ntrials = nrow(data %>% filter(id %in% unique(id)[1])),
+            percept = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept)%>% mutate(trial= NULL)),
+            expectPain = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = pred)%>% mutate(trial= NULL)),
+            percept_bin = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = percept_bin)%>% mutate(trial= NULL)),
+            stim = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = stim)%>% mutate(trial= NULL)),
+            cues = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = cue)%>% mutate(trial= NULL)),
+            u = as.matrix(data %>% pivot_wider(id_cols = trial, names_from = id, values_from = u)%>% mutate(trial= NULL))
+            )
+
+mod = cmdstan_model(here::here("Stan","myKalmanfilter_v3_nocent.stan"))
+
+kalman_fit_sess2 <- mod$sample(
+      data = data1,
+      chains = 4,
+      parallel_chains = 4,
+      refresh = 100,
+      adapt_delta = 0.90,
+      max_treedepth = 12
+    )
+
+ppu_hier(fit = kalman_fit_sess2,
+         parameters = c("sigmaEta","sigmaPsi","sigmaEpsilon","precision_percept"),
+         reals = NA)
+
+```

### 2023-05-31 Manuscript.Rmd
last_cleaning

@@
 q = lapply(here("scripts", scripts), source)
-kalmanplot = plot_parameterrecovery(kalman_pp, div = T, subs = 5)
+kalmanplot = plot_parameterrecovery(kalman_pp, div = T, subs = 5, "Kalman filter")
 load(files[[2]])
 q = lapply(here("scripts", scripts), source)
-logisticplot = plot_parameterrecovery(rw_pp_logs, div = F, subs = 5)
+logisticplot = plot_parameterrecovery(rw_pp_logs, div = F, subs = 5,"Logistic RW")
 load(files[[3]])
 q = lapply(here("scripts", scripts), source)
-rwplot = plot_parameterrecovery(rw_pp, div = T, subs = 5)
+rwplot = plot_parameterrecovery(rw_pp, div = T, subs = 5,"Rescorla Wagner")
 load(files[[4]])
 q = lapply(here("scripts", scripts), source)
-wbplot = plot_parameterrecovery(wb_pp, div = T, subs = 5)
+wbplot = plot_parameterrecovery(wb_pp, div = T, subs = 5,"Weighted bayes")
 
@@
 
+```{r getting temperatures}
+
+# Create a function to assign temperature indicator based on a threshold
+assign_indicator <- function(temperature, threshold) {
+  ifelse(temperature <= threshold, "Low", "High")
+}
+
+# Calculate the threshold for each ID and session
+df$threshold <- ave(df$temperature, df$id, df$session, FUN = median)
+
+# Create the indicator column
+df$temperature_indicator <- mapply(assign_indicator, df$temperature, df$threshold)
+```
+
 ### fitting the models to session 1's data
@@
   rename(id = participant, stim = stimulus, percept = rating, pred = prediction, percept_bin = quality) %>%
-  mutate_all(replace_na, 0)
+  mutate_all(replace_na, 0)git
 

### 2023-05-31 equations.Rmd
last_cleaning

@@
 output:
+  word_document: default
   pdf_document: default
   html_document: default
-  word_document: default
 ---
@@
 $$
-Now uterlising the fact that if $x = \frac{a}{b}$ then $1-x = \frac{(b-a)}{b}$
+Now use the fact that if $x = \frac{a}{b}$ then $1-x = \frac{(b-a)}{b}$
 
@@
 $$
+
+The same logic goes for equation (16)

### 2023-05-31 scripts/visualize_parameters.R

@@ -306,7 +306,7 @@ RW_logistic_vis = function(dd){
 
 
 
-plot_parameterrecovery = function(pp, div, subs){
+plot_parameterrecovery = function(pp, div, subs, title){
   
   if(div){
   hier_pp <- do.call(rbind, lapply(pp, "[[", 1)) %>% drop_na()
@@ -317,7 +317,7 @@ plot_parameterrecovery = function(pp, div, subs){
   }
   if(length(unique(hier_pp$variable)) == 15){
     hier_pp <- hier_pp[!grepl("_b$", hier_pp$variable), ]
-    
+    sub_pp <- sub_pp[!grepl("_b\\[\\d+\\]", sub_pp$variable), ]
   }
   
   hier = hier_pp %>% mutate(divergences = ifelse(div > 0,"yes","no")) %>% 
@@ -329,7 +329,7 @@ plot_parameterrecovery = function(pp, div, subs){
     geom_abline(slope = 1, intercept = 0)+
     scale_color_manual("divergence",values = c("black","red"))+
     scale_y_continuous("simulated value",breaks = scales::pretty_breaks(n = 2))+
-    scale_x_continuous("Recovered value", breaks = scales::pretty_breaks(n = 2))+theme(text = element_text(size = 20))
+    scale_x_continuous("Recovered value", breaks = scales::pretty_breaks(n = 2))+theme(text = element_text(size = 20))+ggtitle(title)
   
 
   # Generate the regular expression pattern dynamically
@@ -349,7 +349,7 @@ plot_parameterrecovery = function(pp, div, subs){
     geom_abline(slope = 1, intercept = 0)+
     scale_color_manual("divergence",values = c("black","red"))+
     scale_y_continuous("simulated value",breaks = scales::pretty_breaks(n = 2))+
-    scale_x_continuous("Recovered value", breaks = scales::pretty_breaks(n = 2))+theme(text = element_text(size = 20))
+    scale_x_continuous("Recovered value", breaks = scales::pretty_breaks(n = 2))+theme(text = element_text(size = 20))+ggtitle(title)
   
   
   
